### 2012-07-09 Papers/paper.tex
Adding paper

\documentclass{acm_proc_article-sp}
\begin{document}

\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\epsfig{file=fly.eps}
\caption{A sample black and white graphic (.eps format).}
\end{figure}

\begin{figure}
\centering
\epsfig{file=fly.eps, height=1in, width=1in}
\caption{A sample black and white graphic (.eps format)
that has been resized with the \texttt{epsfig} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

\begin{figure}
\centering
\psfig{file=rosette.ps, height=1in, width=1in,}
\caption{A sample black and white graphic (.ps format) that has
been resized with the \texttt{psfig} command.}
\end{figure}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

\begin{figure*}
\centering
\epsfig{file=flies.eps}
\caption{A sample black and white graphic (.eps format)
that needs to span two columns of text.}
\end{figure*}
and don't forget to end the environment with
{figure*}, not {figure}!

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The acm\_proc\_article-sp document class file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
\balancecolumns
% That's all folks!
\end{document}

### 2012-07-10 Papers/paper.tex
Adding paper and added comments to classes

@@
+% paper.tex
+% sample ACM SIG Proceedings document using LaTeX2e
+% Author: Heila van der Merwe
+% based upon LaTeX2.09 Guidelines, 9 June 1996
+% Revisions:  10 July 2012
+
+%
+
 \documentclass{acm_proc_article-sp}
@@
 
-\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
-Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
+\title{jpf-android: Model checking Android Applications}
 
-\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
-% 2nd. author
-\alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
+\numberofauthors{3}
+
+\author{%
+\alignauthor  Brink van der Merwe\\
+ \affaddr{Dept. of Computer Science}\\
+       \affaddr{University of Stellenbosch}\\
+       \affaddr{Private Bag X1 Matieland}\\
+       \affaddr{South Africa, 7602}
+       \email{abvdm@gmail.com}
+\alignauthor Heila van der Merwe\\
+       \affaddr{Dept. of Computer Science}\\
+       \affaddr{University of Stellenbosch}\\
+       \affaddr{Private Bag X1 Matieland}\\
+       \affaddr{South Africa, 7602}
+       \email{heilamvdm@gmail.com}
+\alignauthor  Willem Visser\\
+ \affaddr{Dept. of Computer Science}\\
+       \affaddr{University of Stellenbosch}\\
+       \affaddr{Private Bag X1 Matieland}\\
+       \affaddr{South Africa, 7602}
+       \email{willem@gmail.com}
 }
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
 
 \maketitle
+
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms to
-the formatting guidelines for ACM SIG Proceedings.
-It complements the document \textit{Author's Guide to Preparing
-ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
 
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file.
 \end{abstract}
@@
 
-\terms{Theory}
+\terms{VERIFICATION}
 
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+\keywords{Java PathFinder,JPF, Android, Verification} % NOT required for Proceedings
 
 \section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
 
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
+\section{Implementation}
 
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
+\section{Example}
+\section{Discussion}
+\section{Related Work}
+\section{Conclusions}
 
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
-
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
-
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
-
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
-
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-conference
-proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps}
-\caption{A sample black and white graphic (.eps format).}
-\end{figure}
-
-\begin{figure}
-\centering
-\epsfig{file=fly.eps, height=1in, width=1in}
-\caption{A sample black and white graphic (.eps format)
-that has been resized with the \texttt{epsfig} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-\begin{figure}
-\centering
-\psfig{file=rosette.ps, height=1in, width=1in,}
-\caption{A sample black and white graphic (.ps format) that has
-been resized with the \texttt{psfig} command.}
-\end{figure}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-\begin{figure*}
-\centering
-\epsfig{file=flies.eps}
-\caption{A sample black and white graphic (.eps format)
-that needs to span two columns of text.}
-\end{figure*}
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
 \section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
 
@@
 \bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
+\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
 % 
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The acm\_proc\_article-sp document class file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-\balancecolumns
-% That's all folks!
 \end{document}

### 2012-07-10 jpf-android/src/classes/android/app/Activity.java

@@ -3,52 +3,39 @@ package android.app;
 import android.content.Context;
 import android.content.Intent;
 import android.os.Bundle;
-import android.os.Handler;
-import android.os.IBinder;
 import android.view.ContextThemeWrapper;
-import android.view.KeyEvent;
-import android.view.MotionEvent;
 import android.view.View;
 import android.view.ViewGroup;
 import android.view.Window;
 
 import com.android.internal.policy.PolicyManager;
 
-public class Activity extends ContextThemeWrapper implements Window.Callback {
+public class Activity extends ContextThemeWrapper {
+
 	private Context mBase;
-	private Application mApplication;
-	Intent mIntent;
+	// private Application mApplication;
+	Intent mIntent; // Reference to the intent that started this Activity
+	ActivityThread mMainThread; // Reference to the applciation's ActivityThread
+	Activity mParent; // Reference to the activity that started this activity
 
-	ActivityThread mMainThread;
-	Activity mParent;
-
-	boolean mLoadersStarted;
+	// Activity Locks
 	boolean mResumed;
 	private boolean mStopped;
 	boolean mFinished;
 	boolean mStartedActivity;
+
 	/** true if the activity is going through a transient pause */
 	boolean mTemporaryPause = false;
-
-	// private SearchManager mSearchManager;
-	// private MenuInflater mMenuInflater;
 
 	private Window mWindow;
 	// private WindowManager mWindowManager;
 
-	// View mDecor = null; - not using Decor jet
 	boolean mWindowAdded = false;
-	// ActionBarImpl mActionBar = null;
 
 	private CharSequence mTitle;
 	private int mTitleColor = 0;
 
 	Intent mResultData = null;
-
-	private boolean mTitleReady = false;
-
-	private Thread mUiThread;
-	final Handler mHandler = new Handler();
 
 	public void onCreate(Bundle savedInstanceState) {
 		// Loads activity from bundle
@@ -185,7 +172,6 @@ public class Activity extends ContextThemeWrapper implements Window.Callback {
 		// mFragments.attachActivity(this);
 
 		mWindow = PolicyManager.makeNewWindow(this);
-		mWindow.setCallback(this);
 		// mWindow.getLayoutInflater().setPrivateFactory(this);
 		// if (info.softInputMode !=
[…]

### 2012-07-10 jpf-android/src/classes/android/view/View.java

@@ -6,7 +6,7 @@ import android.util.AttributeSet;
 
 /**
  * This is a model of the View class. Currently it only stores the listeners of
- * the View and executes these listeners when the onCLick method is called.
+ * the View and executes these listeners when the onClick method is called.
  * 
  * @author "Heila van der Merwe"
  * 

### 2012-07-10 jpf-android/src/classes/android/view/ViewGroup.java

@@ -2,6 +2,11 @@ package android.view;
 
 import android.content.Context;
 
+/**
+ * An extension to View. It contains a list of child Views.
+ * @author "Heila van der Merwe"
+ *
+ */
 public class ViewGroup extends View {
 
 	private static final int ARRAY_INITIAL_CAPACITY = 12;

### 2012-07-10 jpf-android/src/classes/android/view/ViewRootImpl.java

@@ -1,6 +1,0 @@
-package android.view;
-
-
-public class ViewRootImpl {
-
-}

### 2012-07-10 jpf-android/src/classes/android/view/Window.java

@@ -22,26 +22,23 @@ public class Window extends ViewGroup {
 													// entire application
 													// context
 
-	private Callback mCallback; // for handling window events
-
 	/**
 	 * For now this is the root of the ViewTree (it is suppose to be the
 	 * DecorView but we are not using DecorView yet)
 	 */
 	private ViewGroup mContentParent;
 
-	// static private HashMap<String, Integer> layoutIdMap; // lookup id from
-	// name
-	static private HashMap<Integer, View> layoutMap = new HashMap<Integer, View>(); // get
-																					// view
-																					// hierarchy
-
+	/**Maps the id of the layout to the inflated view hierarchy */
+	static private HashMap<Integer, View> layoutMap = new HashMap<Integer, View>(); 
+																					
 	public Window(Context context) {
 		super(context);
 		Log.i(TAG, "Creating new Window");
-		super.mID = 0; // temp solution teh Window must not be a view If you
-						// look at view hierarchy the farameview is the base
+		
+		super.mID = 0; // temp solution the Window must not be a view If you
+						// look at view hierarchy the frame view is the base
 		mContext = context;
+		
 		if (mLayoutInflater == null) {
 			Log.i(TAG, "Creating new LayouInflator");
 			mLayoutInflater = new LayoutInflater(mContext);
@@ -71,24 +68,6 @@ public class Window extends ViewGroup {
 	static native int[] getLayouts();
 
 	/**
-	 * Set the Callback interface for this window, used to intercept key events
-	 * and other dynamic operations in the window.
-	 * 
-	 * @param callback
-	 *            The desired Callback interface.
-	 */
-	public void setCallback(Callback callback) {
-		mCallback = callback;
-	}
-
-	/**
-	 * Return the current Callback interface for this window.
-	 */
-	public final Callback getCallback() {
-		return mCallback;
-	}
-
-	/**
 	 * Return the Context this window policy is running in, for retrieving
 	 * resources and other information.
 	 * 
@@ -102,6 +81,10 @@ public class Window extends ViewGroup {
 		return mContentParent.findViewById(id);
 	}
 
+	/**
+	 * Sets the parent view of this Window
+	 * @param v
+	 */
 	public void setContentView(int layoutResID) {
 		View layout = layoutMap.get(layoutResID); // inflate
 		layout.mParent = null;
@@ -111,270 +94,14 @@ public class Window extends ViewGroup {
 		// //if (cb != null && !isDestroyed()) {
 		// cb.onContentChanged();
 		// }
-		setVisible0("title", true);
[…]

### 2012-07-10 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_view_Window.java

@@ -75,7 +75,7 @@ public class JPF_android_view_Window {
 		parseRFile(rPath);
 
 	}
-
+	
 	/**
 	 * Parse the R.java file and builds the componentMap and layoutMap.
 	 * 
@@ -83,7 +83,7 @@ public class JPF_android_view_Window {
 	 * @param rPath
 	 *            the path to the R.java file on disk
 	 */
-	private static void parseRFile(String rPath) {
+	public static void parseRFile(String rPath) {
 		
 		Scanner scanner = null;
 		String nextLine;

### 2012-07-16 SampleProject/src/com/example/com/SampleProjectActivity.java
Adding back/home button functionality

@@ -42,6 +42,89 @@ public class SampleProjectActivity extends Activity {
 		});
 	}
 
+	@Override
+	protected void onPostCreate(Bundle savedInstanceState) {
+		super.onPostCreate(savedInstanceState);
+
+	}
+
+	@Override
+	protected void onStart() {
+		super.onStart();
+		System.out.println("1 onStart()");
+
+	}
+
+	@Override
+	protected void onRestart() {
+		super.onRestart();
+		System.out.println("1 onRestart()");
+	}
+
+	@Override
+	protected void onResume() {
+		super.onResume();
+		System.out.println("1  onResume()");
+
+	}
+
+	@Override
+	protected void onPostResume() {
+		super.onPostResume();
+		System.out.println("1  onPostResume()");
+	}
+
+	@Override
+	protected void onPause() {
+		super.onPause();
+		System.out.println("1  onPause()");
+	}
+
+	@Override
+	protected void onStop() {
+		super.onStop();
+		System.out.println("1  onStop()");
+
+	}
+
+	@Override
+	protected void onDestroy() {
+		super.onDestroy();
+		System.out.println("1  onDestroy()");
+
+	}
+
+	@Override
+	public Intent getIntent() {
+		System.out.println("1  getIntent()");
+		return super.getIntent();
+	}
+
+	@Override
+	protected void onRestoreInstanceState(Bundle savedInstanceState) {
+		System.out.println("1  onRestoreInstanceState()");
+		super.onRestoreInstanceState(savedInstanceState);
+	}
+
+	@Override
+	protected void onNewIntent(Intent intent) {
+		System.out.println("1  onNewIntent()");
+
+		super.onNewIntent(intent);
+	}
+
+	@Override
+	protected void onSaveInstanceState(Bundle outState) {
+		System.out.println("1  onSaveInstanceState()");
+		super.onSaveInstanceState(outState);
+	}
+
+	@Override
+	protected void onActivityResult(int requestCode, int resultCode, Intent data) {
+		System.out.println("1  onActivityResult()");
+		super.onActivityResult(requestCode, resultCode, data);
+	}
+
 	/**
 	 * The main entry point to the application
 	 * 

### 2012-07-16 SampleProject/src/com/example/vdm/SampleProjectActivity.java

@@ -49,6 +49,86 @@ public class SampleProjectActivity extends Activity {
 			}
 		});
 	}
+	@Override
+	protected void onStart() {
+		super.onStart();
+		System.out.println("2 onStart()");
+
+	}
+
+	@Override
+	protected void onRestart() {
+		super.onRestart();
+		System.out.println("2 onRestart()");
+	}
+
+	@Override
+	protected void onResume() {
+		super.onResume();
+		System.out.println("2  onResume()");
+
+		
+		
+	}
+
+	@Override
+	protected void onPostResume() {
+		super.onPostResume();
+		System.out.println("2  onPostResume()");
+	}
+
+	@Override
+	protected void onPause() {
+		super.onPause();
+		System.out.println("2  onPause()");
+	}
+
+	@Override
+	protected void onStop() {
+		super.onStop();
+		System.out.println("2  onStop()");
+
+		
+	}
+
+	@Override
+	protected void onDestroy() {
+		super.onDestroy();
+		System.out.println("2  onDestroy()");
+
+	}
+
+	@Override
+	public Intent getIntent() {
+		System.out.println("2  getIntent()");
+		return super.getIntent();
+	}
+
+	@Override
+	protected void onRestoreInstanceState(Bundle savedInstanceState) {
+		System.out.println("2  onRestoreInstanceState()");
+		super.onRestoreInstanceState(savedInstanceState);
+	}
+
+	@Override
+	protected void onNewIntent(Intent intent) {
+		System.out.println("2  onNewIntent()");
+
+		super.onNewIntent(intent);
+	}
+
+	@Override
+	protected void onSaveInstanceState(Bundle outState) {
+		System.out.println("2  onSaveInstanceState()");
+		super.onSaveInstanceState(outState);
+	}
+
+	@Override
+	protected void onActivityResult(int requestCode, int resultCode, Intent data) {
+		System.out.println("2  onActivityResult()");
+		super.onActivityResult(requestCode, resultCode, data);
+	}
+
 
 	/**
 	 * The main entry point to the application

### 2012-07-16 jpf-android/src/classes/android/app/Activity.java

@@ -161,13 +161,14 @@ public class Activity extends ContextThemeWrapper {
 		mBase = newBase;
 	}
 
-	final void attach(ActivityThread aThread,  Application application, Activity parent) {// ,
+	final void attach(ActivityThread aThread, Application application,
+			Activity parent, Intent intent) {// ,
 		// Instrumentation instr, IBinder token, int ident,
-		//, Intent intent, ActivityInfo info,
+		// , Intent intent, ActivityInfo info,
 		// CharSequence title, Activity parent, String id,
 		// NonConfigurationInstances lastNonConfigurationInstances,
 		// Configuration config) {
-		
+
 		// attachBaseContext(context);
 
 		// mFragments.attachActivity(this);
@@ -187,11 +188,11 @@ public class Activity extends ContextThemeWrapper {
 		// mToken = token;
 		// mIdent = ident;
 		// mApplication = application;
-		// mIntent = intent;
+		 mIntent = intent;
 		// mComponent = intent.getComponent();
 		// mActivityInfo = info;
 		// mTitle = title;
-		// mParent = parent;
+		 mParent = parent;
 		// mEmbeddedID = id;
 		// mLastNonConfigurationInstances = lastNonConfigurationInstances;
 
@@ -208,9 +209,11 @@ public class Activity extends ContextThemeWrapper {
 		startActivityForResult(intent, -1);
 	}
 
-	public void startActivityForResult(Intent intent, int requestCode) {
+	public final void startActivityForResult(Intent intent, int requestCode) {
 		// if (mParent == null) {
 		// Instrumentation.ActivityResult ar =
+		intent.setParent(this);
+		onPause();
 		System.out.println("Activity for result");
 		ActivityManagerProxy.startActivityProxy(intent);
 		// if (ar != null) {
@@ -232,6 +235,11 @@ public class Activity extends ContextThemeWrapper {
 		// } else {
 		// mParent.startActivityFromChild(this, intent, requestCode);
 		// }
+	}
+
+	public void onRestoreInstanceState(Bundle state) {
+		// TODO Auto-generated method stub
+
 	}
 
 }

### 2012-07-16 jpf-android/src/classes/android/app/ActivityStack.java

@@ -1,518 +1,0 @@
-package android.app;
-
-import android.content.Context;
-
-import com.android.server.am.ActivityManagerService;
-
-final class ActivityStack {
-	static final boolean DEBUG_SWITCH = true;
-	static final String TAG = "ActivityStack";
-
-	// How long between activity launches that we consider safe to not warn
-	// the user about an unexpected activity being launched on top.
-	static final long START_WARN_TIME = 5 * 1000;
-
-	enum ActivityState {
-		INITIALIZING, RESUMED, PAUSING, PAUSED, STOPPING, STOPPED, FINISHING, DESTROYING, DESTROYED
-	}
-
-	final ActivityManagerService mService = null;
-	final boolean mMainStack = false;
-
-	final Context mContext = null;
-	//
-	// /**
-	// * The back history of all previous (and possibly still running)
-	// activities.
-	// * It contains HistoryRecord objects.
-	// */
-	// final ArrayList<ActivityRecord> mHistory = new
-	// ArrayList<ActivityRecord>();
-	//
-	// /**
-	// * Used for validating app tokens with window manager.
-	// */
-	// // final ArrayList<IBinder> mValidateAppTokens = new
-	// ArrayList<IBinder>();
-	//
-	// /**
-	// * List of running activities, sorted by recent usage. The first entry in
-	// * the list is the least recently used. It contains HistoryRecord objects.
-	// */
-	// final ArrayList<ActivityRecord> mLRUActivities = new
-	// ArrayList<ActivityRecord>();
-	//
-	// /**
-	// * List of activities that are waiting for a new activity to become
-	// visible
-	// * before completing whatever operation they are supposed to do.
-	// */
-	// final ArrayList<ActivityRecord> mWaitingVisibleActivities = new
-	// ArrayList<ActivityRecord>();
-	//
-	// /**
-	// * List of activities that are ready to be stopped, but waiting for the
-	// next
-	// * activity to settle down before doing so. It contains HistoryRecord
-	// * objects.
-	// */
-	// final ArrayList<ActivityRecord> mStoppingActivities = new
-	// ArrayList<ActivityRecord>();
-	//
-	// /**
-	// * List of activities that are in the process of going to sleep.
-	// */
-	// final ArrayList<ActivityRecord> mGoingToSleepActivities = new
-	// ArrayList<ActivityRecord>();
-	//
-	// /**
[…]

### 2012-07-16 jpf-android/src/classes/android/app/ActivityThread.java

@@ -2,7 +2,6 @@ package android.app;
 
 import java.util.HashMap;
 
-import android.content.ComponentName;
 import android.content.Intent;
 import android.os.Bundle;
 import android.os.Handler;
@@ -41,10 +40,32 @@ public final class ActivityThread {
 
 		public final void scheduleLaunchActivity(String activityName,
 				Intent intent) {
+
+			if (currentActivity != null
+					&& activityName == currentActivity.getName()) {
+				// TODO
+				System.out.println("This activity has already been started");
+			} else {
+
+			}
+
 			ActivityClientRecord r = new ActivityClientRecord();
 			r.name = activityName;
 			r.intent = intent;
 			queueOrSendMessage(H.LAUNCH_ACTIVITY, r, 0, 0);
+		}
+
+		private void performBackPressed() {
+			Activity parent = currentActivity.activity.mParent;
+			//TODO stop id parent null
+			ActivityClientRecord r = new ActivityClientRecord();
+			r.name = parent.getClass().getName();
+			r.intent = new Intent();
+			queueOrSendMessage(H.LAUNCH_ACTIVITY, r, 0, 0);
+		}
+
+		private void performHomePressed() {
+			handleDestroyActivity(currentActivity.name);
 		}
 	}
 
@@ -185,29 +206,20 @@ public final class ActivityThread {
 
 		}
 
-		private void handleDestroyActivity(String obj) {
-			// TODO Auto-generated method stub
+	}
 
-		}
+	private void handleDestroyActivity(String obj) {
+		currentActivity.activity.onPause();
+		currentActivity.activity.onStop();
+
 	}
 
 	private Activity performLaunchActivity(ActivityClientRecord r,
 			Intent customIntent) {
 
-		// ComponentName component = r.intent.getComponent();
-		// if (component == null) {
-		// component = r.intent.resolveActivity(mInitialApplication
-		// .getPackageManager());
-		// r.intent.setComponent(component);
-		// }
-		//
-		// if (r.activityInfo.targetActivity != null) {
-		// component = new ComponentName(r.activityInfo.packageName,
-		// r.activityInfo.targetActivity);
-		// }
-
 		// Make new instance of the Activity class
 		Activity activity = null;
+
 		try {
 			Class<Activity> cls = (Class<Activity>) Class.forName(r.getName());
 			activity = cls.newInstance();
@@ -215,94 +227,40 @@ public final class ActivityThread {
 			throw new RuntimeException("Unable to instantiate activity " + ": "
[…]

### 2012-07-16 jpf-android/src/classes/android/content/Intent.java

@@ -4,15 +4,25 @@ import java.util.ArrayList;
 import java.util.HashSet;
 import java.util.Set;
 
+import android.app.Activity;
 import android.os.Bundle;
 
 public class Intent {
 
+	Activity parent; 
 	String mAction;
 	String mType;
 	String mComponent;
 	HashSet<String> mCategories;
 	Bundle mExtras;
+
+	public Activity getParent() {
+		return parent;
+	}
+
+	public void setParent(Activity parent) {
+		this.parent = parent;
+	}
 
 	public Intent() {
 

### 2012-07-16 jpf-android/src/classes/com/android/internal/os/RunTimeInit.java

@@ -1,9 +1,0 @@
-package com.android.internal.os;
-
-
-public class RunTimeInit {
-	public static void wtf(String tag, Throwable t) {
-
-	}
-
-}

### 2012-07-16 jpf-android/src/classes/com/android/internal/policy/impl/PhoneWindow.java

@@ -1,45 +1,0 @@
-package com.android.internal.policy.impl;
-
-import android.content.Context;
-import android.view.Window;
-
-public class PhoneWindow extends Window {
-
-	public PhoneWindow(Context context) {
-		super(context);
-		// TODO Auto-generated constructor stub
-	}
-//    private final static String TAG = "PhoneWindow";
-//	
-//    private LayoutInflater mLayoutInflater;
-//    
-//
-//    // This is the top-level view of the window, containing the window decor.
-//    private DecorView mDecor;
-//
-//    // This is the view in which the window contents are placed. It is either
-//    // mDecor itself, or a child of mDecor where the contents go.
-//    private ViewGroup mContentParent;
-//
-//    
-//    public PhoneWindow(Context context) {
-//        super(context);
-//        mLayoutInflater = LayoutInflater.from(context);
-//    }
-//    
-//    
-//    @Override
-//    public void setContentView(int layoutResID) {
-//        if (mContentParent == null) {
-//            installDecor();
-//        } else {
-//            mContentParent.removeAllViews();
-//        }
-//        mLayoutInflater.inflate(layoutResID, mContentParent);
-//        final Callback cb = getCallback();
-//        if (cb != null && !isDestroyed()) {
-//            cb.onContentChanged();
-//        }
-//    }
-
-}

### 2012-07-16 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_app_ActivityManagerProxy.java

@@ -11,9 +11,6 @@ import java.lang.reflect.Method;
 import java.util.HashMap;
 import java.util.logging.Logger;
 
-import android.content.ComponentName;
-import android.content.Intent;
-
 /**
  * Models the Android ActivityManagerService. This Service is traditionally run
  * in the system process and is not part of the application process. That is why
@@ -86,13 +83,37 @@ public class JPF_android_app_ActivityManagerProxy {
 			int intentref = getJPFIntent(env, intentName);
 			startActivity(env, 0, intentref);
 
-		} else if (action.action.equals("destroy")) {
-			String intentName = (String) action.arguments[0];
-			int intentref = getJPFIntent(env, intentName);
-			startActivity(env, 0, intentref);
-
+		} else if (action.action.equals("backButton")) {
+			backButton(env);
+		}else if(action.action.equals("homeButton")) {
+			homeButton(env);
 		}
 	}
+
+	
+	private static void backButton(MJIEnv env) {
+		// schedule launch of activity
+		int appRef = JPF_android_app_ActivityThread.getApplicationRef();
+		String methodName = "performBackPressed()V";
+		int[] args = {};
+
+		callMethod(env, appRef, methodName, args);
+
+	}
+	
+	private static void homeButton(MJIEnv env) {
+		// schedule launch of activity
+		int appRef = JPF_android_app_ActivityThread.getApplicationRef();
+		String methodName = "performHomePressed()V";
+		int[] args = {};
+
+		callMethod(env, appRef, methodName, args);
+
+	}
+	
+	
+	
+	
 
 	/**
 	 * Returns the reference to an the Intent object
@@ -158,7 +179,7 @@ public class JPF_android_app_ActivityManagerProxy {
 		return env.getReferenceField(intentRef, "mComponent");
 	}
 
-	public static void stopActivity() {
+	private static void stopActivity(MJIEnv env, int clsRef, int intentRef) {
 		// TODO
 		@SuppressWarnings("unused")
 		String methodName = "scheduleDestroyActivity(Ljava/lang/String;)V";

### 2012-07-16 Papers/paper.tex
Updating JPF paper

@@
 \documentclass{acm_proc_article-sp}
+\usepackage{graphicx}
 \begin{document}
 
-\title{jpf-android: Model checking Android Applications}
+\title{Verifying Android Applications using Java PathFinder}
 
@@
 
-\keywords{Java PathFinder,JPF, Android, Verification} % NOT required for Proceedings
+\keywords{Java PathFinder, JPF, Android, Verification} % NOT required for Proceedings
 
 \section{Introduction}
+%The current trend in software development is mobile application development.
 
-\section{Implementation}
+%At Google I/O 2012 Android claimed to have approximately 600
+%thousand applications on the market with a total of 20 billion application downloads. They continue to note that this number is growing by
+%one billion per month.
 
+Although Android mobile applications and Java desktop applications both use the Java language, they are developed for a completely different
+platforms.  and both contain many similar errors and defects. These defects include faults such as concurrency issues and run-time
+exceptions. 
+         are  compared to
+
+The testing of Android applications  also faces many challenges including:
+\begin{enumerate}
+ \item The device challenge. 
+ Mobile applications can only fully run on a mobile devices/emulators. Additionally the physical devices are
+not designed with testing in mind.
+
+ \item Event driven architecture.
+ The event input must be simulated which is especially difficult due to the many types of
+sensory inputs that must be supported.
+
+ \item Operating system variety. It is impossible to test the application on all the different operating system versions.
+\end{enumerate}
+
+Due to these challenges and the rapid pace at which applications are developed and released, application testing becomes too expensive in
+terms of time and money. This results in many mobile applications being unstable and unreliable.
+
+Manual testing is not the solution to the problem as it is very expensive, time consuming and does not detect enough errors in
+Android applications. That is why only automatic testing frameworks are the best options.
+
+There are currently two ways to automatically test Android applications:
+\begin{enumerate}
+ \item testing on a physical device/emulator
+  Install application on the device. Install test project that runs in the same process. The test project drives the application testing.
+
+ %\begin{figure}[h!]
+ %\centering
+ %\includegraphics{../../Pictures/test_framework.png}
+ % test_framework.png: 473x517 pixel, 96dpi, 12.51x13.68 cm, bb=0 0 355 388
+%\end{figure}
+  Examples include: Robotium\ref{} Android Test project
+
+  MoneyRunner~\ref{},SPark~\ref{}
+  -advantage wifi and many sensor events  already modelled
+-problem is that emulator run actual android so testing framework as to either be android application
+-
+
+ \item testing the application on a computer
+   Examples:
+    android unit tests
+    android lint
+
+   mock objects
+   adapt for pc
+- static analysis or model android framework
+- mock unit tests - still have to write the tests
+- Robolectric
+\end{enumerate}
+
+% what are we going to do and why (WHAT ARE ADVANTAGES)
+This paper describes jpf-android, an extension to Java PathFinder that allows the automatic testing of Android Applications.
+
+The first section of the paper provides an overview of Android and Java Pathfinder and how JPF can be used to test Android applications.
+The next section describes the design and development of the jpf-android tool followed by an simple example to show how the tool works. The
+paper will conclude by discussing the effectiveness and usefulness of the tool.
+
+\newpage
+\section{Background}
+\subsection{The Android architecture}
+Android is an open source software stack for mobile devices such as smartphones and tablets with an advanced RISC Machine (ARM)
+architecture.
+
+It consists of:
+    the Android operating system built on top of a modified Linux kernel,
+    the application framework - set of libraries api
+    an application development toolkit assisting developers to create applications for the platform.
+
+An application runs on framework using api libs to communicate.
+system process threading
+
+%\begin{figure}[h!]
+% \centering
+% \includegraphics[width=\pagewidth]{../../M-Projek/heila/research_proposal/02-AndroidStack.png}
+ % 5502982451_1f78830c9e.jpg: 500x270 pixel, 96dpi, 13.23x7.14 cm, bb=0 0 375 203
+%\end{figure}
+
+each application runs in own process
+1 thread called the looper
+handler message queue structure
+2 types of input
+
+%\begin{figure}[h!]
+% \centering
+% \includegraphics[width=\pagewidth]{../../M-Projek/heila/research_proposal/5502982451_1f78830c9e.jpg}
+ % 5502982451_1f78830c9e.jpg: 500x270 pixel, 96dpi, 13.23x7.14 cm, bb=0 0 375 203
+%\end{figure}
+
+% why cant we just run android applications they are written in java?
+Specific java version without swing etc
+native code - has to be modelled
+
+\subsection{Java PathFinder}
+JPF is a powerful software model checker used to test automatically whether the system under test (SUT) meets a given specification.
+Java applications~\cite{}. It consists of a custom Java virtual machine implementation that executes the compiled java byte-code of the
+system under test(SUT).
+
+JPF models the Java API libraries to allow... 
+-how does it work?
+-modelled java libs
+-custom vm executing java bytecode
+-controlled environment executing all execution paths
+-listeners for certain property violations
+
+Furthermore, JPF's design encourages developers to create extensions to the framework. It provides that key mechanisms:
+to model java libraries,
+model native method calls (MJI),
+track bytecode execusion and listen for property violations
+
+Currently there exists many extensions including a symbolic execution extension (jpf-symbc), data race detector (jpf-racefinder) and a
+abstract window toolkit (AWT) extension (jpf-awt).
+
+One of the advantages of extending JPF is that it has been thoroughly tested and already works for Java applications. So as soon as the the
+Android applications can run on JPF, common errors and defects can be detected.
+
+\subsection{Applying JPF to Android applications}
+Android applications are written in a custom Java implementation Apache Harmony.
+
+Dalvik, the virtual machine used in Google's Android platform, uses a subset of Harmony for the core of its Class Library.[15] However,
+Dalvik does not align to Java SE nor Java ME Class Library profiles (for example J2ME classes, AWT and Swing are not supported). Instead it
+uses its own library,[16] built on a subset of Harmony.
+
+-model the android framework so that android applications can run on the java JVM
+-on it can be run on the java jvm we can run it on jpf’s java jvm
+
+- testing with object maps
+- advantage above capture and replay is that all event sequences are executed
+
+%what do I want to detect?
+
+The objective of this project is to create a JPF extension based on JPF-AWT's scripting mechanism that will:
+\begin{itemize}
+ \item model the Android framework libraries using Java SE. Android applications are built on a framework written in Apache Harmony's Java
+implementation. This framework will basically be simplified and closed down to allow the Android application to execute in a controlled
+environment of JPF on a computer.
+
+ \item model user and system input to the application. Android applications are event driven. We need to create a user model to simulate
+input events for the application, similar to a driver.
+
+ \item use these models to automatically detect property violations such as deadlocks,race conditions and run-time exceptions in Android
+applications.
+
+\end{itemize}
+\newpage
+\section{Development}
+% what are the issues of modelling the framework?
+size of android framework - what to model
+  - we don't necessarily want to have to run android applications exactly as they are run, then gets to complication to test all application
+  paths.
+
+   - the more is modelled the more has to be re-modelled if something changes
+
+   - if too little is modelled, then support to little functionality
+
+native code and the fact that it is run in different thread - but if not native cannot be back tracked
+
+2 important parts to model:
+- processes we don’t need ipc on computer everything runs in one process and we do not need this for testing
+- binder ipc communication between components very import part see application as a whole
+- gui\& system events drives applciation
+- application framework
+
+% description of the model:
+1 process
+1 main thread
+1 application
+direct communication instead of binder
+no gui drawing
+
+\subsection{The model}
+- how is an application structured
+--activitythread
+--messagequeue + handler structure
+--window structure
+
+script input
+- what is the purpose of the script
+-- input to program
+-- vars added
+-- later check added
+
+- what can the script handle
+- GUI and external events
+-- depth first
+-- non-determinism
+
+- what can the script not handle
+-- specific activity event structure
+-- progressive disclosure
+
+how and where is the script events handled
+- messagequeue processScriptAction
+- generates event sequences uses backtrack to do depth first search trough all possible sequences
+\newpage
 \section{Example}
+% example showing the detection of a null pointer exception in certain case
+
 \section{Discussion}
-\section{Related Work}
-\section{Conclusions}
+%discussion showing how the tool is successful and the advantages of the tool
 
-\section{Acknowledgments}
+\section{Conclusion}
+
+limitations
+- only 1 application
+- no android native code can be handled
+
+\section{Acknowledgements}
 

### 2012-07-16 Papers/paper.tex
Adding paper updated intro and background

@@
 
-Although Android mobile applications and Java desktop applications both use the Java language, they are developed for a completely different
-platforms.  and both contain many similar errors and defects. These defects include faults such as concurrency issues and run-time
-exceptions. 
-         are  compared to
+%Although Android mobile applications and Java desktop applications both use the Java language, they are developed for completely different
+%platforms.  and both contain many similar errors and defects. These defects include faults such as concurrency issues and run-time
+%exceptions. 
+ %        are  compared to
 
-The testing of Android applications  also faces many challenges including:
-\begin{enumerate}
- \item The device challenge. 
- Mobile applications can only fully run on a mobile devices/emulators. Additionally the physical devices are
-not designed with testing in mind.
+%Software testing is a complex and time consuming process.
 
- \item Event driven architecture.
- The event input must be simulated which is especially difficult due to the many types of
-sensory inputs that must be supported.
+Android applications and Java desktop applications are designed for completely different computing platforms. They are both however, built on an implementation of the 
+Java programming language. As a consequence, Android applications contain many of the same defects as Java applications. These defects include but is not limited to concurrency
+issues and runtime exceptions. It follows that it must be possible to adapt existing testing frameworks for Java applications to verify Android applications.
 
- \item Operating system variety. It is impossible to test the application on all the different operating system versions.
-\end{enumerate}
+The problem is that Android applications face the following obstacles when it comes to application testing:
+\begin{description}
+ \item [Event driven architecture]. Android application flow is driven by events. This event input must be simulated which is especially difficult due to the many types of
+sensory and system inputs that must be supported.
 
-Due to these challenges and the rapid pace at which applications are developed and released, application testing becomes too expensive in
+ \item [The device challenge]. 
+ Mobile applications are created to run on ARM devices/ emulators. Additionally the physical devices are
+not designed with testing in mind. Alternative ways have to be devised to automatically simulate input to the application.
+- java version
+
+ \item [Operating system variety]. It is impossible to test an application on all the different operating system versions.
+\end{description}
+
+Due to these challenges and the rapid pace at which applications are developed and released~\cite{}, mobile application testing becomes too expensive in
 terms of time and money. This results in many mobile applications being unstable and unreliable.
@@
 Manual testing is not the solution to the problem as it is very expensive, time consuming and does not detect enough errors in
-Android applications. That is why only automatic testing frameworks are the best options.
+Android applications. That is why only automatic testing frameworks are discussed below.
 
-There are currently two ways to automatically test Android applications:
-\begin{enumerate}
- \item testing on a physical device/emulator
-  Install application on the device. Install test project that runs in the same process. The test project drives the application testing.
+There are currently two ways to automatically test Android applications: on the device/emulator or on a computer.
 
- %\begin{figure}[h!]
- %\centering
- %\includegraphics{../../Pictures/test_framework.png}
- % test_framework.png: 473x517 pixel, 96dpi, 12.51x13.68 cm, bb=0 0 355 388
-%\end{figure}
-  Examples include: Robotium\ref{} Android Test project
+The most common way is to test an application is the on a physical device/emulator. Examples of such projects include 
+the Android testing framework~\cite{AndroidTesting}, MonkeyRunner~\cite{AndroidTesting} and Robotium~\cite{Robotium}. 
+These projects depend on Android's built-in JUnit framework and InstrumentationTestRunner as the test case runner~\cite{AndroidTesting}.Other
+projects use alternative ways to automatically generate input by manipulating the accessibility technologies 
+or the software keyboard~\cite{AccessibilityTech, KeyboardModel}.
+Mockito or Android Mock a user to  mock out the Android SDK.
+While this is a valid approach, we have found that without Robolectric, the level of mocking needed to test an
+Android app quickly yields tests that are essentially reverse implementations of the application code.
 
-  MoneyRunner~\ref{},SPark~\ref{}
-  -advantage wifi and many sensor events  already modelled
--problem is that emulator run actual android so testing framework as to either be android application
--
+The advantage of running the application on the emulator is that the application runs on actual android operating system. The disadvantage is, as mentioned before,
+Android applications are driven by user and system events. So the input has to be modeled which is not so easy. It is slow to run the tests and each test 
+sequence has to be defined and executed one by one.
 
- \item testing the application on a computer
-   Examples:
-    android unit tests
-    android lint
-
-   mock objects
-   adapt for pc
-- static analysis or model android framework
-- mock unit tests - still have to write the tests
-- Robolectric
-\end{enumerate}
+The other approach is to test an Android application on the computer. There are different ways of implementing such a framework. Android lint~\cite{} for example makes 
+use of static analysis to identify common errors in applications. Robolectric~\cite{} create mocks of classes that allows an application to be Unit tested on the JVM.
 
 % what are we going to do and why (WHAT ARE ADVANTAGES)
-This paper describes jpf-android, an extension to Java PathFinder that allows the automatic testing of Android Applications.
+This paper describes jpf-android, an extension to Java PathFinder~\cite{JPFDocs} which is a Java application model checker framework. jpf-android will allow the automatic
+verification of Android Applications on the standard Java jvm.
 
@@
 
-\newpage
 \section{Background}
@@
 One of the advantages of extending JPF is that it has been thoroughly tested and already works for Java applications. So as soon as the the
-Android applications can run on JPF, common errors and defects can be detected.
+Android applications can run on JPF, common errors and defects can be detected. It provides an simple way to model classes.
 
@@
 %what do I want to detect?
-
 The objective of this project is to create a JPF extension based on JPF-AWT's scripting mechanism that will:
@@
 \section{Development}
+
 % what are the issues of modelling the framework?
-size of android framework - what to model
+Modeling the Android framework is quite a complex task. The main problems being:
+\begin{itemize}
+ \item android.jar libs
+\item we need a driver 
+ \item size of android framework - what to model
   - we don't necessarily want to have to run android applications exactly as they are run, then gets to complication to test all application
   paths.
-
    - the more is modelled the more has to be re-modelled if something changes
-
    - if too little is modelled, then support to little functionality
 
-native code and the fact that it is run in different thread - but if not native cannot be back tracked
+\item native code and the fact that it is run in different thread - but if not native cannot be back tracked
+
+\end{itemize}
 

### 2012-07-23 Papers/paper.tex
Paper changes

--- 2012-07-10 Papers/paper.tex
@@
 % based upon LaTeX2.09 Guidelines, 9 June 1996
-% Revisions:  10 July 2012
-
+% Revisions:  17 July 2012
 %
-
-\documentclass{acm_proc_article-sp}
+\documentclass{sig-alternate}
+\usepackage{listings}
 \begin{document}
 
-\title{jpf-android: Model checking Android Applications}
+\title{Verifying Android Applications using Java PathFinder}
 
@@
 
-\keywords{Java PathFinder,JPF, Android, Verification} % NOT required for Proceedings
+\keywords{Java PathFinder, JPF, Android, Verification} % NOT required for Proceedings
+
+%The current trend in software development is mobile application development.
+%At Google I/O 2012 Android claimed to have approximately 600
+%thousand applications on the market with a total of 20 billion application downloads. They continue to note that this number is growing by
+%one billion per month.
+%Although Android mobile applications and Java desktop applications both use the Java language, they are developed for completely different
+%platforms.  and both contain many similar errors and defects. These defects include faults such as concurrency issues and run-time
+%exceptions. 
+%are  compared to
 
 \section{Introduction}
+Software testing and verification is a crucial part of software development. It determines the quality and the user
+experience of software which are two very important aspects of Android applications. Especially for the high volume Android applications
+that are released.
 
-\section{Implementation}
+Although application testing is so important, it is often neglected as a result of its complex and time consuming process. Android
+applications also face additional challenges when it comes to software testing:
 
-\section{Example}
+Firstly, Android applications are graphical user interface (GUI) based. Their application flow is hence driven by GUI events. The
+simplest way to test GUI applications is manual black-box testing, but this is time consuming, error prone and
+expensive~\cite{AccessibilityTech}. Furthermore, user input is not the only factor that determines application flow. Android applications
+also receive input from system events. These include events such as battery low and network down warnings as well as start application and
+stop application commands.
+
+Secondly, Android applications are developed in a custom implementation of Java adopted from the Apache Harmony~\cite{harmony} project. The
+compiled applications can only be executed on a special virtual machine (VM) called the DalvikVM that is part of the Android operating
+system~\cite{dalvik}. Hence Android applications can only run on a computer in an Android emulator. This makes testing very slow and
+difficult to automate.
+
+Due to these challenges, the rapid pace at which applications are developed and the lack of testing tools available, mobile application
+testing becomes too expensive in terms of time and money. An important method to reduce this high cost, is to 
+automate the testing of GUI -- in this case Android -- applications~\cite{AccessibilityTech}.
+
+Currently, Android applications are tested automatic in one of two ways:
+
+The most common way to test Android applications is using a physical device/emulator. Testing frameworks such as
+the MonkeyRunner~\cite{monkey} and Robotium~\cite{robotium} makes use of Android's built-in JUnit framework~\cite{TestingAndroid} to
+execute test on the emulator/device. Other projects use alternative ways to automatically generate input by manipulating the built in
+accessibility technologies~\cite{AccessibilityTech} or by re-implementing the Android keyboard~\cite{KeyboardModel}. Mockito~\cite{mockito}
+and Android Mock~\cite{androidMock} allows JUnit testing on the DalvikVM by using a mocking architecture.
+
+The advantage of running the application on the Dalvik VM is that the application runs on the actual android operating system. The
+disadvantage is, as mentioned before, Android applications are driven by user and system events. So the input has to be modelled which is
+not simple to
+automate on a device/emulator. Moreover running test on the Dalvik VM is slow as they have to be instrumented and each test sequence has
+to be defined and executed one by one.
+
+The other approach is to test Android applications by using the Java Virtual Machine (JVM). There are different ways of implementing such a
+framework. Android
+lint~\cite{lint}, for example, makes use of static analysis to identify common errors in applications. Robolectric~\cite{robolectric}
+intercepts the loading of Android classes and then uses shadows classes that model these classes.
+
+Although Android applications and Java desktop applications are designed for completely different Java virtual machines, they are both
+built on an implementation of the Java Application Programming Interface (API). As a consequence, Android applications contain many of the
+same errors as Java applications. These defects include but is not limited to concurrency issues and runtime exceptions. It follows that it
+is possible to adapt an existing testing frameworks for Java applications, to verify Android applications on the JVM.
+
+% what are we going to do and why 
+This paper describes an extension to Java PathFinder (JPF)~\cite{JPFDocs} that enables the automatic
+verification of Android Applications on the standard Java JVM.
+
+This paper will first provide an overview of JPF and how it can be used to test Android applications. Thereafter a description of the
+development of the jpf-android tool is provided, followed by a simple example to show how the tool works.
+
+\section{Design}
+\subsection{Java PathFinder}
+JPF is an automated open source analysis engine for Java applications~\cite{JPFDocs}. It is implemented as explicit state model checker
+that includes mechanisms to model Java class files, model native method calls (MJI), track bytecode execution and listen for
+property violations. Additionally, JPF's design encourages developers to create extensions to the framework. Currently there exists many
+extensions including a symbolic execution extension (jpf-symbc), data race
+detector (jpf-racefinder) and an abstract window toolkit (AWT) extension (jpf-awt).
+
+The JPF Android extension (jpf-android) will use JPF's extension mechanisms to:
+\begin{enumerate}
+\item model the Android library classes so that Android applications can run on the JVM
+\item create an input model to simulate user and system input to the application.
+\end{enumerate}
+
+One of the advantages of extending JPF is that it has been rigorously tested and already works for Java applications. As soon as
+Android applications can run on JPF, common software errors such as null pointer exceptions, assertion violations, deadlocks,
+race-conditions will be detected.
+
+The first step in modelling the android class libraries is to understand the structure of the Android operating system (OS).
+
+\subsection{The Android operating system}
+
+The Android OS is built on top of the Linux kernel. For security reasons, each Android application is installed as a separate user
+on the OS. Linux's built-in user management system then keeps applications from modifying the data and code of other applications. For
+even more security each application is run as a separate process on the OS. The applications can only interact using the Binder
+inter-process communication (IPC) mechanism. The main process/application of the OS is called the system process. The system process
+contains services responsible for running the main tasks of the OS for example:
+\begin{itemize}
+ \item activity manager -- manages the life-cycle and interaction of all the activities running in the system
+ \item window manager -- allows applications to draw on the screen
+ \item package manager -- stores information on the application packages installed on the device
+\end{itemize}
+
+Android follows a single-threaded application design in which a main thread handles all application events. This structure is
+commonly used by many UI frameworks since it becomes too complex to make all UI classes thread safe~\cite{}. This main thread is called
+the \texttt{Looper} and has a message queue attach to it containing application events to be handled. When UI events are fired, they
+are added to the \texttt{Looper}'s message queue. System events are also scheduled on the main \texttt{Looper} by adding them to the message
+queue. The \texttt{Looper} is responsible for continuously looping through these messages and handling them appropriately. This could
+include updating a widget, loading a new activity or processing an intent.
+
+The main class of an Android application is called the \texttt{ActivityThread}. The \texttt{ActivityThread} keeps track of the
+application's components and handles user and system events. Android applications written by developers consists of the
+following application components:
+\begin{itemize}
+\item Activities -- responsible for representing and managing an user interface. An application can consist of many
+Activities.
+\item Services -- performs background operations such as the pulling of messages from a server every 5 minutes. Services do not have user
+interfaces and an application can have zero or more services running simultaneously.
+\item Broadcast receivers -- listens for and responds to system-wide events such as network failing, low battery or screen orientation
+change events.
+\item Content providers -- manages application data stored on the file system, in databases, on the web or other storage medium and provides
+a gateway to this data from other applications.
+\end{itemize}
+
+These components are created and managed by the \texttt{ActivityThread}.They interact with each other and with other
+applications using a structure called an \texttt{Intent}. An \texttt{Intent} is a high level implementation of the Binder IPC.
+
+\subsection{Scope of jpf-android}
+The Android platform is very large and one of the main challenges is to decide which parts of the system to model. The objective of
+jpf-android is to test Android application not to model the Android framework, so we do not necessarily want to model the entire
+Android OS. Additionally, the more of the framework is modelled, the more has to be re-modelled when Google changes the design.
+
+jpf-android will only model one application with multiple components and their interaction. Furthermore the graphics libraries will not
+be modelled as we do not have to physically draw on the screen for testing. The system service of the Android OS is not run in the
+application process and runs in its own thread. To reduce scheduling possibilities we will not model this service, but implement the
+necessary tasks as part of the application process. Lastly, as the application will not be communicating with outside processes, the Binder
+IPC will not be modelled. The components will communicate with each other by sending direct references to themselves.
+
+\section{Development}
+At the basis of the tool's modelled framework are the message queue, the view structure and the activity manager. These components will be
+discussed in greater detail below:
+
+In the Android framework all input events of the system are placed on the message queue and then processed by the \texttt{Looper}. Hence,
+jpf-android needed a way to place events in this queue. jpf-awt introduced the idea of using a simple script to write event sequences as
+input for the application. This scripting mechanism made use of JPF's state backtracking feature to support elements such as the ANY and
+REPEAT structures to make it simpler to specify many input sequences simultaneously. Each time the message queue is empty an event is
+read from the script file.
+
+As Android and AWT both use a single-threaded UI design, jpf-android could build on the idea of scripting input events. There were two
+challenges to using this approach in jpf-android:
+\begin{enumerate}
+ \item Android applications other that AWT applications receive input from two different
+sources: user input from the UI, and system input from the activity manager through Intents. 
+ \item Android applications contains multiple windows - one for each Activity. This complicates the UI input as each
+window has its own unique set of view components - thus a unique input sequence.
+\end{enumerate}
+These challenges were addressed by expanded the scripting language in a few ways:
+
+\subsection{The input model}
+jpf-android classifies input events as either UI events or system events. UI events are handled similar to
+how they were handled in jpf-awt. When the activity's UI is inflated, an object map is built binding the name of a view component (widget)
+to a reference of the inflated view object. When an UI event occurs the name of the target view component is looked-up in the object map
+and then the action is called on the actual view object.
+
+An Intent-object are used to describe system events. Intents are used to start Activities
+and Services or to provide a notification of certain events. They are similar to messages containing a description of an operation to be
+performed or, often in the case of broadcasts, a description of something that has happened and is being announced. The are two types of
+Intents:
+\begin{itemize}
+ \item explicit intents -- explicitly store the name of the component to start
+ \item implicit intents -- store the details of a event that occurred these details are then used to lookup components that are registered
+for such events. Component's register for intents in the AndroidManifest file. Now to resolve the component to which the intent is sent an
+the ActivityManager has to parse the AndroidManifest file. This file contains the the list of Intent filters for each
+Application component. 
+\end{itemize}
+
+But the ActivityManager requires information about which component to send the intent to: an Activity, Service or Receiver. In the Android
+code
+an Intent is sent by calling one of the methods \texttt{startActivity(Intent), startService(Intent), sendBroadcast(Intent)}. Usually this
+request is sent to the activity manager where it is handled appropriately. But as we are not modelling the
+ActivityManger, the Intent is handled by a local, small model of the ActivityManager. The Activity Manager then resolves the intent to the
+appropriate application and then forwards the intent to the application's ActivityThread to be processed.
+
+To allow a user to script system events, variables were added to the scripting language. Variable names will be identified by
+the '@' in front of the name as '\$' is already used in jpf-awt to identify UI components:
+
+The script file that send an intent to start the \texttt{SampleActivity} will look like:
+\begin{figure}
+{\small
+{\sf 
+@intent1.setComponent(``SampleActivity'')\\
+startActivity(@intent1)\\
+\$button1.onClick()
+}
+}
+\caption{Starting an Activity}
+\end{figure}
+
+\subsection{The input sequence}
+jpf-android started out by using a sequential input script that drove the application execution. This became an issue when some of the
+input events were non-deterministically scheduled to happen. In other words, if we do not know whether an event took place or
+not, we can not schedule following events. Hence, the scriptwriter has to have knowledge of the system and
+know which button press fires what activities. There could in be non-determinism in term of events but not in terms of starting
+activities/services. This is because if an Activity is started, the following events in the script must be related to the new Activity.
+
+Lets look at an example:
+\begin{figure}
+\centering
+\epsfig{file=newContact.eps, width=1in,}
+\caption{Adding a new contact screen}
+\end{figure}
+
+This is the Create new contact screen of a phonebook application. At the bottom of the screen there are three buttons. The cancel button
+returns to the previous screen, the clear button stays on the current screen and the create button forwards to a new screen. Noe  let us
+look at the following input script:
+
+\begin{figure}
+{\small
+{\sf 
+@startIntent.setComponent(``com.example.AddContactActivity'')\\
+startActivity(@startIntent)\\
+\\
+\textbf{REPEAT} 3 \{\\
+\textbf{ANY} \{backButton.onclick(),clearButton.onClick(),addButton.onClick()\}\\
+\}
+
+nameEdit.setText(``Mary'')
+}
+}
+\caption{Starting an Activity}
+\end{figure}
+
+This script file will execute 3 event sequences:
+\begin{enumerate}
+ \item start AddContactActivity\\
+press clearButton\\
+set name edit's text
+ \item start AddContactActivity\\ 
+ press addButton button, \\
+ set name edit's text
+ \item start AddContactActivity\\
+ press homeButton button, \\
+ set name edit's text
+\end{enumerate}
+
+The problem is that only after the clear button is pressed is the nameEdit.setText(`` Mary'') command valid as we do not know if the other
+screens contain textboxes.
+
+Android applications have many Activities, each with a unique interface. At any time, the system or the UI can fire an event to start a new
+Activity. The problem is as this is a nondeterministic chance the the input file can not run sequential. So that when an Activity is
+started, jpf-android can go and look up what are the event sequences that can be performed on the activity.
+
+To address this issue, we adopted the input script to be divided into sections. Each section list the sequential input to an specific
+Activity:
+
+\begin{figure}
+{\small
+{\sf 
+@startIntent.setComponent(``com.example.ListContactsActivity'')
+
+\textbf{TARGET:} start\\
+startActivity(@startIntent)\\
+
+\textbf{TARGET:} com.example.ListContactsActivity\\
+listbox.select<0-N> \#starts ViewActivity\\
+
+\textbf{TARGET:} com.example.ViewContactActivity\\
+backButton.onClick() \# restarts ListContactsActivity, \\
+
+}
+}
+\caption{Starting an Activity}
+\end{figure}
+so how do we know not to run sequence again other wise infinite loop?
+
+The next challenge 
+-  returning to an activity don't wan to execute sequence again example contacts list contact - view contact - list contact
+
+\begin{figure}
+{\small
+{\sf 
+TARGET: start\\
+  startActivity(ListContactsActivity)
+
+TARGET: com.example.ListContactsActivity\\
+  listbox.select<0-N> \#starts ViewActivity
+
+TARGET: com.example.ViewContactActivity\\
+   backButton.onClick() \# restarts ListContactsActivity, 
+}
+}
+\caption{Starting an Activity}
+\end{figure}
+
+The question is how do we then backtrack the case where an activity was started?
+
+All state that is stored in the JPF side will be backtracked automatically, but we are not on the JPF side. We have to know when an
+activity is started as a backtrack or as a new start.
+
+entrypoint 
+\newpage
+\section{Case Study}
+% example showing the detection of a null pointer exception in certain case
+
 \section{Discussion}
-\section{Related Work}
-\section{Conclusions}
+%discussion showing how the tool is successful and the advantages of the tool
 
-\section{Acknowledgments}
+limitations
+- only 1 application
+- no android native code can be handled
+
+\section{Conclusion}
+
+\section{Acknowledgements}
 

### 2012-07-23 Papers/paper.tex
Updating paper

@@
 %
-\documentclass{sig-alternate}
+\documentclass{acm_proc_article-sp}
 \usepackage{listings}
@@
        \affaddr{South Africa, 7602}
-       \email{abvdm@gmail.com}
+       \email{abvdm@cs.sun.ac.za}
 \alignauthor Heila van der Merwe\\
@@
        \affaddr{South Africa, 7602}
-       \email{heilamvdm@gmail.com}
+       \email{hvdmerwe@cs.sun.ac.za}
 \alignauthor  Willem Visser\\
@@
        \affaddr{South Africa, 7602}
-       \email{willem@gmail.com}
+       \email{wvisser@cs.sun.ac.za}
 }
@@
 \begin{abstract}
+Software testing and verification plays an important role in determining the quality and robustness of software. These are two very important attributes of 
+mobile applications and can determine the success of the applications. Especially since there are more than 600 000 applications available on the Google play
+market today. But, mobile application testing is a specialized and complex field. Due to mobile applications' event driven design and mobile execution environment,
+there currently exist only a small number of 
+effective tools to verify these applications.
 
+This paper describes the development of JPF-ANDROID, an Android application verification tool. JPF-ANDROID is built on Java PathFinder, 
+a Java model checking engine. JPF-ANDROID attempts to create a simplified model of the Android framework on which an Android application can run. It then allows
+the user to script input events to drive the application flow. JPF-ANDROID provides a way to detect common property violations such as deadlocks and runtime exceptions
+in Android applications. The paper also provides an example of how to apply JPF-ANDROID to an application and discusses the limitations of the framework.
 \end{abstract}
 
-% A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+\category{D.2.5}{Software Engineering}{Testing and Debugging}[Testing tools]
 
@@
 
-\keywords{Java PathFinder, JPF, Android, Verification} % NOT required for Proceedings
-
-%The current trend in software development is mobile application development.
-%At Google I/O 2012 Android claimed to have approximately 600
-%thousand applications on the market with a total of 20 billion application downloads. They continue to note that this number is growing by
-%one billion per month.
-%Although Android mobile applications and Java desktop applications both use the Java language, they are developed for completely different
-%platforms.  and both contain many similar errors and defects. These defects include faults such as concurrency issues and run-time
-%exceptions. 
-%are  compared to
+\keywords{Mobile Application, Java PathFinder, JPF, Android, Verification, Testing}
 
 \section{Introduction}
-Software testing and verification is a crucial part of software development. It determines the quality and the user
+Software testing is a crucial part of software development. It determines the quality and the user
 experience of software which are two very important aspects of Android applications. Especially for the high volume Android applications
-that are released.
+that are released yearly.
 
@@
 
-Firstly, Android applications are graphical user interface (GUI) based. Their application flow is hence driven by GUI events. The
+Firstly, Android applications are graphical user interface (GUI) based and their application flow is driven by GUI events. The
 simplest way to test GUI applications is manual black-box testing, but this is time consuming, error prone and
 expensive~\cite{AccessibilityTech}. Furthermore, user input is not the only factor that determines application flow. Android applications
-also receive input from system events. These include events such as battery low and network down warnings as well as start application and
-stop application commands.
+also receive input from system events. These include events such as battery low and network down warnings as well as ``start application'' and
+``stop application'' commands.
 
-Secondly, Android applications are developed in a custom implementation of Java adopted from the Apache Harmony~\cite{harmony} project. The
-compiled applications can only be executed on a special virtual machine (VM) called the DalvikVM that is part of the Android operating
-system~\cite{dalvik}. Hence Android applications can only run on a computer in an Android emulator. This makes testing very slow and
+Secondly, Android applications are developed in a custom implementation of Java Application Programming Interface (API)
+ adopted from the Apache Harmony~\cite{harmony} project. The
+compiled applications can only be executed on a special virtual machine (VM) called the DalvikVM that runs on Android devices~\cite{dalvik}. 
+This means that Android applications can only execute on an device/emulator running the Android operating system. This makes testing very slow and
 difficult to automate.
@@
 
-Currently, Android applications are tested automatic in one of two ways:
+Currently, Android applications are tested automatically in one of two ways:
 
-The most common way to test Android applications is using a physical device/emulator. Testing frameworks such as
+The most common way to test Android applications is to use a physical device/emulator. Testing frameworks such as
 the MonkeyRunner~\cite{monkey} and Robotium~\cite{robotium} makes use of Android's built-in JUnit framework~\cite{TestingAndroid} to
-execute test on the emulator/device. Other projects use alternative ways to automatically generate input by manipulating the built in
+execute tests on the emulator/device. Other projects use alternative ways to automatically generate input by manipulating the built in
 accessibility technologies~\cite{AccessibilityTech} or by re-implementing the Android keyboard~\cite{KeyboardModel}. Mockito~\cite{mockito}
@@
 
-The advantage of running the application on the Dalvik VM is that the application runs on the actual android operating system. The
-disadvantage is, as mentioned before, Android applications are driven by user and system events. So the input has to be modelled which is
-not simple to
-automate on a device/emulator. Moreover running test on the Dalvik VM is slow as they have to be instrumented and each test sequence has
+The advantage of testing application on the Dalvik VM is that the applications run on the actual Android operating system. The
+disadvantage is, as mentioned before, Android applications are driven by user and system events. So the input has to be modeled which is
+not simple to automate on a device/emulator. Moreover running test on the Dalvik VM is slow as they have to be instrumented and each test sequence has
 to be defined and executed one by one.
@@
 Although Android applications and Java desktop applications are designed for completely different Java virtual machines, they are both
-built on an implementation of the Java Application Programming Interface (API). As a consequence, Android applications contain many of the
-same errors as Java applications. These defects include but is not limited to concurrency issues and runtime exceptions. It follows that it
-is possible to adapt an existing testing frameworks for Java applications, to verify Android applications on the JVM.
+built on an implementation of the Java API. As a consequence, Android applications contain many of the
+same errors as Java applications. These defects include, but is not limited to, concurrency issues and common runtime exceptions such as NullPointer Exceptions. It follows that it
+is possible to adapt an existing Java testing framework to verify Android applications.
 
@@
 This paper will first provide an overview of JPF and how it can be used to test Android applications. Thereafter a description of the
-development of the jpf-android tool is provided, followed by a simple example to show how the tool works.
+development of the JPF-ANDROID tool is provided, followed by a simple example to show how the tool works.
 
@@
 JPF is an automated open source analysis engine for Java applications~\cite{JPFDocs}. It is implemented as explicit state model checker
-that includes mechanisms to model Java class files, model native method calls (MJI), track bytecode execution and listen for
+that includes mechanisms to model Java classes, model native method calls (MJI), track byte code execution and listen for
 property violations. Additionally, JPF's design encourages developers to create extensions to the framework. Currently there exists many
-extensions including a symbolic execution extension (jpf-symbc), data race
-detector (jpf-racefinder) and an abstract window toolkit (AWT) extension (jpf-awt).
+extensions including a symbolic execution extension (JPF-SYMB), data race
+detector (JPF-RACEFINDER) and an abstract window toolkit (AWT) extension (JPF-AWT).
 
-The JPF Android extension (jpf-android) will use JPF's extension mechanisms to:
+The JPF Android extension (JPF-ANDROID) will use JPF's extension mechanisms to:
 \begin{enumerate}
@@
 
-One of the advantages of extending JPF is that it has been rigorously tested and already works for Java applications. As soon as
-Android applications can run on JPF, common software errors such as null pointer exceptions, assertion violations, deadlocks,
-race-conditions will be detected.
+One of the advantages of extending JPF is that it has been rigorously tested and can can detect many different defects in Java applications. As soon as
+Android applications can run on JPF, common software errors such as null pointer exceptions, assertion violations, deadlocks and
+race-conditions will automatically be detected.
 
-The first step in modelling the android class libraries is to understand the structure of the Android operating system (OS).
+The first step in modeling the android class libraries is to understand the structure of the Android application framework.
 
-\subsection{The Android operating system}
+\subsection{The Android application framework}
 
-The Android OS is built on top of the Linux kernel. For security reasons, each Android application is installed as a separate user
-on the OS. Linux's built-in user management system then keeps applications from modifying the data and code of other applications. For
-even more security each application is run as a separate process on the OS. The applications can only interact using the Binder
-inter-process communication (IPC) mechanism. The main process/application of the OS is called the system process. The system process
+Android can be described as a software stack that includes an operating system (OS), middleware and key applications~\cite{AndroidDocs}. 
+The Android framework is built on top of the Linux kernel, using the native libraries. For security reasons each application is run as a separate process on the OS on its 
+own Dalvik VM instance. The applications can only communicate with the Android framework using the Binder inter-process communication (IPC) mechanism. 
+\begin{figure}
+\centering
+\epsfig{file=stack.eps, width=3in,}
+\caption{The Android application stack}
+\end{figure}
+
+The main application of the OS is called the system process. The system process
 contains services responsible for running the main tasks of the OS for example:
 \begin{itemize}
- \item activity manager -- manages the life-cycle and interaction of all the activities running in the system
+ \item activity manager -- manages the life-cycle and interaction of all the activities running on the system
  \item window manager -- allows applications to draw on the screen
@@
 
-Android follows a single-threaded application design in which a main thread handles all application events. This structure is
-commonly used by many UI frameworks since it becomes too complex to make all UI classes thread safe~\cite{}. This main thread is called
+Android follows a single-threaded application design in which the main thread of an application handles all application events~\cite{AndroidDocs}. This structure is
+commonly used by many UI frameworks since it becomes too complex to make all UI classes thread safe~\cite{SingleThread}. For Android, this main thread is called
 the \texttt{Looper} and has a message queue attach to it containing application events to be handled. When UI events are fired, they
@@
 
+\begin{figure}
+\centering
+\epsfig{file=app.eps, width=3in,}
+\caption{The Android structure}
+\end{figure}
+
 The main class of an Android application is called the \texttt{ActivityThread}. The \texttt{ActivityThread} keeps track of the
-application's components and handles user and system events. Android applications written by developers consists of the
+application's components and handles user and system events. Android applications consists of the
 following application components:
@@
 
-\subsection{Scope of jpf-android}
+\subsection{Scope of JPF-ANDROID}
 The Android platform is very large and one of the main challenges is to decide which parts of the system to model. The objective of
-jpf-android is to test Android application not to model the Android framework, so we do not necessarily want to model the entire
+JPF-ANDROID is to test Android application not to model the Android framework, so we do not necessarily want to model the entire
 Android OS. Additionally, the more of the framework is modelled, the more has to be re-modelled when Google changes the design.
 
-jpf-android will only model one application with multiple components and their interaction. Furthermore the graphics libraries will not
+JPF-ANDROID will only model one application with multiple components and their interaction. Furthermore the graphics libraries will not
 be modelled as we do not have to physically draw on the screen for testing. The system service of the Android OS is not run in the
@@
 In the Android framework all input events of the system are placed on the message queue and then processed by the \texttt{Looper}. Hence,
-jpf-android needed a way to place events in this queue. jpf-awt introduced the idea of using a simple script to write event sequences as
+JPF-ANDROID needed a way to place events in this queue. jpf-awt introduced the idea of using a simple script to write event sequences as
 input for the application. This scripting mechanism made use of JPF's state backtracking feature to support elements such as the ANY and
@@
 
-As Android and AWT both use a single-threaded UI design, jpf-android could build on the idea of scripting input events. There were two
-challenges to using this approach in jpf-android:
+As Android and AWT both use a single-threaded UI design, JPF-ANDROID could build on the idea of scripting input events. There were two
+challenges to using this approach in JPF-ANDROID:
 \begin{enumerate}
@@
 \subsection{The input model}
-jpf-android classifies input events as either UI events or system events. UI events are handled similar to
+JPF-ANDROID classifies input events as either UI events or system events. UI events are handled similar to
 how they were handled in jpf-awt. When the activity's UI is inflated, an object map is built binding the name of a view component (widget)
@@
 \subsection{The input sequence}
-jpf-android started out by using a sequential input script that drove the application execution. This became an issue when some of the
+JPF-ANDROID started out by using a sequential input script that drove the application execution. This became an issue when some of the
 input events were non-deterministically scheduled to happen. In other words, if we do not know whether an event took place or
@@
 Activity. The problem is as this is a nondeterministic chance the the input file can not run sequential. So that when an Activity is
-started, jpf-android can go and look up what are the event sequences that can be performed on the activity.
+started, JPF-ANDROID can go and look up what are the event sequences that can be performed on the activity.
 

### 2012-07-24 Papers/images/Stack.tex
Adding images to paper

\documentclass[10pt,a4paper]{article}
\usepackage[rgb]{xcolor}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{fit}
\usetikzlibrary{shapes.geometric}
\usepgflibrary{shapes.geometric}
\usepgflibrary{decorations.shapes}

\begin{document}
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}
\definecolor[named]{fillColor}{rgb}{0.48,0.17,0.26}

\begin{figure}[h!]
 \centering
\definecolor[named]{fillColor}{rgb}{0.48,0.17,0.26}
\begin{tikzpicture}
[block/.style={rectangle,draw=black!50,text width=1.7cm,,align=center,
decoration={shape sep=.1cm}}]

\node[block, minimum height=30mm,minimum width=60mm, fill=gray!20 ] (server)  at (5.3,0) {};
\node[text width=6cm,align=center] (text) at (5.3,2.1)  {Web application server\\(Tomcat)};

\node[block,minimum width=18mm, minimum height=17mm,fill=fillColor!69!white,text=white] (client) {Client};
\node[text width=3cm,align=center] (text) at (0,2.1)  {Web browser\\ (Firefox,Chrome)};

\node[block, minimum width=20mm,minimum height=25mm,fill=fillColor!69!white,text=white] (webserver)
at (3.6,0) {Web server};
\node[block, minimum width=30mm,minimum height=25mm,fill=fillColor!69!white,text=white] (applicationserver)
at (6.4,0) {Application server};

\node[block,fill=black!0 ,minimum width=18mm, minimum height=17mm] (persistence) 		at (8.5,0) {Persistence
provider};

\node[text width=6cm,align=center] (text) at (12,2.1)  {Database\\ (HSQLDB)};
\node[minimum width=1cm, minimum height=2.7cm, cylinder, shape border rotate=90, draw, >=stealth,shape
aspect=.2,fill=fillColor!69!white,text=white] (database) 				at (12,0) {Data source};

\draw [->] (client) to (server);
\draw [<-] (client) to node [above,align=center,midway] {HTTP}  (server);
\draw [<->] (persistence) to node [above,align=center,midway] {JDBC} (database) ;

\end{tikzpicture}
\caption{Starlight web-based application architecture}
\end{figure}

\begin{figure}[h!]
 \centering
\definecolor[named]{fillColor}{rgb}{0.48,0.17,0.26}
\begin{tikzpicture}
[block/.style={rectangle,draw=black!50,text width=1.7cm,,align=center,
decoration={shape sep=.1cm}}]

\node[block, minimum height=20mm,minimum width=60mm, fill=fillColor!69!white,text=white] (apps1)  at (-5.1,0) {};
\node[text width=6cm,align=center,text=white,font=\Large\bfseries\sf ] (text) at (-5.25,0.64)  {Stock Android Apps};
\node[text width=6cm,align=center,text=white,font=\small\sf ] (text) at (-5.25,-0.34)  {Launcher   Phone  Alarm\\Email  Settings  Camera\\Gallery  Calendar ... };

\node[block, minimum height=20mm,minimum width=60mm, fill=fillColor!69!white,text=white ] (apps2)  at (1.1,0) {};
\node[text width=6cm,align=center,text=white, font=\Large\bfseries\sf ] (text) at (0.2,0)  {Custom/Market Apps};

\draw[style=dashed] (-8.5, -1.2) to (3.5,-1.2);

\node[block, minimum height=20mm,minimum width=60mm, fill=fillColor!69!white,text=white] (apps1)  at (-5.1,-2.4) {};

\end{tikzpicture}
\caption{Starlight web-based application architecture}
\end{figure}

\end{document}

### 2012-07-24 Papers/paper.tex
Adding images to paper

@@
 \begin{abstract}
-Software testing and verification plays an important role in determining the quality and robustness of software. These are two very important attributes of 
-mobile applications and can determine the success of the applications. Especially since there are more than 600 000 applications available on the Google play
-market today. But, mobile application testing is a specialized and complex field. Due to mobile applications' event driven design and mobile execution environment,
-there currently exist only a small number of 
-effective tools to verify these applications.
+Mobile application testing is a specialized and complex field. Due to mobile applications' event driven design and mobile runtime environment,
+there currently exist only a small number of tools to verify these applications.
 
 This paper describes the development of JPF-ANDROID, an Android application verification tool. JPF-ANDROID is built on Java PathFinder, 
-a Java model checking engine. JPF-ANDROID attempts to create a simplified model of the Android framework on which an Android application can run. It then allows
+a Java model checking engine. JPF-ANDROID provides a simplified model of the Android framework on which an Android application can run. It then allows
 the user to script input events to drive the application flow. JPF-ANDROID provides a way to detect common property violations such as deadlocks and runtime exceptions
-in Android applications. The paper also provides an example of how to apply JPF-ANDROID to an application and discusses the limitations of the framework.
+in Android applications. The paper also provides an example of how to apply JPF-ANDROID to an application.
 \end{abstract}
@@
 \section{Introduction}
+%Software testing and verification plays an important role in determining the quality and robustness of software. These are two very important attributes of 
+%mobile applications and can determine the success of the applications. Especially since there are more than 600 000 applications available on the Google play
+%market today. But, m
+
 Software testing is a crucial part of software development. It determines the quality and the user
@@
 \begin{enumerate}
-\item model the Android library classes so that Android applications can run on the JVM
+\item model the Android application framework so that Android applications can run on the JVM,
 \item create an input model to simulate user and system input to the application.
@@
 
-One of the advantages of extending JPF is that it has been rigorously tested and can can detect many different defects in Java applications. As soon as
-Android applications can run on JPF, common software errors such as null pointer exceptions, assertion violations, deadlocks and
+One of the advantages of extending JPF is that it has been rigorously tested and can successfully detect many common defects in Java applications. As soon as
+Android applications can run on JPF-ANDROID, common software errors such as null pointer exceptions, assertion violations, deadlocks and
 race-conditions will automatically be detected.
 
-The first step in modeling the android class libraries is to understand the structure of the Android application framework.
+The first step in modeling the android framework is to understand its architecture.
 
-\subsection{The Android application framework}
+\subsection{Android}
+Android is an open source software stack for mobile devices such as smartphones with an advanced RISC Machine (ARM) architecture (Figure 1).
+It consists of the Android operating system (OS), the application framework and an application development toolkit assisting developers to create
+applications for the platform~\cite{AndroidDocs}.
 
-Android can be described as a software stack that includes an operating system (OS), middleware and key applications~\cite{AndroidDocs}. 
-The Android framework is built on top of the Linux kernel, using the native libraries. For security reasons each application is run as a separate process on the OS on its 
-own Dalvik VM instance. The applications can only communicate with the Android framework using the Binder inter-process communication (IPC) mechanism. 
+The Android OS is built on top of a modified Linux kernel. It provides a layer of abstraction on top of its low level functionality such as process,
+memory, user, network and thread management. On top of the Android kernel is a set of native libraries including a custom, optimised version of the
+JVM called the Dalvik VM.
+
+For security reasons every Android application is run as a separate process in its own Dalvik VM instance. Hence, applications can only
+communicate with each other and the with the Android framework using Android's Binder inter-process communication (IPC) mechanism.
+
 \begin{figure}
@@
 
-The main application of the OS is called the system process. The system process
-contains services responsible for running the main tasks of the OS for example:
+The main Android application is called the system process. The system process contains services responsible for running the main tasks of the system for example:
 \begin{itemize}
@@
 
-Android follows a single-threaded application design in which the main thread of an application handles all application events~\cite{AndroidDocs}. This structure is
+Android applications follow a single-threaded design in which the main thread of the application handles all application events~\cite{AndroidDocs}. This structure is
 commonly used by many UI frameworks since it becomes too complex to make all UI classes thread safe~\cite{SingleThread}. For Android, this main thread is called
-the \texttt{Looper} and has a message queue attach to it containing application events to be handled. When UI events are fired, they
+the \texttt{Looper}. The \texttt{Looper} and has a message queue attach to it containing application events to be handled. When UI events are fired, they
 are added to the \texttt{Looper}'s message queue. System events are also scheduled on the main \texttt{Looper} by adding them to the message
@@
 The Android platform is very large and one of the main challenges is to decide which parts of the system to model. The objective of
-JPF-ANDROID is to test Android application not to model the Android framework, so we do not necessarily want to model the entire
-Android OS. Additionally, the more of the framework is modelled, the more has to be re-modelled when Google changes the design.
+JPF-ANDROID is to verify Android applications by running the code using a collection of event sequences and then to detect when errors appear.
 
-JPF-ANDROID will only model one application with multiple components and their interaction. Furthermore the graphics libraries will not
-be modelled as we do not have to physically draw on the screen for testing. The system service of the Android OS is not run in the
-application process and runs in its own thread. To reduce scheduling possibilities we will not model this service, but implement the
-necessary tasks as part of the application process. Lastly, as the application will not be communicating with outside processes, the Binder
-IPC will not be modelled. The components will communicate with each other by sending direct references to themselves.
+The more the Android framework gets modeled, the more realistic the model is and the more errors can be found. But, the more of the Android framework
+get modeled, the more scheduling possibilities can occur and the search space becomes to big. Additionally, the more of the framework is modelled, 
+the more has to be re-modelled when the architecture changes.
+
+JPF-ANDROID will focus on verifying one application with multiple application components and their interaction. The system service of the Android OS
+is not run in the application process and runs in its own thread. To reduce scheduling possibilities we will not model the entire system service,
+but implement the necessary tasks as part of the application process.
+
+The following parts of the Android framework will be modeled:
+\begin{description}
+ \item [Activity manager] - modeled to manages the lifecycle of Activities and other application components.
+ \item [Activity thread] - modeled to manage the application components and their input.
+ \item [Application components] - including Activity, Service, Broadcast Receiver and Content Provider. 
+ \item [Window and View structure] - The view hierachy will be modeled including the widgets and the sindow classes.
+ \item [Message queue] - The message queue will be modeled to support input from the script file.
+\end{description}
+
+Lastly, as the application will not be communicating with outside processes, the Binder IPC will not be modelled.
+The components will communicate with each other by sending direct references to themselves.
 
@@
 
-In the Android framework all input events of the system are placed on the message queue and then processed by the \texttt{Looper}. Hence,
-JPF-ANDROID needed a way to place events in this queue. jpf-awt introduced the idea of using a simple script to write event sequences as
+As shown in Figure 2, all input events of the system are placed in the message queue and then processed by the \texttt{Looper}. Hence,
+JPF-ANDROID needed a way to place events in this queue. JPF-AWT introduced the idea of using a simple script to write event sequences as
 input for the application. This scripting mechanism made use of JPF's state backtracking feature to support elements such as the ANY and
 REPEAT structures to make it simpler to specify many input sequences simultaneously. Each time the message queue is empty an event is
-read from the script file.
+read from the script file. As Android and AWT both use a single-threaded UI design, JPF-ANDROID could build on the idea of scripting input events.
 
-As Android and AWT both use a single-threaded UI design, JPF-ANDROID could build on the idea of scripting input events. There were two
-challenges to using this approach in JPF-ANDROID:
-\begin{enumerate}
- \item Android applications other that AWT applications receive input from two different
-sources: user input from the UI, and system input from the activity manager through Intents. 
- \item Android applications contains multiple windows - one for each Activity. This complicates the UI input as each
-window has its own unique set of view components - thus a unique input sequence.
-\end{enumerate}
-These challenges were addressed by expanded the scripting language in a few ways:
+%There were two
+%challenges to using this approach in JPF-ANDROID:
+%\begin{enumerate}
+% \item Android applications other that AWT applications receive input from two different
+%sources: user input from the UI, and system input from the activity manager through Intents. 
+% \item Android applications contain multiple windows - one for each Activity. This complicates the UI input as each
+%window has its own unique set of view components - thus a unique input sequence.
+%\end{enumerate}
+%These challenges were addressed by expanded the scripting feature in a few ways:
 
 \subsection{The input model}
+\begin{figure}
+\centering
+\epsfig{file=arch.eps, width=3in,}
+\caption{JPF-ANDROID architecture}
+\end{figure}
+
 JPF-ANDROID classifies input events as either UI events or system events. UI events are handled similar to
-how they were handled in jpf-awt. When the activity's UI is inflated, an object map is built binding the name of a view component (widget)
-to a reference of the inflated view object. When an UI event occurs the name of the target view component is looked-up in the object map
+how they were handled in JPF-AWT. When the activity's UI is inflated, an object map is built binding the name of a view component (widget)
+to the inflated widget. When an UI event occurs the name of the target view component is looked-up in the object map
 and then the action is called on the actual view object.
 
-An Intent-object are used to describe system events. Intents are used to start Activities
+An Intent-object are is to describe system events. Intents are used to start Activities
 and Services or to provide a notification of certain events. They are similar to messages containing a description of an operation to be

### 2012-08-07 Papers/images/Stack.tex
updating files

@@
 \usepgflibrary{decorations.shapes}
-
+\thispagestyle{empty}
 \begin{document}
@@
  \centering
+\definecolor[named]{grey}{rgb}{0.9,0.9,0.9}
+\definecolor[named]{green}{rgb}{0.297,0.832,0.793}
+\definecolor[named]{blue}{rgb}{0.574,0.633,0.926}
+
 \definecolor[named]{fillColor}{rgb}{0.48,0.17,0.26}
+
 \begin{tikzpicture}
-[block/.style={rectangle,draw=black!50,text width=1.7cm,,align=center,
+[block/.style={rectangle,draw=black,text width=1.7cm,,align=center,
 decoration={shape sep=.1cm}}]
 
-\node[block, minimum height=30mm,minimum width=60mm, fill=gray!20 ] (server)  at (5.3,0) {};
-\node[text width=6cm,align=center] (text) at (5.3,2.1)  {Web application server\\(Tomcat)};
+\node[block, minimum height=20mm,minimum width=60mm,fill=green] (apps1)  at (-3.25,1.25) {};
+\node[text width=6cm,align=center,font=\Large\bfseries\sf ] (text) at (-3.25,1.8)  {Stock Android Apps};
+\node[text width=6cm,align=center,font=\small\sf ] (text) at (-3.25,0.9)  {Launcher   Phone  Alarm\\Email  Settings 
+Camera\\Gallery  Calendar ... };
 
-\node[block,minimum width=18mm, minimum height=17mm,fill=fillColor!69!white,text=white] (client) {Client};
-\node[text width=3cm,align=center] (text) at (0,2.1)  {Web browser\\ (Firefox,Chrome)};
+\node[block, minimum height=20mm,minimum width=60mm,fill=green] (apps2)  at (3.25,1.25) {};
+\node[text width=6cm,align=center, font=\Large\bfseries\sf ] (text) at (3.25,1.25)  {Custom/Market Apps};
 
-\node[block, minimum width=20mm,minimum height=25mm,fill=fillColor!69!white,text=white] (webserver)
-at (3.6,0) {Web server};
-\node[block, minimum width=30mm,minimum height=25mm,fill=fillColor!69!white,text=white] (applicationserver)
-at (6.4,0) {Application server};
+\draw[style=dashed] (-7, 0) to (7,0);
+\draw[style=dashed] (0, 0) to (0,-3.5);
+\node[align=center,font=\small\sf,rotate=90, fill=white] (text) at (0,-1.5)  {Binder};
 
-\node[block,fill=black!0 ,minimum width=18mm, minimum height=17mm] (persistence) 		at (8.5,0) {Persistence
-provider};
+\node[block, minimum height=30mm,minimum width=60mm,fill=grey] (apps1)  at (-3.25,-1.75) {};
+\node[text width=6cm,align=center,font=\Large\bfseries\sf ] (text) at (-3.25,-0.65)  {System Server};
+\node[text width=6cm,align=center,font=\small\sf ] (text) at (-3.25,-2)  {Activity Manager    Window Manager\\Package Manager   
+Location Manager\\Power Manager Battery Service\\Notification Manager Mount Service\\Clipboard Service  ...};
 
-\node[text width=6cm,align=center] (text) at (12,2.1)  {Database\\ (HSQLDB)};
-\node[minimum width=1cm, minimum height=2.7cm, cylinder, shape border rotate=90, draw, >=stealth,shape
-aspect=.2,fill=fillColor!69!white,text=white] (database) 				at (12,0) {Data source};
+\node[block, minimum height=30mm,minimum width=28.75mm,fill=grey] (apps1)  at (1.6875,-1.75) {};
+\node[text width=6cm,align=center,font=\Large\bfseries\sf ] (text) at (1.6875,-1.75)  {android.*};
+\node[block, minimum height=30mm,minimum width=28.75mm,fill=grey] (apps1)  at (4.8125,-1.75) {};
+\node[text width=6cm,align=center,font=\Large\bfseries\sf ] (text) at (4.8125,-1.57)  {java.*};
+\node[text width=6cm,align=center,font=\small\sf ] (text) at (4.8125,-2)  {(Apache Harmony)};
 
-\draw [->] (client) to (server);
-\draw [<-] (client) to node [above,align=center,midway] {HTTP}  (server);
-\draw [<->] (persistence) to node [above,align=center,midway] {JDBC} (database) ;
+\node[block, minimum height=10mm,minimum width=125mm,fill=grey] (apps1)  at (0,-4) {};
+\node[text width=13cm,align=center,font=\large\bfseries\sf ] (text) at (0,-4)  {Android Runtime/Dalvik/Zygote};
+
+\draw[style=dashed] (-7, -4.75) to (7,-4.75);
+
+\node[block, minimum height=12mm,minimum width=28.75mm,fill=blue] (apps1)  at (1.6875,-5.6) {};
+\node[text width=3cm,align=center,font=\large\bfseries\sf ] (text) at (1.6875,-5.6)  {Libs};
+\node[block, minimum height=12mm,minimum width=28.75mm,fill=blue] (apps1)  at (4.8125,-5.6) {};
+\node[text width=3cm,align=center,font=\large\bfseries\sf ] (text) at (4.8125,-5.6)  {Init/Toolbox};
+\node[block, minimum height=12mm,minimum width=28.75mm,fill=blue] (apps1)  at (-1.6875,-5.6) {};
+\node[text width=3cm,align=center,font=\large\bfseries\sf ] (text) at (-1.6875,-5.6)  {Native\\Daemons};
+\node[block, minimum height=12mm,minimum width=28.75mm,fill=blue] (apps1)  at (-4.8125,-5.6) {};
+\node[text width=3cm,align=center,font=\large\bfseries\sf ] (text) at (-4.8125,-5.6)  {Hardware\\Drivers};
+
+\node[block, minimum height=10mm,minimum width=125mm,fill=blue] (apps1)  at (0,-6.95) {};
+\node[text width=13cm,align=center,font=\Large\bfseries\sf ] (text) at (0,-6.75)  {Linux Kernel};
+\node[text width=6cm,align=center,font=\small\sf ] (text) at (0,-7.25)  {Binder, ashmem, wakelocks,lowmem, ...};
 
 \end{tikzpicture}
-\caption{Starlight web-based application architecture}
 \end{figure}
 
+\newpage
+\thispagestyle{empty}
 \begin{figure}[h!]
  \centering
+\definecolor[named]{grey}{rgb}{0.9,0.9,0.9}
+\definecolor[named]{green}{rgb}{0.297,0.832,0.793}
+\definecolor[named]{blue}{rgb}{0.574,0.633,0.926}
+
 \definecolor[named]{fillColor}{rgb}{0.48,0.17,0.26}
+
 \begin{tikzpicture}
-[block/.style={rectangle,draw=black!50,text width=1.7cm,,align=center,
+[block/.style={rectangle,draw=black,text width=1.7cm,,align=center,
 decoration={shape sep=.1cm}}]
 
-\node[block, minimum height=20mm,minimum width=60mm, fill=fillColor!69!white,text=white] (apps1)  at (-5.1,0) {};
-\node[text width=6cm,align=center,text=white,font=\Large\bfseries\sf ] (text) at (-5.25,0.64)  {Stock Android Apps};
-\node[text width=6cm,align=center,text=white,font=\small\sf ] (text) at (-5.25,-0.34)  {Launcher   Phone  Alarm\\Email  Settings  Camera\\Gallery  Calendar ... };
+\node[block,minimum height=1cm,minimum width=4.8cm,fill=green,text width=4.8cm,align=center, font=\bfseries\sf ] (application) at
+(0cm,1.7cm) {Application Components};
 
-\node[block, minimum height=20mm,minimum width=60mm, fill=fillColor!69!white,text=white ] (apps2)  at (1.1,0) {};
-\node[text width=6cm,align=center,text=white, font=\Large\bfseries\sf ] (text) at (0.2,0)  {Custom/Market Apps};
+\path [draw,fill=grey ] (-3.8,-4) -- (-3.8,1.6) -- (-2.7,1.6) -- (-2.7,1) -- (2.7,1) -- (2.7,1.6) --  (3.8,1.6) -- (3.8,-4) --
+(-3.8,-4);
 
-\draw[style=dashed] (-8.5, -1.2) to (3.5,-1.2);
+\node[block, minimum height=1cm,minimum width=2cm,text width=2cm, font=\small\bfseries\sf,fill=white ] (am)  at (-2.5cm,-3.3cm)
+{JPF\_Activity Manager};
+\node[block, minimum height=1cm,minimum width=2cm,text width=2cm,font=\small\bfseries\sf,fill=white ] (mq)  at (0cm,-3.3cm) {JPF\_Message
+Queue};
+\node[block, minimum height=1cm,minimum width=2cm,text width=2cm, font=\small\bfseries\sf ,fill=white] (win)  at (2.5cm,-3.3cm)
+{JPF\_Window};
 
-\node[block, minimum height=20mm,minimum width=60mm, fill=fillColor!69!white,text=white] (apps1)  at (-5.1,-2.4) {};
+\draw[style=dashed,thick] (-5, -2.6) to (5,-2.6);
+\node[text width=6cm,align=center, font=\bfseries\sf ] (text1) at (4.3cm,-2.3)  {JPF};
+\node[text width=6cm,align=center, font=\bfseries\sf ] (text2) at (4.3cm,-2.9)  {MJI};
+
+ \node[block, minimum height=1cm,minimum width=2.7cm,font=\bfseries\sf,,fill=white] (MQ)  at (-2.25cm,-1.3) {Message Queue};
+\node[block, minimum height=1cm,minimum width=7.2cm,align=center, font=\large\bfseries\sf,fill=white ] (apps2)  at (0cm,0.3cm)
+{ActivityThread};
+% \draw[style=dashed] (-3.8,-1) to (3.8,-1);
+ \node[block, minimum height=1cm,minimum width=2.7cm, font=\small\bfseries\sf,fill=white ] (loop)  at (2.25cm,-1.3cm) {Looper};
+%  \node[block, minimum height=1cm,minimum width=2cm,text width=2cm, font=\small\bfseries\sf ] (apps2)  at (2.5cm,-1.9cm) {};
+
+\node[minimum width=1cm,text width=1cm, minimum height=1.4cm, cylinder, shape border rotate=90, draw, >=stealth,shape
+aspect=.2,fill=green, align=center] (database) 				at (0,-5) {Input\\ Script};
+
+\draw [->, thick] (win) to [ out=30, in= -10] (application)  ;
+\node[text width=3cm,align=center, font=\small\bfseries\sf ] (text) at (5,-1)  {\$button.onClick()};
+
+\draw [->,thick] (database) to (mq);
+
+\draw [->,thick] (mq) to (am);
+\draw [->,thick] (mq) to (win);
+\draw [->, thick] (am) to  [ out=180, in=180] (MQ);
+\draw [->, thick] (MQ) to (mq);
+\draw [->, thick] (loop) to (MQ);
+\draw [->, thick] (loop) to (apps2);
+\node[text width=3cm,align=center, font=\small\bfseries\sf ] (text) at (1.8cm,-0.5cm)  {handleLaunchActivity(...)};
+\node[text width=3cm,align=center, font=\small\bfseries\sf ] (text) at (-4,-2.3)  {scheduleLaunchActivity(...)};
+
+\node[text width=3cm,align=center, font=\small\bfseries\sf ] (text) at (0.5, -2.3)  {processScriptAction()};
+\node[text width=3cm,align=center, font=\small\bfseries\sf ] (text) at (0, -1.1)  {getNext()};
+
+\draw [->,thick] (apps2) to (application);
 
 \end{tikzpicture}
-\caption{Starlight web-based application architecture}
 \end{figure}

### 2012-08-07 Papers/paper.tex
updating files

@@
 \documentclass{acm_proc_article-sp}
-\usepackage{listings}
 \begin{document}
@@
 \author{%
+\alignauthor Heila van der Merwe\\
+       \affaddr{Dept. of Computer Science}\\
+       \affaddr{University of Stellenbosch}\\
+       \affaddr{Private Bag X1 Matieland}\\
+       \affaddr{South Africa, 7602}
+       \email{hvdmerwe@cs.sun.ac.za}
 \alignauthor  Brink van der Merwe\\
@@
        \email{abvdm@cs.sun.ac.za}
-\alignauthor Heila van der Merwe\\
-       \affaddr{Dept. of Computer Science}\\
-       \affaddr{University of Stellenbosch}\\
-       \affaddr{Private Bag X1 Matieland}\\
-       \affaddr{South Africa, 7602}
-       \email{hvdmerwe@cs.sun.ac.za}
 \alignauthor  Willem Visser\\
@@
 \begin{abstract}
-Mobile application testing is a specialized and complex field. Due to mobile applications' event driven design and mobile runtime environment,
-there currently exist only a small number of tools to verify these applications.
+Mobile application testing is a specialised and complex field. Due to mobile applications' event driven design and mobile runtime
+environment, there currently exist only a small number of tools to verify these applications.
 
@@
 in Android applications. The paper also provides an example of how to apply JPF-ANDROID to an application.
-\end{abstract}
+\end{abstract}ii
 
@@
 \section{Introduction}
-%Software testing and verification plays an important role in determining the quality and robustness of software. These are two very important attributes of 
-%mobile applications and can determine the success of the applications. Especially since there are more than 600 000 applications available on the Google play
-%market today. But, m
+Software testing and verification plays an important role in determining the quality and robustness of software. These are two very
+important attributes of mobile applications. Especially since users currently have more than 600 000 applications to choose from on the
+Google Play Market.
 
-Software testing is a crucial part of software development. It determines the quality and the user
-experience of software which are two very important aspects of Android applications. Especially for the high volume Android applications
-that are released yearly.
+Although application testing is so important, it is often neglected due to its complex and time consuming process. Android
+applications also face additional challenges when it comes to software testing.
 
-Although application testing is so important, it is often neglected as a result of its complex and time consuming process. Android
-applications also face additional challenges when it comes to software testing:
+Firstly, they have an event based design which means that their application flow is driven by graphical user interface (GUI) and system
+events.
 
-Firstly, Android applications are graphical user interface (GUI) based and their application flow is driven by GUI events. The
-simplest way to test GUI applications is manual black-box testing, but this is time consuming, error prone and
-expensive~\cite{AccessibilityTech}. Furthermore, user input is not the only factor that determines application flow. Android applications
-also receive input from system events. These include events such as battery low and network down warnings as well as ``start application'' and
-``stop application'' commands.
-
-Secondly, Android applications are developed in a custom implementation of Java Application Programming Interface (API)
- adopted from the Apache Harmony~\cite{harmony} project. The
-compiled applications can only be executed on a special virtual machine (VM) called the DalvikVM that runs on Android devices~\cite{dalvik}. 
-This means that Android applications can only execute on an device/emulator running the Android operating system. This makes testing very slow and
-difficult to automate.
+Secondly, Android applications are developed in a custom implementation of the Java Application Programming Interface (API)
+ adopted from the Apache Harmony~\cite{harmony} project. The compiled applications can only be executed on a special virtual machine (VM)
+called the Dalvik VM that runs on Android devices~\cite{dalvik}.
 
 Due to these challenges, the rapid pace at which applications are developed and the lack of testing tools available, mobile application
-testing becomes too expensive in terms of time and money. An important method to reduce this high cost, is to 
+testing becomes too expensive in terms of time and money.
+
+The simplest way to test GUI applications is manual black-box testing, but this is time consuming, error prone
+and expensive~\cite{AccessibilityTech}. One way to reduce this high cost, is to 
 automate the testing of GUI -- in this case Android -- applications~\cite{AccessibilityTech}.
 
-Currently, Android applications are tested automatically in one of two ways:
+Currently, Android applications can be tested automatically in one of two ways:
 
-The most common way to test Android applications is to use a physical device/emulator. Testing frameworks such as
-the MonkeyRunner~\cite{monkey} and Robotium~\cite{robotium} makes use of Android's built-in JUnit framework~\cite{TestingAndroid} to
-execute tests on the emulator/device. Other projects use alternative ways to automatically generate input by manipulating the built in
-accessibility technologies~\cite{AccessibilityTech} or by re-implementing the Android keyboard~\cite{KeyboardModel}. Mockito~\cite{mockito}
-and Android Mock~\cite{androidMock} allows JUnit testing on the DalvikVM by using a mocking architecture.
+The most common way is to run tests on the Dalvik VM of a physical device/emulator. Testing frameworks such as the MonkeyRunner and
+Robotium makes use of Android's built-in JUnit framework~\cite{TestingAndroid} to execute tests on the emulator/device. Other projects use
+alternative ways to automatically generate input by manipulating the built in accessibility technologies~\cite{AccessibilityTech} or by
+re-implementing the Android keyboard~\cite{KeyboardModel}. Mockito and Android Mock allow JUnit testing on the Dalvik VM by using  mock 
+Android classes.
 
-The advantage of testing application on the Dalvik VM is that the applications run on the actual Android operating system. The
-disadvantage is, as mentioned before, Android applications are driven by user and system events. So the input has to be modeled which is
-not simple to automate on a device/emulator. Moreover running test on the Dalvik VM is slow as they have to be instrumented and each test sequence has
-to be defined and executed one by one.
+The advantage of testing applications on the Dalvik VM is that Android applications are designed to run on an Android
+device and we can physically emulate the input events. The disadvantage is that it is not simple to automate input event emulation. Moreover
+running test on the Dalvik VM is slow as they have to be instrumented and each test sequence has to be defined and executed sequentially.
 
-The other approach is to test Android applications by using the Java Virtual Machine (JVM). There are different ways of implementing such a
-framework. Android
+The other approach is to test Android applications by using the Java Virtual Machine (JVM). There are different ways of implementing such
+a framework. Android
 lint~\cite{lint}, for example, makes use of static analysis to identify common errors in applications. Robolectric~\cite{robolectric}
-intercepts the loading of Android classes and then uses shadows classes that model these classes.
+intercepts the loading of Android classes and then uses shadows classes that model these classes to allow JUnit testing on the JVM.
 
-Although Android applications and Java desktop applications are designed for completely different Java virtual machines, they are both
+Although Android applications and Java desktop applications are designed for completely different Java VMs, they are both
 built on an implementation of the Java API. As a consequence, Android applications contain many of the
-same errors as Java applications. These defects include, but is not limited to, concurrency issues and common runtime exceptions such as NullPointer Exceptions. It follows that it
-is possible to adapt an existing Java testing framework to verify Android applications.
+same errors as Java applications. These defects include, but are not limited to, concurrency issues and common runtime exceptions such as
+NullPointer Exceptions. It follows that existing Java testing frameworks can be adapted to verify Android applications.
 
 % what are we going to do and why 
-This paper describes an extension to Java PathFinder (JPF)~\cite{JPFDocs} that enables the automatic
-verification of Android Applications on the standard Java JVM.
+This paper describes an extension to Java PathFinder (JPF)~\cite{JPFDocs} that enables the automatic verification of Android applications on
+the standard Java JVM.
 
-This paper will first provide an overview of JPF and how it can be used to test Android applications. Thereafter a description of the
-development of the JPF-ANDROID tool is provided, followed by a simple example to show how the tool works.
+The next section will provide an overview of JPF and Android and how JPF can be used to test Android applications. Thereafter
+the development of the JPF-ANDROID tool will be discussed, followed by a simple example to show how the tool works.
 
@@
 \subsection{Java PathFinder}
-JPF is an automated open source analysis engine for Java applications~\cite{JPFDocs}. It is implemented as explicit state model checker
-that includes mechanisms to model Java classes, model native method calls (MJI), track byte code execution and listen for
-property violations. Additionally, JPF's design encourages developers to create extensions to the framework. Currently there exists many
-extensions including a symbolic execution extension (JPF-SYMB), data race
-detector (JPF-RACEFINDER) and an abstract window toolkit (AWT) extension (JPF-AWT).
+JPF is an automated, open source, analysis engine for Java applications~\cite{JPFDocs}. It is implemented as an explicit state model checker
+that includes mechanisms to model Java classes and native method calls (Model Java Interface - MJI Environment), track byte code execution
+and
+listen for property violations. Additionally, JPF's design encourages developers to create extensions to the framework. Currently there
+exist many
+extensions including a symbolic execution extension (JPF-SYMBC)~\cite{JPF-SYMB}, data race
+detector (JPF-RACEFINDER) and an abstract window toolkit (AWT) extension (JPF-AWT)~\cite{JPF-AWT}.
 
-The JPF Android extension (JPF-ANDROID) will use JPF's extension mechanisms to:
+The JPF-ANDROID will use JPF's extension mechanisms to:
 \begin{enumerate}
 \item model the Android application framework so that Android applications can run on the JVM,
-\item create an input model to simulate user and system input to the application.
+\item create an input model to simulate user and system input to drive the application flow.
 \end{enumerate}
@@
 One of the advantages of extending JPF is that it has been rigorously tested and can successfully detect many common defects in Java applications. As soon as
-Android applications can run on JPF-ANDROID, common software errors such as null pointer exceptions, assertion violations, deadlocks and
-race-conditions will automatically be detected.
+Android applications can run on JPF-ANDROID, common software errors are automatically detected.
 
-The first step in modeling the android framework is to understand its architecture.
+The first step in modelling the Android framework is to understand its architecture.
 
 \subsection{Android}
-Android is an open source software stack for mobile devices such as smartphones with an advanced RISC Machine (ARM) architecture (Figure 1).
+Android is an open source software stack for devices with an advanced RISC Machine (ARM) architecture  such as smartphones.
 It consists of the Android operating system (OS), the application framework and an application development toolkit assisting developers to create
-applications for the platform~\cite{AndroidDocs}.
+applications for the platform~\cite{AndroidDocs}(see Figure 1~\cite{systemserver}).
 
 The Android OS is built on top of a modified Linux kernel. It provides a layer of abstraction on top of its low level functionality such as process,
-memory, user, network and thread management. On top of the Android kernel is a set of native libraries including a custom, optimised version of the
-JVM called the Dalvik VM.
+memory, user, network and thread management. On top of the Android kernel is a set of native libraries. A custom, optimised
+version of the JVM called the Dalvik VM is built on these native libraries.
 
-For security reasons every Android application is run as a separate process in its own Dalvik VM instance. Hence, applications can only
-communicate with each other and the with the Android framework using Android's Binder inter-process communication (IPC) mechanism.
+For security reasons every Android application is run as a separate process in its own Dalvik VM instance~\cite{AndroidSecurity}. Hence, applications can only
+communicate with each other and the with the Android framework using Android's Binder inter-process communication (IPC)
+mechanism~\cite{Binder}.
 
@@
 \centering
-\epsfig{file=stack.eps, width=3in,}
+\epsfig{file=Stack.eps, width=3in,}
 \caption{The Android application stack}
@@
 The main Android application is called the system process. The system process contains services responsible for running the main tasks of the system for example:
-\begin{itemize}
- \item activity manager -- manages the life-cycle and interaction of all the activities running on the system
- \item window manager -- allows applications to draw on the screen
- \item package manager -- stores information on the application packages installed on the device
-\end{itemize}
+\begin{description}
+ \item [ActivityManager] manages the life-cycle and interaction of all the activities running on the system
+ \item [WindowManager] allows applications to draw on the screen and forwards UI input to the application.
+ \item [PackageManager] stores information on the application packages installed on the device
+\end{description}
 
@@
 commonly used by many UI frameworks since it becomes too complex to make all UI classes thread safe~\cite{SingleThread}. For Android, this main thread is called
-the \texttt{Looper}. The \texttt{Looper} and has a message queue attach to it containing application events to be handled. When UI events are fired, they
-are added to the \texttt{Looper}'s message queue. System events are also scheduled on the main \texttt{Looper} by adding them to the message
+the \texttt{Looper}. The \texttt{Looper} has a message queue attached to it containing application events to be dispatched. UI and system
+events are scheduled on the main \texttt{Looper} by adding them to the message
 queue. The \texttt{Looper} is responsible for continuously looping through these messages and handling them appropriately. This could
-include updating a widget, loading a new activity or processing an intent.
-
-\begin{figure}
-\centering
-\epsfig{file=app.eps, width=3in,}
-\caption{The Android structure}
-\end{figure}
+include updating a widget, loading a new activity or processing an Intent.
 
@@
 following application components:
-\begin{itemize}
-\item Activities -- responsible for representing and managing an user interface. An application can consist of many
+\begin{description}
+\item [Activity] responsible for representing and managing an user interface. An application can consist of many
 Activities.
-\item Services -- performs background operations such as the pulling of messages from a server every 5 minutes. Services do not have user
+\item [Service] performs background operations such as the pulling of messages from a server every 5 minutes. Services do not have user
 interfaces and an application can have zero or more services running simultaneously.
-\item Broadcast receivers -- listens for and responds to system-wide events such as network failing, low battery or screen orientation
+\item [Broadcast receiver] listens for and responds to system-wide events such as network failing, low battery or screen orientation
 change events.
-\item Content providers -- manages application data stored on the file system, in databases, on the web or other storage medium and provides
-a gateway to this data from other applications.
-\end{itemize}
+\item [Content provider] manages application data stored on the file system, in databases, on the web or other storage medium and provides a
+gateway to this data from other applications.
+\end{description}
 
-These components are created and managed by the \texttt{ActivityThread}.They interact with each other and with other
+These components are created and managed by the \texttt{ActivityManager}. They interact with each other and with other
 applications using a structure called an \texttt{Intent}. An \texttt{Intent} is a high level implementation of the Binder IPC.
@@
 \subsection{Scope of JPF-ANDROID}
-The Android platform is very large and one of the main challenges is to decide which parts of the system to model. The objective of
-JPF-ANDROID is to verify Android applications by running the code using a collection of event sequences and then to detect when errors appear.
+The Android framework is very large and one of the main challenges of JPF-ANDROID is to decide which parts of the system to model. The
+objective of JPF-ANDROID is to verify Android applications by executing the code using a collection of different event sequences and then to
+detect when certain errors occur.
 
-The more the Android framework gets modeled, the more realistic the model is and the more errors can be found. But, the more of the Android framework
-get modeled, the more scheduling possibilities can occur and the search space becomes to big. Additionally, the more of the framework is modelled, 
-the more has to be re-modelled when the architecture changes.
+The more of the Android framework is modelled, the more realistic the model is and the more errors can be found. But, if too much
+of the framework is modelled the scheduling possibilities increase exponentially which means that the search space can become too big to
+verify.
 
 JPF-ANDROID will focus on verifying one application with multiple application components and their interaction. The system service of the Android OS
-is not run in the application process and runs in its own thread. To reduce scheduling possibilities we will not model the entire system service,
-but implement the necessary tasks as part of the application process.
+is not part of the application process and runs in its own thread. To reduce scheduling possibilities we will not model the entire system
+service, but implement the necessary tasks as part of the application process.
 
-The following parts of the Android framework will be modeled:
+The following parts of the Android framework will be modelled:
 \begin{description}
- \item [Activity manager] - modeled to manages the lifecycle of Activities and other application components.
- \item [Activity thread] - modeled to manage the application components and their input.
- \item [Application components] - including Activity, Service, Broadcast Receiver and Content Provider. 
- \item [Window and View structure] - The view hierachy will be modeled including the widgets and the sindow classes.
- \item [Message queue] - The message queue will be modeled to support input from the script file.
+ \item [ActivityManager] will manage the life-cycle of Activities and other application components.
+ \item [ActivityThread]  will manage the application components and their input.
+ \item [Application components] including Activity, Service, Broadcast Receiver and Content Provider. 
+ \item [Window and View structure] The view hierarchy will be modelled including the widgets and the window classes.
+ \item [Message queue] - The message queue will be modelled to support input from the script file.
 \end{description}
 
-Lastly, as the application will not be communicating with outside processes, the Binder IPC will not be modelled.
-The components will communicate with each other by sending direct references to themselves.
+Lastly, as the application will not be communicating with outside processes, the \texttt{Intent} objects will be modelled to exclude the
+Binder IPC service.
 
 \section{Development}
-At the basis of the tool's modelled framework are the message queue, the view structure and the activity manager. These components will be
-discussed in greater detail below:
+JPF-AWT introduced the idea of using a simple script file to write event sequences as input to an application. This scripting mechanism makes use of
+JPF's state matching and backtracking features to support non-deterministic elements such as the \texttt{ANY} and \texttt{REPEAT}
+structures. These structures make it simpler to specify many input sequences simultaneously. As both Android and AWT have a single-threaded
+UI design, JPF-ANDROID is built on the design of JPF-AWT. There are two challenges to using this approach:
+\begin{enumerate}
+ \item Android applications receive input from two different sources: user input and system input where AWT applications only receive user input.
+ \item Android applications contain multiple windows - one for each Activity. This complicates the UI input as each
+window has its own unique set of view components, hence, a unique input sequence.
+\end{enumerate}
 
-As shown in Figure 2, all input events of the system are placed in the message queue and then processed by the \texttt{Looper}. Hence,
-JPF-ANDROID needed a way to place events in this queue. JPF-AWT introduced the idea of using a simple script to write event sequences as
-input for the application. This scripting mechanism made use of JPF's state backtracking feature to support elements such as the ANY and
-REPEAT structures to make it simpler to specify many input sequences simultaneously. Each time the message queue is empty an event is
-read from the script file. As Android and AWT both use a single-threaded UI design, JPF-ANDROID could build on the idea of scripting input events.
-
-%There were two
-%challenges to using this approach in JPF-ANDROID:
-%\begin{enumerate}
-% \item Android applications other that AWT applications receive input from two different
-%sources: user input from the UI, and system input from the activity manager through Intents. 
-% \item Android applications contain multiple windows - one for each Activity. This complicates the UI input as each
-%window has its own unique set of view components - thus a unique input sequence.
-%\end{enumerate}
-%These challenges were addressed by expanded the scripting feature in a few ways:
-
-\subsection{The input model}
+\subsection{The JPF-ANDROID input model}
 \begin{figure}
 \centering
-\epsfig{file=arch.eps, width=3in,}
+\epsfig{file=arch.eps, width=3.5in,}
 \caption{JPF-ANDROID architecture}
@@
 
-JPF-ANDROID classifies input events as either UI events or system events. UI events are handled similar to
-how they were handled in JPF-AWT. When the activity's UI is inflated, an object map is built binding the name of a view component (widget)
-to the inflated widget. When an UI event occurs the name of the target view component is looked-up in the object map
-and then the action is called on the actual view object.
+Figure 2 shows JPF-ANDROID's architecture. JPF-ANDROID models Android's message queue structure by using JPF's MJI environment. When the
+\texttt{Looper} requests a new message from the 
+message queue and it is empty, a call to the native \texttt{JPF\_MessageQueue} class is made. This class reads the next event from the
+input script file and classifies it as either a UI event or system event.
 
-An Intent-object are is to describe system events. Intents are used to start Activities
-and Services or to provide a notification of certain events. They are similar to messages containing a description of an operation to be
-performed or, often in the case of broadcasts, a description of something that has happened and is being announced. The are two types of
-Intents:
-\begin{itemize}
- \item explicit intents -- explicitly store the name of the component to start
- \item implicit intents -- store the details of a event that occurred these details are then used to lookup components that are registered
-for such events. Component's register for intents in the AndroidManifest file. Now to resolve the component to which the intent is sent an
-the ActivityManager has to parse the AndroidManifest file. This file contains the the list of Intent filters for each
-Application component. 
-\end{itemize}
+UI events are directed to and handled by the native \texttt{JPF\_Window} class. When an Activity's window is inflated, an object map
+is created in this native window class. This map binds the name of a widget to the reference of the inflated widget object.
+When an UI event is received, the name of the target widget is looked-up in the object map. The action is then called directly on the
+inflated widget object by pushing a direct call frame on the JPF call stack.
 
-But the ActivityManager requires information about which component to send the intent to: an Activity, Service or Receiver. In the Android
-code
-an Intent is sent by calling one of the methods \texttt{startActivity(Intent), startService(Intent), sendBroadcast(Intent)}. Usually this
-request is sent to the activity manager where it is handled appropriately. But as we are not modelling the
-ActivityManger, the Intent is handled by a local, small model of the ActivityManager. The Activity Manager then resolves the intent to the
-appropriate application and then forwards the intent to the application's ActivityThread to be processed.
+System events are a little more complex. They use \texttt{Intent} objects to describe a system event. \texttt{Intents} are used to start
+Activities and Services or to provide a notification of certain events. They are similar to messages containing a
+description of an operation to be performed or, often in the case of broadcasts, a description of something that has happened and is being
+announced~\cite{AndroidDocs}.
 
-To allow a user to script system events, variables were added to the scripting language. Variable names will be identified by
-the '@' in front of the name as '\$' is already used in jpf-awt to identify UI components:
+System events are handled by the \texttt{ActivityManager} implemented as the native \texttt{JPF\_ActivityManager} class. The
+\texttt{ActivityManager} needs to know which component to send the Intent to: an Activity, Service or Receiver. In an Android
+application this information is conveyed by calling one of the following methods: \texttt{startActivity(Intent), startService(Intent),
+sendBroadcast(Intent)} from the code. This request is sent to the \texttt{ActivityManager} where it is 
+handled appropriately. The  \texttt{ActivityManager} resolves the Intent to the appropriate component and then
+schedules the \texttt{Intent} on the application's  message queue. This message will be processed by the \texttt{Looper} which will direct
+the event to the \texttt{ActivityThread} to be handled.
 
-The script file that send an intent to start the \texttt{SampleActivity} will look like:
-\begin{figure}
+To allow a user to script system events, variables were added to the scripting language. Variable names are identified by
+the ``@'' in front of the name as '\$' is already used in JPF-AWT to identify UI components. For example a script file that sends an
+\texttt{Intent} to start the \texttt{SampleActivity} will contain:
+
 {\small
 {\sf
-@intent1.setComponent(``SampleActivity'')\\
-startActivity(@intent1)\\
-\$button1.onClick()
+\hspace*{4mm}@intent1.setComponent(``com.example.SampleActivity'')\\
+\hspace*{4mm}startActivity(@intent1)\\
+\hspace*{4mm}\$button1.onClick()
+
 }
 }
-\caption{Starting an Activity}
-\end{figure}
 
 \subsection{The input sequence}
-JPF-ANDROID started out by using a sequential input script that drove the application execution. This became an issue when some of the
+JPF-ANDROID started out by using a sequential input script to drive the application execution. This became a problem when some of the
 input events were non-deterministically scheduled to happen. In other words, if we do not know whether an event took place or
-not, we can not schedule following events. Hence, the scriptwriter has to have knowledge of the system and
-know which button press fires what activities. There could in be non-determinism in term of events but not in terms of starting
-activities/services. This is because if an Activity is started, the following events in the script must be related to the new Activity.
+not, we can not schedule the following events. Lets look at an example:
 
-Lets look at an example:
 \begin{figure}
@@
 \epsfig{file=newContact.eps, width=1in,}
-\caption{Adding a new contact screen}
+\caption{Contacts application windows}
 \end{figure}
 
-This is the Create new contact screen of a phonebook application. At the bottom of the screen there are three buttons. The cancel button
-returns to the previous screen, the clear button stays on the current screen and the create button forwards to a new screen. Noe  let us
-look at the following input script:
+Figure 3 displays the ``Add Contact'' window of a Contacts application. It contains three
+buttons: the back button starts the \texttt{ContactsListActivity}, the clear button stays on the current Activity and the create 
+button starts the \texttt{ViewContactActivity}. Now let us look at Figure 4 containing the input sequence for the ``Add Contact'' window.
 
@@
 \\
-\textbf{REPEAT} 3 \{\\
-\textbf{ANY} \{backButton.onclick(),clearButton.onClick(),addButton.onClick()\}\\
-\}
-
-nameEdit.setText(``Mary'')
+\textbf{REPEAT} 2 \{\\
+\hspace*{2mm}\textbf{ANY} \{ \$backButton.onclick(), \$clearButton.onClick()  \}
+\}\\
+\$nameEdit.setText(``Mary'')\\
+\$addButton.onClick() 
 }
 }
-\caption{Starting an Activity}
+\caption{Non-deterministically starting an Activity}
 \end{figure}
 
-This script file will execute 3 event sequences:
+This input sequence describes 2 event sequences:
 \begin{enumerate}
@@
 press clearButton\\
-set name edit's text
+set name edit's text\\
+press addButton
  \item start AddContactActivity\\
- press addButton button, \\
- set name edit's text
- \item start AddContactActivity\\
- press homeButton button, \\
- set name edit's text
+ press backButton button, \\
+ set name edit's text\\
+ press addButton
 \end{enumerate}
 
-The problem is that only after the clear button is pressed is the nameEdit.setText(`` Mary'') command valid as we do not know if the other
-screens contain textboxes.
-
-Android applications have many Activities, each with a unique interface. At any time, the system or the UI can fire an event to start a new
-Activity. The problem is as this is a nondeterministic chance the the input file can not run sequential. So that when an Activity is
-started, JPF-ANDROID can go and look up what are the event sequences that can be performed on the activity.
-
-To address this issue, we adopted the input script to be divided into sections. Each section list the sequential input to an specific
-Activity:
+The problem is that only after the clear button is pressed is the \texttt{\$nameEdit.setText} command valid. As we do not know
+which window is visible after the button press event, we can not use a sequential script. To address this issue, we included the use of
+sections in the input script (see figure 5). Each section lists the sequential input of a specific Activity.
 
@@
 {\sf 
-@startIntent.setComponent(``com.example.ListContactsActivity'')
+\textbf{SECTION} default \{\\
+\hspace*{5mm}@startIntent.setComponent(``com.example.ListContactsActivity'')\\
+\hspace*{5mm}startActivity(@startIntent)\\
+\}
 
-\textbf{TARGET:} start\\
-startActivity(@startIntent)\\
+\textbf{SECTION} com.example.ListContactsActivity \{\\
+\hspace*{5mm}\$addButton.onClick()\\
+\hspace*{5mm}\$list.setSelectedIndex([0-3])\\
+\}\\
 
-\textbf{TARGET:} com.example.ListContactsActivity\\
-listbox.select<0-N> \#starts ViewActivity\\
-
-\textbf{TARGET:} com.example.ViewContactActivity\\
-backButton.onClick() \# restarts ListContactsActivity, \\
-
+\textbf{SECTION} com.example.AddContactActivity \{\\
+\hspace*{5mm}\textbf{REPEAT} 2 \{\\
+\hspace*{7mm}\textbf{ANY} \{ \$backButton.onclick(), \$clearButton.onClick()  \}
+\hspace*{5mm}\}\\
+\hspace*{5mm}\$nameEdit.setText(``Mary'')\\
+\hspace*{5mm}\$addButton.onClick()\\
+\}
 }
 }
-\caption{Starting an Activity}
-\end{figure}
-so how do we know not to run sequence again other wise infinite loop?
-
-The next challenge 
--  returning to an activity don't wan to execute sequence again example contacts list contact - view contact - list contact
-
-\begin{figure}
-{\small
-{\sf 
-TARGET: start\\
-  startActivity(ListContactsActivity)
-
-TARGET: com.example.ListContactsActivity\\
-  listbox.select<0-N> \#starts ViewActivity
-
-TARGET: com.example.ViewContactActivity\\
-   backButton.onClick() \# restarts ListContactsActivity, 
-}
-}
-\caption{Starting an Activity}
+\caption{Adding sections to the input script}
 \end{figure}
 
-The question is how do we then backtrack the case where an activity was started?
+Now, if the back button is pressed the \texttt{ListContactsActivity} will be started and then \texttt{ListContactsActivity}'s event sequence
+will execute.
 
-All state that is stored in the JPF side will be backtracked automatically, but we are not on the JPF side. We have to know when an
-activity is started as a backtrack or as a new start.
+The next challenge is to avoid an infinite loop when returning to an Activity. For example if the back button is pressed on the
+\texttt{AddContactActivity} we return to the \texttt{ListContactsActivity}, but, we do not want to repeat the action of pressing on the
+addButton again, we want to continue executing the next events. In other words we have to determine when an Activity's event sequence has to
+be continued or restarted. We are currently working on this issue.
 
-entrypoint 
-\newpage
 \section{Case Study}
 % example showing the detection of a null pointer exception in certain case
+We assume that JPF-CORE and JPF-ANDROID has been downloaded and build in eclipse. To verify an Android application using JPF-ANDROID we
+require the source code of the project. In the ``src'' package of the project a script 
+file has to be  created including the input events like in figure 6. Also in the ``src'' package has to be a .jpf file that
+includes the project setup. Lastly we need to include a stub main method so that JPF-ANDROID has an entry point to the application.
 
-\section{Discussion}
-%discussion showing how the tool is successful and the advantages of the tool
+\begin{verbatim}
+	/**
+	 * The main entry point to the application
+	 * 
+	 * @param args
+	 */
+	public static void main(String[] args) {
+		  ActivityThread.main(null);
+	}
+\end{verbatim}
 
-limitations
-- only 1 application
-- no android native code can be handled
+The ViewContactActivity requires an argument containing the contact to view. In this application we did not attach this information to
+the starting intent for ViewContactActivity. A null pointer exception occurs when we try to retrieve this value in the ViewContactActivity
+and is detected by JPF.
 
 \section{Conclusion}
+The paper discussed the design and implementation of JPF-ANDROID. JPF-ANDROID is still under development and currently only models
+the core libraries needed to verify a basic Android application. It allows Android applications to be tested using JPF's proven verification
+techniques and can successfully detect common Java errors such as runtime exceptions and deadlocks.
 
-\section{Acknowledgements}
-
+This extension provides a basis on which Android applications can be tested. It can later be extended to verify functional requirements
+and identify Android specific errors using JPF's listener mechanism.
+\balancecolumns
 %
@@
 \bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
-% 
+
 \end{document}

### 2012-08-07 jpf-android/src/classes/android/os/Looper.java

@@ -1,6 +1,5 @@
 package android.os;
 
-import android.util.PrefixPrinter;
 import android.util.Printer;
 
 /**
@@ -169,23 +168,23 @@ public class Looper {
 	}
 
 	public void dump(Printer pw, String prefix) {
-		pw = PrefixPrinter.create(pw, prefix);
-		pw.println(this.toString());
-		pw.println("mRun=" + mRun);
-		pw.println("mThread=" + mThread);
-		pw.println("mQueue=" + ((mQueue != null) ? mQueue : "(null"));
-		if (mQueue != null) {
-			synchronized (mQueue) {
-				long now = SystemClock.uptimeMillis();
-				Message msg = null;
-				int i = 0;
-				for (; i < mQueue.getSize(); i++) {
-					msg = mQueue.getMessage(i);
-					pw.println("  Message " + i + ": " + msg.toString(now));
-				}
-				pw.println("(Total messages: " + (i + 1) + ")");
-			}
-		}
+//		pw = PrefixPrinter.create(pw, prefix);
+//		pw.println(this.toString());
+//		pw.println("mRun=" + mRun);
+//		pw.println("mThread=" + mThread);
+//		pw.println("mQueue=" + ((mQueue != null) ? mQueue : "(null"));
+//		if (mQueue != null) {
+//			synchronized (mQueue) {
+//				long now = SystemClock.uptimeMillis();
+//				Message msg = null;
+//				int i = 0;
+//				for (; i < mQueue.getSize(); i++) {
+//					msg = mQueue.getMessage(i);
+//					pw.println("  Message " + i + ": " + msg.toString(now));
+//				}
+//				pw.println("(Total messages: " + (i + 1) + ")");
+//			}
+//		}
 	}
 
 	public String toString() {

### 2012-08-07 jpf-android/src/classes/android/view/View.java

@@ -277,7 +277,6 @@ public class View {
 	 *         otherwise is returned.
 	 */
 	public void onClick() {
-		System.out.println("############################# onclick");
 		OnClickListener li = getOnClickListener();
 		if (li != null) {
 			li.onClick(this);

### 2012-08-07 jpf-android/src/classes/android/widget/TextView.java

@@ -1,13 +1,0 @@
-package android.widget;
-
-import android.content.Context;
-import android.view.View;
-
-public class TextView extends View {
-
-	public TextView(Context context) {
-		super(context);
-		// TODO Auto-generated constructor stub
-	}
-
-}

### 2012-08-07 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_os_MessageQueue.java

@@ -104,7 +104,7 @@ public class JPF_android_os_MessageQueue {
 					if (forceActionStates) {
 						env.setIntField(objref, "forceNewState", counter);
 					}
-
+					System.out.println("setting next cg: " + cg);
 					ss.setNextChoiceGenerator(cg);
 					// ti.skipInstructionLogging();
 					// System.out.println("ProcessAction " + cg.toString());
@@ -112,6 +112,8 @@ public class JPF_android_os_MessageQueue {
 					env.repeatInvocation();
 					return true; // doesn't really matter
 				} else {
+					System.out.println("setting next cg: false");
+
 					return false;
 				}
 
@@ -119,10 +121,14 @@ public class JPF_android_os_MessageQueue {
 						// left), retrieve it
 				UIActionGenerator cg = ss.getCurrentChoiceGenerator(
 						"processScriptAction", UIActionGenerator.class);
-				assert (cg != null) : "no UIActionGenerator";
-				// System.out.println("processing UIAction: " + cg);
+				
+				
 
-				runAction(env, cg.getNextChoice());
+				assert (cg != null) : "no UIActionGenerator";
+				System.out.println("processing UIAction: " + cg);
+				UIAction ac =  cg.getNextChoice();
+				System.out.println("Next choice : " + ac);
+				runAction(env, ac);
 				env.repeatInvocation();
 
 			}
@@ -150,7 +156,6 @@ public class JPF_android_os_MessageQueue {
 	}
 
 	private static void handleViewAction(MJIEnv env, UIAction action) {
-		System.out.println("#######" + action.toString());
 		int tgtRef = JPF_android_view_Window.getViewRef(action.getTarget());
 		if (tgtRef == MJIEnv.NULL) {
 			log.warning("no view found for UIAction: " + action);

### 2012-09-01 Papers/paper.tex
Updating JPF-Android Workshop paper

@@
 the user to script input events to drive the application flow. JPF-ANDROID provides a way to detect common property violations such as deadlocks and runtime exceptions
-in Android applications. The paper also provides an example of how to apply JPF-ANDROID to an application.
-\end{abstract}ii
+in Android applications.
+\end{abstract}
 
@@
 
-Although application testing is so important, it is often neglected due to its complex and time consuming process. Android
-applications also face additional challenges when it comes to software testing.
+Although software testing is so important, it is often neglected due to its complex and time consuming process. Android
+applications face additional challenges when it comes to application testing. Firstly, they have an event based design which means that
+their application flow is driven by graphical user interface (GUI) and system events. Secondly, Android applications are developed in a
+custom implementation of the Java Application Programming Interface (API)  adopted from the Apache Harmony~\cite{harmony} project. The
+compiled applications can only be executed on a special virtual machine (VM) called the Dalvik VM that runs on Android
+devices~\cite{dalvik}.
 
-Firstly, they have an event based design which means that their application flow is driven by graphical user interface (GUI) and system
-events.
+Due to these challenges, the rapid pace at which mobile applications are developed and the lack of testing tools available, mobile
+application testing is often omitted altogether. The simplest way to test GUI applications is manual black-box testing.
+But, this is a time consuming, error prone and expensive~\cite{AccessibilityTech} process. One way to reduce this high cost, is to  automate
+the testing of GUI -- in this case Android -- applications~\cite{AccessibilityTech}.
 
-Secondly, Android applications are developed in a custom implementation of the Java Application Programming Interface (API)
- adopted from the Apache Harmony~\cite{harmony} project. The compiled applications can only be executed on a special virtual machine (VM)
-called the Dalvik VM that runs on Android devices~\cite{dalvik}.
+The most common way to automate Android application testing is to run tests on the Dalvik VM on a
+physical device/emulator. Testing frameworks such as the MonkeyRunner and Robotium make use of Android's built-in JUnit
+framework~\cite{TestingAndroid} to run test suites on the device. Running tests on the Dalvik VM is slow as they have to be instrumented and
+each test sequence has to be defined and executed sequentially. Other projects use alternative ways to automatically generate input by
+manipulating the built in accessibility technologies~\cite{AccessibilityTech} or by re-implementing the Android
+keyboard~\cite{KeyboardModel}. Mockito and Android Mock allow JUnit testing on the Dalvik VM by using mock Android classes. The advantage of
+testing applications on the Dalvik VM is that we can physically emulate input events on the device. The disadvantage is that it is not
+simple to automate this input emulation.
 
-Due to these challenges, the rapid pace at which applications are developed and the lack of testing tools available, mobile application
-testing becomes too expensive in terms of time and money.
+Another approach is to test Android applications using the Java Virtual Machine (JVM). There are different ways of implementing such
+a framework. Android lint~\cite{lint}, for example, makes use of static analysis to identify common errors in applications.
+Robolectric~\cite{robolectric}, a JUnit testing framework running on the JVM,  intercepts the loading of Android classes and then uses
+shadows classes that model these classes.
 
-The simplest way to test GUI applications is manual black-box testing, but this is time consuming, error prone
-and expensive~\cite{AccessibilityTech}. One way to reduce this high cost, is to 
-automate the testing of GUI -- in this case Android -- applications~\cite{AccessibilityTech}.
-
-Currently, Android applications can be tested automatically in one of two ways:
-
-The most common way is to run tests on the Dalvik VM of a physical device/emulator. Testing frameworks such as the MonkeyRunner and
-Robotium makes use of Android's built-in JUnit framework~\cite{TestingAndroid} to execute tests on the emulator/device. Other projects use
-alternative ways to automatically generate input by manipulating the built in accessibility technologies~\cite{AccessibilityTech} or by
-re-implementing the Android keyboard~\cite{KeyboardModel}. Mockito and Android Mock allow JUnit testing on the Dalvik VM by using  mock 
-Android classes.
-
-The advantage of testing applications on the Dalvik VM is that Android applications are designed to run on an Android
-device and we can physically emulate the input events. The disadvantage is that it is not simple to automate input event emulation. Moreover
-running test on the Dalvik VM is slow as they have to be instrumented and each test sequence has to be defined and executed sequentially.
-
-The other approach is to test Android applications by using the Java Virtual Machine (JVM). There are different ways of implementing such
-a framework. Android
-lint~\cite{lint}, for example, makes use of static analysis to identify common errors in applications. Robolectric~\cite{robolectric}
-intercepts the loading of Android classes and then uses shadows classes that model these classes to allow JUnit testing on the JVM.
-
-Although Android applications and Java desktop applications are designed for completely different Java VMs, they are both
-built on an implementation of the Java API. As a consequence, Android applications contain many of the
-same errors as Java applications. These defects include, but are not limited to, concurrency issues and common runtime exceptions such as
-NullPointer Exceptions. It follows that existing Java testing frameworks can be adapted to verify Android applications.
+Although Android applications and Java desktop applications are designed for completely different Java VMs, they are both built on an
+implementation of the Java API. As a consequence, Android applications contain many of the same error as Java applications. These defects
+include, but are not limited to, concurrency issues and common runtime exceptions such as NullPointer Exceptions. It follows that existing
+Java testing frameworks can be adapted to verify Android applications.
 
@@
 The next section will provide an overview of JPF and Android and how JPF can be used to test Android applications. Thereafter
-the development of the JPF-ANDROID tool will be discussed, followed by a simple example to show how the tool works.
+the development of the JPF-ANDROID tool will be discussed.
 
@@
 that includes mechanisms to model Java classes and native method calls (Model Java Interface - MJI Environment), track byte code execution
-and
-listen for property violations. Additionally, JPF's design encourages developers to create extensions to the framework. Currently there
-exist many
-extensions including a symbolic execution extension (JPF-SYMBC)~\cite{JPF-SYMB}, data race
+and listen for property violations. Additionally, JPF's design encourages developers to create extensions to the framework. Currently there
+exist many extensions including a symbolic execution extension (JPF-SYMBC)~\cite{JPF-SYMB}, data race
 detector (JPF-RACEFINDER) and an abstract window toolkit (AWT) extension (JPF-AWT)~\cite{JPF-AWT}.
 
-The JPF-ANDROID will use JPF's extension mechanisms to:
-\begin{enumerate}
-\item model the Android application framework so that Android applications can run on the JVM,
-\item create an input model to simulate user and system input to drive the application flow.
-\end{enumerate}
+JPF-AWT allows the model checking of AWT applications. AWT applications are event driven and based on a single
+threaded, message queue design. All application events are put in a message queue and then handled by the main thread of the application,
+called the EventDispatchThread. JPF-AWT introduced the idea of using a simple event script file to write sequences of user inputs to drive
+the application execution. JPF-AWT models the EventDispatchThread so that when the message queue is empty, it requests an event from the
+script file simulating the event occurring.
 
-One of the advantages of extending JPF is that it has been rigorously tested and can successfully detect many common defects in Java applications. As soon as
-Android applications can run on JPF-ANDROID, common software errors are automatically detected.
-
-The first step in modelling the Android framework is to understand its architecture.
+JPF-ANDROID makes use of JPF's extension mechanisms to model the Android application framework so that Android applications can run on the
+JVM. It then extends JPF-AWT's input model to simulate user and system input to drive the application flow. One of the advantages of
+extending JPF is that it has been rigorously tested and can successfully detect many common defects in Java applications. As soon as Android
+applications can run on JPF-ANDROID, common software errors are automatically detected.
 
 \subsection{Android}
-Android is an open source software stack for devices with an advanced RISC Machine (ARM) architecture  such as smartphones.
+Android is an open source software stack for devices with an advanced RISC Machine (ARM) architecture.
 It consists of the Android operating system (OS), the application framework and an application development toolkit assisting developers to create
-applications for the platform~\cite{AndroidDocs}(see Figure 1~\cite{systemserver}).
+applications for the platform~\cite{AndroidDocs}.
 
-The Android OS is built on top of a modified Linux kernel. It provides a layer of abstraction on top of its low level functionality such as process,
-memory, user, network and thread management. On top of the Android kernel is a set of native libraries. A custom, optimised
-version of the JVM called the Dalvik VM is built on these native libraries.
-
-For security reasons every Android application is run as a separate process in its own Dalvik VM instance~\cite{AndroidSecurity}. Hence, applications can only
-communicate with each other and the with the Android framework using Android's Binder inter-process communication (IPC)
-mechanism~\cite{Binder}.
+As shown in figure 1, the Android OS is built on top of a modified Linux kernel. The kernel provides a layer of abstraction on top of its
+low level functionality such as process, memory, user, network and thread management. On top of the Android kernel is a set of native
+C-libraries. The Dalvik VM is a custom, optimised version of the JVM. For security reasons each Android application is run as a separate
+process in its own Dalvik VM instance~\cite{AndroidSecurity}.  Hence, applications can only communicate with each other and the with the
+Android framework using Android's Binder inter-process communication (IPC) mechanism~\cite{Binder}.
 
@@
 \epsfig{file=Stack.eps, width=3in,}
-\caption{The Android application stack}
+\caption{The Android application stack~\cite{systemserver}}
 \end{figure}
 
-The main Android application is called the system process. The system process contains services responsible for running the main tasks of the system for example:
+Android has one main application called the system process. The system process contains services responsible for performing the main
+tasks of the system including:
 \begin{description}
@@
 
-Android applications follow a single-threaded design in which the main thread of the application handles all application events~\cite{AndroidDocs}. This structure is
-commonly used by many UI frameworks since it becomes too complex to make all UI classes thread safe~\cite{SingleThread}. For Android, this main thread is called
-the \texttt{Looper}. The \texttt{Looper} has a message queue attached to it containing application events to be dispatched. UI and system
-events are scheduled on the main \texttt{Looper} by adding them to the message
-queue. The \texttt{Looper} is responsible for continuously looping through these messages and handling them appropriately. This could
-include updating a widget, loading a new activity or processing an Intent.
+All Android applications follow a single-threaded design in which the main thread of the application handles all application
+events~\cite{AndroidDocs}. This structure is commonly used by many UI frameworks since it becomes too complex to make all UI classes thread
+safe~\cite{SingleThread}. In Android, this main thread is called the \texttt{Looper} thread. The \texttt{Looper} has a message queue
+attached to it containing all application events to be dispatched. UI and system events are scheduled on the main \texttt{Looper} by adding
+them to the message queue. The \texttt{Looper} is responsible for continuously looping through these messages and handling them
+appropriately. This could include updating a widget, loading a new activity or processing an Intent.
 
-The main class of an Android application is called the \texttt{ActivityThread}. The \texttt{ActivityThread} keeps track of the
-application's components and handles user and system events. Android applications consists of the
-following application components:
+The main entry-point of each Android application is in its \texttt{ActivityThread} class. The \texttt{ActivityThread} class is part of the
+Android framework and starts the application's \texttt{Looper} thread. It also keeps track of the application's components and handles user
+and system events. Android applications also consists of the following application components:
 \begin{description}
@@
 
-These components are created and managed by the \texttt{ActivityManager}. They interact with each other and with other
-applications using a structure called an \texttt{Intent}. An \texttt{Intent} is a high level implementation of the Binder IPC.
+These components interact with each other and with other applications using a structure called an \texttt{Intent}. An \texttt{Intent} is a
+high level implementation of the Binder IPC.
 
 \subsection{Scope of JPF-ANDROID}
-The Android framework is very large and one of the main challenges of JPF-ANDROID is to decide which parts of the system to model. The
-objective of JPF-ANDROID is to verify Android applications by executing the code using a collection of different event sequences and then to
-detect when certain errors occur.
+The objective of JPF-ANDROID is to verify Android applications by running the application code on the JVM using a collection of different
+event sequences and then to detect when certain errors occur using JPF.
+%what scope of android will be modeled
 
-The more of the Android framework is modelled, the more realistic the model is and the more errors can be found. But, if too much
+The Android framework is very large and one of the main challenges of JPF-ANDROID is to decide which parts of the system to model. The more
+of the Android framework is modelled, the more realistic the model is and the more errors can be found. But, if too much
 of the framework is modelled the scheduling possibilities increase exponentially which means that the search space can become too big to
@@
 
-JPF-ANDROID will focus on verifying one application with multiple application components and their interaction. The system service of the Android OS
-is not part of the application process and runs in its own thread. To reduce scheduling possibilities we will not model the entire system
-service, but implement the necessary tasks as part of the application process.
-
-The following parts of the Android framework will be modelled:
+JPF-ANDROID focuses on verifying a single application with multiple application components and their interaction. The system service of
+the Android OS is not part of the application process and runs in its own thread. To reduce scheduling possibilities, the entire system
+service is not modelled but its necessary components are implemented as part of the application process. The following parts of the Android
+framework is modelled:
 \begin{description}
- \item [ActivityManager] will manage the life-cycle of Activities and other application components.
- \item [ActivityThread]  will manage the application components and their input.
+ \item [ActivityManager]  manages the life-cycle of Activities and other application components.
+ \item [ActivityThread]   the main entry-point to the application. It controls and manages the application components and their input.
  \item [Application components] including Activity, Service, Broadcast Receiver and Content Provider. 
- \item [Window and View structure] The view hierarchy will be modelled including the widgets and the window classes.
- \item [Message queue] - The message queue will be modelled to support input from the script file.
+ \item [Window and View structure] The view hierarchy is modelled including the widgets and the window classes.
+ \item [Message queue] modelled to support input from the script file.
 \end{description}
 
-Lastly, as the application will not be communicating with outside processes, the \texttt{Intent} objects will be modelled to exclude the
+Lastly, as the application will not be communicating with outside processes, the \texttt{Intent} objects are modelled to exclude the
 Binder IPC service.
@@
 \section{Development}
-JPF-AWT introduced the idea of using a simple script file to write event sequences as input to an application. This scripting mechanism makes use of
-JPF's state matching and backtracking features to support non-deterministic elements such as the \texttt{ANY} and \texttt{REPEAT}
-structures. These structures make it simpler to specify many input sequences simultaneously. As both Android and AWT have a single-threaded
-UI design, JPF-ANDROID is built on the design of JPF-AWT. There are two challenges to using this approach:
-\begin{enumerate}
- \item Android applications receive input from two different sources: user input and system input where AWT applications only receive user input.
- \item Android applications contain multiple windows - one for each Activity. This complicates the UI input as each
-window has its own unique set of view components, hence, a unique input sequence.
-\end{enumerate}
-
-\subsection{The JPF-ANDROID input model}
+\subsection{JPF-ANDROID architecture}
 \begin{figure}
@@
 \end{figure}
+As discussed above, Android and AWT applications have a single-threaded application design. That is why JPF-ANDROID's architecture
+is based on JPF-AWT. Figure 2 shows JPF-ANDROID's architecture. JPF-ANDROID models Android's message queue structure
+by using JPF's MJI environment. When the \texttt{Looper} thread requests a new message from the message queue and it is empty, a call to the
+native \texttt{JPF\_MessageQueue} class reads the next event from the input script file.
 
-Figure 2 shows JPF-ANDROID's architecture. JPF-ANDROID models Android's message queue structure by using JPF's MJI environment. When the
-\texttt{Looper} requests a new message from the 
-message queue and it is empty, a call to the native \texttt{JPF\_MessageQueue} class is made. This class reads the next event from the
-input script file and classifies it as either a UI event or system event.
+Android applications can receive input from two different sources: user input and system input. The
+\texttt{JPF\_MessageQueue} class classifies events as either UI or system events. UI events are directed to and handled by the native
+\texttt{JPF\_Window} class and system events are handled by the \texttt{ActivityManager} implemented as the
+native \texttt{JPF\_ActivityManager} class.
 
-UI events are directed to and handled by the native \texttt{JPF\_Window} class. When an Activity's window is inflated, an object map
-is created in this native window class. This map binds the name of a widget to the reference of the inflated widget object.
-When an UI event is received, the name of the target widget is looked-up in the object map. The action is then called directly on the
+When an Activity's UI (window) is inflated, an object map is created in the native \texttt{JPF\_Window} class. This
+map binds the name of each widget to the reference of the inflated widget object. When an UI event is received by the native
+\texttt{JPF\_Window} class, the name of the target widget is looked-up in the object map and the action is then called directly on the
 inflated widget object by pushing a direct call frame on the JPF call stack.
@@
 System events are a little more complex. They use \texttt{Intent} objects to describe a system event. \texttt{Intents} are used to start
-Activities and Services or to provide a notification of certain events. They are similar to messages containing a
-description of an operation to be performed or, often in the case of broadcasts, a description of something that has happened and is being
-announced~\cite{AndroidDocs}.
+Activities and Services or to provide a notification of certain events. They are similar to messages containing a description of an
+operation to be performed or, often in the case of broadcasts, a description of something that has happened and is being
+announced~\cite{AndroidDocs}. System events are handled by the native \texttt{JPF\_ActivityManager} class. This class keeps a map of Intents
+as they are created in the script file. When a system event is received, the \texttt{ActivityManager} looks up the corresponding
+\texttt{Intent} in the map. It then resolves the \texttt{Intent} to the relevant application and sends it to the application's
+\texttt{ActivityThread} to be handled. This message will be processed by the \texttt{Looper} which will direct the \texttt{Intent} to the
+corresponding application component.
 
-System events are handled by the \texttt{ActivityManager} implemented as the native \texttt{JPF\_ActivityManager} class. The
-\texttt{ActivityManager} needs to know which component to send the Intent to: an Activity, Service or Receiver. In an Android
-application this information is conveyed by calling one of the following methods: \texttt{startActivity(Intent), startService(Intent),
-sendBroadcast(Intent)} from the code. This request is sent to the \texttt{ActivityManager} where it is 
-handled appropriately. The  \texttt{ActivityManager} resolves the Intent to the appropriate component and then
-schedules the \texttt{Intent} on the application's  message queue. This message will be processed by the \texttt{Looper} which will direct
-the event to the \texttt{ActivityThread} to be handled.
-
-To allow a user to script system events, variables were added to the scripting language. Variable names are identified by
-the ``@'' in front of the name as '\$' is already used in JPF-AWT to identify UI components. For example a script file that sends an
-\texttt{Intent} to start the \texttt{SampleActivity} will contain:
+\subsection{The input script}
+AWT applications that are tested with JPF-AWT contains at least one input script. This script consist of a list of UI events. These
+events are executed one-by-one when the message queue it empty. JPF-AWT's syntax only supports the scripting of UI events. To
+allow users to script system events, variables were added to the scripting language. Variable names are identified by the ``@'' in front of
+the name as '\$' is already used in JPF-AWT to identify UI components. These variable can be used to construct most Intent objects. For
+example, a script file that sends an \texttt{Intent} to start the \texttt{SampleActivity} will contain:
 
@@
 \hspace*{4mm}\$button1.onClick()
-
 }
@@
 
-\subsection{The input sequence}
-JPF-ANDROID started out by using a sequential input script to drive the application execution. This became a problem when some of the
-input events were non-deterministically scheduled to happen. In other words, if we do not know whether an event took place or
-not, we can not schedule the following events. Lets look at an example:
+JPF-ANDROID scripts also adopted the REPEAT and ANY constructs from JPF-AWT. REPEAT constructs repeat a list of events a specified number
+of times. ANY constructs take a list of events and then uses a ChoiceGenerator and JPF's state matching and backtracking features to visit
+each of the execution branches. JPF stores the state of the system before the it advances to a new state. JPF-AWT uses a JPF search listener
+to store and retrieve the current position of the input script in a specific state so that the script's state is also saved.
+
+Android applications contain multiple windows - one for each Activity. This complicates the script input as each window has its own unique
+set of view components, hence, a unique input sequence. Furthermore, the application flow can switch between these Activities
+at any point of execution. In other words, if we do not know in what Activity the application is, we can not schedule
+the following events.
 
@@
 \centering
-\epsfig{file=newContact.eps, width=1in,}
-\caption{Contacts application windows}
+\epsfig{file=newContact.eps, width=1in,}\\
+\caption{Contacts application window}
 \end{figure}
-
-Figure 3 displays the ``Add Contact'' window of a Contacts application. It contains three
-buttons: the back button starts the \texttt{ContactsListActivity}, the clear button stays on the current Activity and the create 
-button starts the \texttt{ViewContactActivity}. Now let us look at Figure 4 containing the input sequence for the ``Add Contact'' window.
-
 \begin{figure}
@@
 {\sf
-@startIntent.setComponent(``com.example.AddContactActivity'')\\
-startActivity(@startIntent)\\
-\\
-\textbf{REPEAT} 2 \{\\
-\hspace*{2mm}\textbf{ANY} \{ \$backButton.onclick(), \$clearButton.onClick()  \}
-\}\\
+...\\
+\textbf{ANY} \{ \$cancelButton.onclick(), \$clearButton.onClick()  \}
 \$nameEdit.setText(``Mary'')\\
-\$addButton.onClick() 
+\$createButton.onClick()\\
+...
 }
 }
-\caption{Non-deterministically starting an Activity}
+\caption{Input script for ``New Contact'' window}
 \end{figure}
+Figure 3 displays the ``New Contact'' window of a Contacts application. It contains three
+buttons: the cancel button restarts the \texttt{ListContactsActivity}, the clear button stays on the current Activity and the create 
+button starts the \texttt{ViewContactActivity}. Now let us look at figure 4 containing the input sequence for the ``New Contact'' window.
 
-This input sequence describes 2 event sequences:
-\begin{enumerate}
- \item start AddContactActivity\\
-press clearButton\\
-set name edit's text\\
-press addButton
- \item start AddContactActivity\\
- press backButton button, \\
- set name edit's text\\
- press addButton
-\end{enumerate}
-
-The problem is that only after the clear button is pressed is the \texttt{\$nameEdit.setText} command valid. As we do not know
-which window is visible after the button press event, we can not use a sequential script. To address this issue, we included the use of
-sections in the input script (see figure 5). Each section lists the sequential input of a specific Activity.
+The problem occurs in the ANY structure. When the cancelButton.onclick() event fires the application changes to another
+Activity and the following events are not valid any more. To address this issue, we included the
+use of sections in the input script (see figure 5). Each section groups the input events of a specific Activity. Now, if the cancel button
+is pressed the \texttt{ListContactsActivity} will be started and then \texttt{ListContactsActivity}'s event sequence
+will execute instead of executing the following events.
 
@@
 \textbf{SECTION} com.example.ListContactsActivity \{\\
-\hspace*{5mm}\$addButton.onClick()\\
+\hspace*{5mm}\$createButton.onClick()\\
 \hspace*{5mm}\$list.setSelectedIndex([0-3])\\
@@
 \textbf{SECTION} com.example.AddContactActivity \{\\
-\hspace*{5mm}\textbf{REPEAT} 2 \{\\
-\hspace*{7mm}\textbf{ANY} \{ \$backButton.onclick(), \$clearButton.onClick()  \}
-\hspace*{5mm}\}\\
+\hspace*{5mm}\textbf{ANY} \{ \$cancelButton.onclick(), \$clearButton.onClick()  \}
 \hspace*{5mm}\$nameEdit.setText(``Mary'')\\
-\hspace*{5mm}\$addButton.onClick()\\
+\hspace*{5mm}\$createButton.onClick()\\
 \}
@@
 
-Now, if the back button is pressed the \texttt{ListContactsActivity} will be started and then \texttt{ListContactsActivity}'s event sequence
-will execute.
+Now lets view an Android application as a graph with each Activity as its nodes. The root of the tree is the applications main Activity. The
+next challenge is to avoid an infinite loops in the application flow. If we look at the input in figure 5, an infinite loop will occur. The
+ListContactsActivity starts the AddContactActivity and when the cancel button is pressed the AddContactActivity returns to
+the ListContactsActivity. To solve this problem, JPF-ANDROID stores its current Activity. When input events are requensted by the input
+script they are read from the current Activity's script section. The current position in this script file is also stored. When the
+application forwards to a next activity, the state of all the visited activities in the execution path is stored. So when JPF backtracks
+the the state of previous Activity's script files are continued instead of restarted. So when AddContactActivity returns to
+ListContactsActivity, the script is not restarted but continued.
 
-The next challenge is to avoid an infinite loop when returning to an Activity. For example if the back button is pressed on the
-\texttt{AddContactActivity} we return to the \texttt{ListContactsActivity}, but, we do not want to repeat the action of pressing on the
-addButton again, we want to continue executing the next events. In other words we have to determine when an Activity's event sequence has to
-be continued or restarted. We are currently working on this issue.
+\subsection{Case study}
 
-\section{Case Study}
-% example showing the detection of a null pointer exception in certain case
-We assume that JPF-CORE and JPF-ANDROID has been downloaded and build in eclipse. To verify an Android application using JPF-ANDROID we
-require the source code of the project. In the ``src'' package of the project a script 
-file has to be  created including the input events like in figure 6. Also in the ``src'' package has to be a .jpf file that
-includes the project setup. Lastly we need to include a stub main method so that JPF-ANDROID has an entry point to the application.
+Currently JPF-ANDROID can detect deadlocks, race conditions and other property violations in Android applications. The challenge is
+providing a sample application to show how JPF-ANDROID works. This is because most Android applications make use of Android specific
+libraries such as a sqlite database connector, HTTP connection or the mediaplayer libraries. The future work of JPF-ANDROID
+includes modelling these Android specific libraries.
 
-\begin{verbatim}
-	/**
-	 * The main entry point to the application
-	 * 
-	 * @param args
-	 */
-	public static void main(String[] args) {
-		  ActivityThread.main(null);
-	}
-\end{verbatim}
-
-The ViewContactActivity requires an argument containing the contact to view. In this application we did not attach this information to
-the starting intent for ViewContactActivity. A null pointer exception occurs when we try to retrieve this value in the ViewContactActivity
-and is detected by JPF.
+To show how JPF-ANDROID works, we will use a calculator application.
 
@@
 and identify Android specific errors using JPF's listener mechanism.
-\balancecolumns
+
+Future extensions include modelling a sqlite database and http connections.
+
 %

### 2012-09-01 jpf-android/src/classes/android/app/Activity.java
Adding changes to jpf-android

@@ -241,5 +241,10 @@ public class Activity extends ContextThemeWrapper {
 		// TODO Auto-generated method stub
 
 	}
+	
+	
+	public Intent getIntent(){
+		return mIntent;
+	}
 
 }

### 2012-09-01 jpf-android/src/classes/android/content/Intent.java

@@ -16,6 +16,10 @@ public class Intent {
 	HashSet<String> mCategories;
 	Bundle mExtras;
 
+	public Bundle getExtras(){
+		return mExtras;
+	}
+	
 	public Activity getParent() {
 		return parent;
 	}

### 2012-09-01 jpf-android/src/classes/android/text/Editable.java

@@ -1,0 +1,33 @@
+package android.text;
+
+public class Editable implements CharSequence{
+	CharSequence ch ="";
+	
+	public Editable(CharSequence ch){
+		this.ch = ch;
+	}
+
+	@Override
+	public String toString() {
+		return ch.toString();
+	}
+
+	@Override
+	public int length() {
+		return ch.length();
+	}
+
+	@Override
+	public char charAt(int index) {
+		return ch.charAt(index);
+	}
+
+	@Override
+	public CharSequence subSequence(int start, int end) {
+		return ch.subSequence(start, end);
+	}
+	
+	
+	
+
+}

### 2012-09-01 jpf-android/src/classes/android/view/LayoutInflater.java

@@ -5,6 +5,7 @@ import java.lang.reflect.InvocationTargetException;
 
 import android.content.Context;
 import android.util.Log;
+import android.widget.TextView;
 
 /**
  * Inflates a layout file given its resource id into a {@link View} hierarchy.
@@ -13,127 +14,125 @@ import android.util.Log;
  * 
  */
 public class LayoutInflater {
-	public static final String TAG = "LayoutInflater";
+  public static final String TAG = "LayoutInflater";
 
-	/** The package where Android Widgets are stored */
-	private static String WIDGET_PACKAGE = "android.widget";
+  /** The package where Android Widgets are stored */
+  private static String WIDGET_PACKAGE = "android.widget";
 
-	/** Not sure what context to store here TODO */
-	Context c;
+  /** Not sure what context to store here TODO */
+  Context c;
 
-	/** The name of the layout file being inflated */
-	String layout;
+  /** The name of the layout file being inflated */
+  String layout;
 
-	public LayoutInflater(Context c) {
-		this.c = c;
+  public LayoutInflater(Context c) {
+    this.c = c;
 
-	}
+  }
 
-	/**
-	 * Inflates the layout with ID resID and sets root as the root of the
-	 * {@link View} hierarchy.
-	 * 
-	 * @param resId
-	 * @param root
-	 * @return the {@link View} hierarchy's root
-	 */
-	public View inflate(int resId, View root) {
-		layout = setup(resId);
-		nextElement();
-		View v = parse();
-		print(v);
-		return v;
+  /**
+   * Inflates the layout with ID resID and sets root as the root of the {@link View} hierarchy.
+   * 
+   * @param resId
+   * @param root
+   * @return the {@link View} hierarchy's root
+   */
+  public View inflate(int resId, View root) {
+    layout = setup(resId);
+    nextElement();
+    View v = parse();
+    print(v);
+    return v;
 
-	}
+  }
 
-	private void print(View v) {
-		//System.out.println(v.toString() + '{');
-		if (v instanceof ViewGroup)
-			for (View c : ((ViewGroup) v).getChildren()) {
-				if (c != null)
-					print(c);
-			}
+  private void print(View v) {
+    // System.out.println(v.toString() + '{');
+    if (v instanceof ViewGroup)
+      for (View c : ((ViewGroup) v).getChildren()) {
+        if (c != null)
+          print(c);
+      }
 
-		//System.out.println('}');
-	}
+    // System.out.println('}');
+  }
 
-	/**
[…]

### 2012-09-01 jpf-android/src/classes/android/widget/ArrayAdapter.java

@@ -1,0 +1,485 @@
+package android.widget;
+
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.Collection;
+import java.util.Collections;
+import java.util.Comparator;
+import java.util.List;
+
+import android.content.Context;
+import android.view.LayoutInflater;
+import android.view.View;
+import android.view.ViewGroup;
+
+public class ArrayAdapter<T> {
+    /**
+     * Contains the list of objects that represent the data of this ArrayAdapter.
+     * The content of this list is referred to as "the array" in the documentation.
+     */
+    private List<T> mObjects;
+
+    /**
+     * Lock used to modify the content of {@link #mObjects}. Any write operation
+     * performed on the array should be synchronized on this lock. This lock is also
+     * used by the filter (see {@link #getFilter()} to make a synchronized copy of
+     * the original array of data.
+     */
+    private final Object mLock = new Object();
+
+    /**
+     * The resource indicating what views to inflate to display the content of this
+     * array adapter.
+     */
+    private int mResource;
+
+    /**
+     * The resource indicating what views to inflate to display the content of this
+     * array adapter in a drop down widget.
+     */
+    private int mDropDownResource;
+
+    /**
+     * If the inflated resource is not a TextView, {@link #mFieldId} is used to find
+     * a TextView inside the inflated views hierarchy. This field must contain the
+     * identifier that matches the one defined in the resource file.
+     */
+    private int mFieldId = 0;
+
+    /**
+     * Indicates whether or not {@link #notifyDataSetChanged()} must be called whenever
+     * {@link #mObjects} is modified.
+     */
+    private boolean mNotifyOnChange = true;
+
+    private Context mContext;
+
+    // A copy of the original mObjects array, initialized from and then used instead as soon as
+    // the mFilter ArrayFilter is used. mObjects will then only contain the filtered values.
+    private ArrayList<T> mOriginalValues;
+    private ArrayFilter mFilter;
+
+    private LayoutInflater mInflater;
+
+    /**
+     * Constructor
+     *
+     * @param context The current context.
+     * @param textViewResourceId The resource ID for a layout file containing a TextView to use when
+     *                 instantiating views.
+     */
+    public ArrayAdapter(Context context, int textViewResourceId) {
+        init(context, textViewResourceId, 0, new ArrayList<T>());
+    }
+
+    /**
+     * Constructor
+     *
+     * @param context The current context.
+     * @param resource The resource ID for a layout file containing a layout to use when
[…]

### 2012-09-01 jpf-android/src/classes/android/widget/Button.java

@@ -1,9 +1,8 @@
 package android.widget;
 
 import android.content.Context;
-import android.view.View;
 
-public class Button extends View {
+public class Button extends TextView {
 	public Button(Context context) {
 		super(context);
 	}

### 2012-09-01 jpf-android/src/classes/android/widget/EditText.java

@@ -1,0 +1,42 @@
+package android.widget;
+
+import android.content.Context;
+import android.text.Editable;
+import android.util.AttributeSet;
+
+public class EditText extends TextView {
+
+  public EditText(Context context) {
+    super(context);
+  }
+
+  public EditText(Context context, AttributeSet attrs) {
+    super(context);
+  }
+
+  public EditText(Context context, AttributeSet attrs, int defStyle) {
+    super(context);
+  }
+
+  @Override
+  public Editable getText() {
+    return new Editable(super.getText());
+  }
+
+  public void setSelection(int start, int stop) {
+    // Selection.setSelection(getText(), start, stop);
+  }
+
+  public void setSelection(int index) {
+    // Selection.setSelection(getText(), index);
+  }
+
+  public void selectAll() {
+    // Selection.selectAll(getText());
+  }
+
+  public void extendSelection(int index) {
+    // Selection.extendSelection(getText(), index);
+  }
+
+}

### 2012-09-01 jpf-android/src/classes/android/widget/ListView.java

@@ -1,0 +1,85 @@
+package android.widget;
+
+import android.content.Context;
+import android.view.ViewGroup;
+
+public class ListView extends ViewGroup {
+
+    /**
+     * The adapter containing the data to be displayed by this view
+     */
+    ListAdapter mAdapter;
+	
+	public ListView(Context context) {
+		super(context);
+		// TODO Auto-generated constructor stub
+	}
+	
+	 /**
+     * Returns the adapter currently in use in this ListView. The returned adapt
+     * might be a {@link WrapperListAdapter}.
+     *
+     * @return The adapter currently used to display data in this ListView.
+     *
+     * @see #setAdapter(ListAdapter)
+     */
+    //@Override
+    public ListAdapter getAdapter() {
+        return mAdapter;
+    }
+    
+    public void setAdapter(ListAdapter adapter) {
+        /*if (mAdapter != null && mDataSetObserver != null) {
+            mAdapter.unregisterDataSetObserver(mDataSetObserver);
+        }
+
+        resetList();
+        mRecycler.clear();
+
+        if (mHeaderViewInfos.size() > 0|| mFooterViewInfos.size() > 0) {
+            mAdapter = new HeaderViewListAdapter(mHeaderViewInfos, mFooterViewInfos, adapter);
+        } else {
+            mAdapter = adapter;
+        }
+
+        mOldSelectedPosition = INVALID_POSITION;
+        mOldSelectedRowId = INVALID_ROW_ID;
+
+        // AbsListView#setAdapter will update choice mode states.
+        super.setAdapter(adapter);
+
+        if (mAdapter != null) {
+            mAreAllItemsSelectable = mAdapter.areAllItemsEnabled();
+            mOldItemCount = mItemCount;
+            mItemCount = mAdapter.getCount();
+            checkFocus();
+
+            mDataSetObserver = new AdapterDataSetObserver();
+            mAdapter.registerDataSetObserver(mDataSetObserver);
+
+            mRecycler.setViewTypeCount(mAdapter.getViewTypeCount());
+
+            int position;
+            if (mStackFromBottom) {
+                position = lookForSelectablePosition(mItemCount - 1, false);
+            } else {
+                position = lookForSelectablePosition(0, true);
+            }
+            setSelectedPositionInt(position);
+            setNextSelectedPositionInt(position);
+
+            if (mItemCount == 0) {
+                // Nothing selected
+                checkSelectionChanged();
+            }
+        } else {
[…]

### 2012-09-01 jpf-android/src/classes/android/widget/TextView.java

@@ -1,0 +1,22 @@
+package android.widget;
+
+import android.content.Context;
+import android.view.View;
+
+public class TextView extends View {
+  private CharSequence mText;
+
+  public TextView(Context context) {
+    super(context);
+    mText = "";
+  }
+
+  public final void setText(CharSequence text) {
+    mText = text;
+  }
+
+  public CharSequence getText() {
+    return mText;
+  }
+
+}

### 2012-09-01 jpf-android/src/main/gov/nasa/jpf/android/UIActionGeneratorFactory.java

@@ -19,17 +19,17 @@
 
 package gov.nasa.jpf.android;
 
-import java.io.PrintWriter;
-
 import gov.nasa.jpf.Config;
 import gov.nasa.jpf.JPFConfigException;
 import gov.nasa.jpf.util.script.Alternative;
 import gov.nasa.jpf.util.script.ESParser;
 import gov.nasa.jpf.util.script.Event;
+import gov.nasa.jpf.util.script.EventGeneratorFactory;
 import gov.nasa.jpf.util.script.Repetition;
 import gov.nasa.jpf.util.script.ScriptElement;
-import gov.nasa.jpf.util.script.EventGeneratorFactory;
 import gov.nasa.jpf.util.script.Section;
+
+import java.io.PrintWriter;
 
 
 public class UIActionGeneratorFactory extends EventGeneratorFactory {
@@ -87,6 +87,8 @@ public class UIActionGeneratorFactory extends EventGeneratorFactory {
       r.processChildren(this);
     }
   }
+  
+  
 
   public void process (Section sec) {
     // we don't really process sections for UIActions (yet)
@@ -105,4 +107,5 @@ public class UIActionGeneratorFactory extends EventGeneratorFactory {
       t.printStackTrace();
     }
   }
+
 }

### 2012-09-01 jpf-android/src/main/gov/nasa/jpf/android/UIScriptEnvironment.java

@@ -1,14 +1,14 @@
 package gov.nasa.jpf.android;
 
 import gov.nasa.jpf.util.script.Event;
-import gov.nasa.jpf.util.script.ScriptEnvironment;
+import gov.nasa.jpf.util.script.ScriptingEnvironment;
 
 import java.io.FileNotFoundException;
 import java.io.FileReader;
 import java.io.Reader;
 import java.util.List;
-
-public class UIScriptEnvironment extends ScriptEnvironment<UIActionGenerator> {
+ 
+public class UIScriptEnvironment extends ScriptingEnvironment<UIActionGenerator> {
 
   public UIScriptEnvironment (String fname) throws FileNotFoundException {
     super( fname, new FileReader(fname));
@@ -31,5 +31,8 @@ public class UIScriptEnvironment extends ScriptEnvironment<UIActionGenerator> {
       return cg;
     }
   }
+
+
+
 
 }

### 2012-09-01 jpf-android/src/main/gov/nasa/jpf/util/script/ScriptEnvironment.java

@@ -1,312 +1,0 @@
-//
-// Copyright  (C) 2008 United States Government as represented by the
-// Administrator of the National Aeronautics and Space Administration
-//  (NASA).  All Rights Reserved.
-//
-// This software is distributed under the NASA Open Source Agreement
-//  (NOSA), version 1.3.  The NOSA has been approved by the Open Source
-// Initiative.  See the file NOSA-1.3-JPF at the top of the distribution
-// directory tree for the complete NOSA document.
-//
-// THE SUBJECT SOFTWARE IS PROVIDED "AS IS" WITHOUT ANY WARRANTY OF ANY
-// KIND, EITHER EXPRESSED, IMPLIED, OR STATUTORY, INCLUDING, BUT NOT
-// LIMITED TO, ANY WARRANTY THAT THE SUBJECT SOFTWARE WILL CONFORM TO
-// SPECIFICATIONS, ANY IMPLIED WARRANTIES OF MERCHANTABILITY, FITNESS FOR
-// A PARTICULAR PURPOSE, OR FREEDOM FROM INFRINGEMENT, ANY WARRANTY THAT
-// THE SUBJECT SOFTWARE WILL BE ERROR FREE, OR ANY WARRANTY THAT
-// DOCUMENTATION, IF PROVIDED, WILL CONFORM TO THE SUBJECT SOFTWARE.
-//
-package gov.nasa.jpf.util.script;
-
-import gov.nasa.jpf.JPF;
-import gov.nasa.jpf.jvm.ChoiceGenerator;
-import gov.nasa.jpf.util.StateExtensionClient;
-import gov.nasa.jpf.util.StateExtensionListener;
-
-import java.io.FileNotFoundException;
-import java.io.FileReader;
-import java.io.Reader;
-import java.util.ArrayList;
-import java.util.BitSet;
-import java.util.Collection;
-import java.util.HashMap;
-import java.util.List;
-
-/**
- * class representing a statemachine environment that produces SCEventGenerators
- * from scripts
- */
-public abstract class ScriptEnvironment<CG extends ChoiceGenerator<?>>
-		implements StateExtensionClient<ScriptEnvironment<CG>.ActiveSnapshot> {
-
-	static final String DEFAULT = "default";
-
-	// --- just a helper tuple
-	static class ActiveSequence implements Cloneable {
-		String stateName; // the name of the section
-		Section section; // pointer to the section object
-		SequenceInterpreter intrp; // keeps track of the current position of the
[…]

### 2012-09-01 jpf-android/src/main/gov/nasa/jpf/util/script/ScriptingEnvironment.java

@@ -1,0 +1,288 @@
+package gov.nasa.jpf.util.script;
+
+import gov.nasa.jpf.JPF;
+import gov.nasa.jpf.jvm.ChoiceGenerator;
+import gov.nasa.jpf.util.StateExtensionClient;
+import gov.nasa.jpf.util.StateExtensionListener;
+
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.Reader;
+import java.util.ArrayList;
+import java.util.BitSet;
+import java.util.HashMap;
+import java.util.List;
+
+/**
+ * class representing a statemachine environment that produces SCEventGenerators from scripts
+ */
+public abstract class ScriptingEnvironment<CG extends ChoiceGenerator<?>> implements
+    StateExtensionClient<ScriptingEnvironment<CG>.SectionsSnapshot> {
+
+  static final String DEFAULT = "default";
+
+  static class SectionState implements Cloneable {
+    String sectionName; // the name of the section
+    Section section; // pointer to the section object
+    SequenceInterpreter intrp; // keeps track of the current position of the
+
+    // section events
+
+    public SectionState(String sectionName, Section section, SequenceInterpreter intrp) {
+      this.sectionName = sectionName;
+      this.section = section;
+      this.intrp = intrp;
+    }
+
+    public Object clone() {
+      try {
+        SectionState as = (SectionState) super.clone();
+        as.intrp = (SequenceInterpreter) intrp.clone();
+        return as;
+      } catch (CloneNotSupportedException nonsense) {
+        return null; // we are a Cloneable, so we don't get here
+      }
+    }
+
+    public boolean isDone() {
+      return intrp.isDone();
+    }
+  }
+
+  // --- our state extension - we need this mostly for cloning (deep copy)
+  class SectionsSnapshot implements Cloneable {
+    ArrayList<SectionState> sectionsState; // current state of all Active
+
+    SectionsSnapshot() {
+      sectionsState = new ArrayList<SectionState>();
+    }
+
+    SectionsSnapshot(ArrayList<SectionState> as) {
+      sectionsState = as;
+    }
+
+    public SectionState get(String sectionName) {
+      for (SectionState as : sectionsState) {
+        if (as.sectionName.equals(sectionName)) {
+          return as;
+        }
+      }
+      return null;
+    }
+
+    public Object clone() {
+      try {
+        SectionsSnapshot ss = (SectionsSnapshot) super.clone();
+        for (SectionState as : this.sectionsState) {
[…]

### 2012-09-01 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_os_MessageQueue.java

@@ -2,19 +2,13 @@ package gov.nasa.jpf.android;
 
 import gov.nasa.jpf.Config;
 import gov.nasa.jpf.JPF;
-import gov.nasa.jpf.jvm.ClassInfo;
-import gov.nasa.jpf.jvm.DirectCallStackFrame;
-import gov.nasa.jpf.jvm.ElementInfo;
 import gov.nasa.jpf.jvm.MJIEnv;
-import gov.nasa.jpf.jvm.MethodInfo;
-import gov.nasa.jpf.jvm.StackFrame;
 import gov.nasa.jpf.jvm.SystemState;
 import gov.nasa.jpf.jvm.ThreadInfo;
 import gov.nasa.jpf.jvm.bytecode.Instruction;
 import gov.nasa.jpf.util.script.ESParser;
 
 import java.io.FileNotFoundException;
-import java.util.logging.Level;
 import java.util.logging.Logger;
 
 /**
@@ -24,126 +18,122 @@ import java.util.logging.Logger;
  * 
  */
 public class JPF_android_os_MessageQueue {
-	static Logger log = JPF.getLogger("gov.nasa.jpf.android");
-	static final String UIACTION = "[UIAction]";
+  static Logger log = JPF.getLogger("gov.nasa.jpf.android");
+  static final String UIACTION = "[UIAction]";
 
-	// do we want to process all UIActionCGs regardless of state matching
-	static boolean forceActionStates = false;
+  // do we want to process all UIActionCGs regardless of state matching
+  static boolean forceActionStates = false;
 
-	static int counter; // the number of UIActionCGs generated so far
+  static int counter; // the number of UIActionCGs generated so far
 
-	// static UIActionGeneratorFactory cgFactory;
-	static UIScriptEnvironment scriptEnv;
+  // static UIActionGeneratorFactory cgFactory;
+  static UIScriptEnvironment scriptEnv;
 
-	/**
-	 * Called from the MesaageQueue Constructor, i.e. before each application
-	 * run. It opens and parses the input script.
-	 */
-	public static void init____V(MJIEnv env, int objref) {
-		Config conf = env.getConfig();
+  /**
+   * Called from the MesaageQueue Constructor, i.e. before each application run. It opens and parses the input
+   * script.
+   */
+  public static void init____V(MJIEnv env, int objref) {
+    Config conf = env.getConfig();
 
-		counter = 0;
-		forceActionStates = conf.getBoolean("awt.force_states", true);
+    counter = 0;
[…]

### 2012-09-01 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_view_LayoutInflater.java

@@ -21,115 +21,120 @@ import org.w3c.dom.NodeList;
 import android.view.LayoutInflater;
 
 /**
- * Native peer of the {@link LayoutInflater}. Makes use of
- * {@link DocumentBuilder} to parse the layout files.
+ * Native peer of the {@link LayoutInflater}. Makes use of {@link DocumentBuilder} to parse the layout files.
  * 
  * @author "Heila van der Merwe"
  * 
  */
 public class JPF_android_view_LayoutInflater {
-	static Logger log = JPF.getLogger("gov.nasa.jpf.android");
+  static Logger log = JPF.getLogger("gov.nasa.jpf.android");
 
-	/**
-	 * Used to create an unique name and id field for components that are not
-	 * named in the R.java file. Window has count 0. TODO what happens with
-	 * multi-windows come into play?
-	 */
-	private static int count = 1;
+  /**
+   * Used to create an unique name and id field for components that are not named in the R.java file. Window
+   * has count 0. TODO what happens with multi-windows come into play?
+   */
+  private static int count = 1;
 
-	/** Stores the current {@link Element} being inflated */
-	private static Element currentNode = null;
-	private static LinkedList<Element> nodes = new LinkedList<Element>();
+  /** Stores the current {@link Element} being inflated */
+  private static Element currentNode = null;
+  private static LinkedList<Element> nodes = new LinkedList<Element>();
 
-	public static int setup(MJIEnv env, int objref, int fileref) {
-		Config conf = env.getConfig();
-		String lPath = conf.getString("path") +  "/res/layout/"; // TODO if specified in
-		String filename = JPF_android_view_Window.getLayoutName(fileref);
+  public static int setup(MJIEnv env, int objref, int fileref) {
+    Config conf = env.getConfig();
+    String lPath = conf.getString("path") + "/res/layout/"; // TODO if specified in
+    String filename = JPF_android_view_Window.getLayoutName(fileref);
 
-		try {
-			DocumentBuilderFactory factory = DocumentBuilderFactory
-					.newInstance();
-			InputStream is = new FileInputStream(lPath
-					+ filename + ".xml");
-			DocumentBuilder builder = factory.newDocumentBuilder();
-			Document dom = builder.parse(is, null);
+    try {
+      DocumentBuilderFactory factory = DocumentBuilderFactory.newInstance();
[…]

### 2012-09-02 Papers/paper.tex
Paper updates

@@
 
-\numberofauthors{3}
+\numberofauthors{1}
 
 \author{%
-\alignauthor Heila van der Merwe\\
+\alignauthor Heila van der Merwe, Brink van der Merwe and Willem Visser\\
        \affaddr{Dept. of Computer Science}\\
@@
        \affaddr{South Africa, 7602}
-       \email{hvdmerwe@cs.sun.ac.za}
-\alignauthor  Brink van der Merwe\\
- \affaddr{Dept. of Computer Science}\\
-       \affaddr{University of Stellenbosch}\\
-       \affaddr{Private Bag X1 Matieland}\\
-       \affaddr{South Africa, 7602}
-       \email{abvdm@cs.sun.ac.za}
-\alignauthor  Willem Visser\\
- \affaddr{Dept. of Computer Science}\\
-       \affaddr{University of Stellenbosch}\\
-       \affaddr{Private Bag X1 Matieland}\\
-       \affaddr{South Africa, 7602}
-       \email{wvisser@cs.sun.ac.za}
+       \email{hvdmerwe@cs.sun.ac.za, abvdm@cs.sun.ac.za, wvisser@cs.sun.ac.za }
 }
@@
 Another approach is to test Android applications using the Java Virtual Machine (JVM). There are different ways of implementing such
-a framework. Android lint~\cite{lint}, for example, makes use of static analysis to identify common errors in applications.
+a framework. Android lint, for example, makes use of static analysis to identify common errors in applications.
 Robolectric~\cite{robolectric}, a JUnit testing framework running on the JVM,  intercepts the loading of Android classes and then uses
@@
 and listen for property violations. Additionally, JPF's design encourages developers to create extensions to the framework. Currently there
-exist many extensions including a symbolic execution extension (JPF-SYMBC)~\cite{JPF-SYMB}, data race
+exist many extensions including a symbolic execution extension (JPF-SYMBC), data race
 detector (JPF-RACEFINDER) and an abstract window toolkit (AWT) extension (JPF-AWT)~\cite{JPF-AWT}.
@@
 
-As shown in figure 1, the Android OS is built on top of a modified Linux kernel. The kernel provides a layer of abstraction on top of its
-low level functionality such as process, memory, user, network and thread management. On top of the Android kernel is a set of native
-C-libraries. The Dalvik VM is a custom, optimised version of the JVM. For security reasons each Android application is run as a separate
-process in its own Dalvik VM instance~\cite{AndroidSecurity}.  Hence, applications can only communicate with each other and the with the
-Android framework using Android's Binder inter-process communication (IPC) mechanism~\cite{Binder}.
+As shown in figure \ref{fig:android}, the Android OS is built on top of a modified Linux kernel. The kernel provides a layer of abstraction
+on top of its low level functionality such as process, memory, user, network and thread management. On top of the Android kernel is a set of
+native C-libraries. The Dalvik VM is a custom, optimised version of the JVM. For security reasons each Android application is run as a
+separate process in its own Dalvik VM instance~\cite{AndroidSecurity}.  Hence, applications can only communicate with each other and the
+with the Android framework using Android's Binder inter-process communication (IPC) mechanism~\cite{Binder}.
 
@@
 \caption{The Android application stack~\cite{systemserver}}
+\label{fig:android}
 \end{figure}
@@
 tasks of the system including:
+\vspace{-10pt}
 \begin{description}
@@
 \end{description}
-
+\vspace{-5pt}
 All Android applications follow a single-threaded design in which the main thread of the application handles all application
@@
 and system events. Android applications also consists of the following application components:
+\vspace{-10pt}
 \begin{description}
@@
 \end{description}
-
+\vspace{-5pt}
 These components interact with each other and with other applications using a structure called an \texttt{Intent}. An \texttt{Intent} is a
-high level implementation of the Binder IPC.
+high level implementation of the Binder IPC. \texttt{Intents} are used to start Activities and Services or to provide a notification of
+certain events. They are similar to messages containing a description of an operation to be performed or, often in the case of broadcasts, a
+description of something that has happened and is being announced~\cite{AndroidDocs}.
 
@@
 framework is modelled:
+\vspace{-10pt}
 \begin{description}
@@
  \item [Window and View structure] The view hierarchy is modelled including the widgets and the window classes.
- \item [Message queue] modelled to support input from the script file.
+ \item [Message queue] modelled to support script input.
 \end{description}
-
+\vspace{-5pt}
 Lastly, as the application will not be communicating with outside processes, the \texttt{Intent} objects are modelled to exclude the
@@
 \subsection{JPF-ANDROID architecture}
+% \begin{figure}
+% \centering
+% \epsfig{file=arch.eps, width=3.5in,}
+% \caption{JPF-ANDROID architecture}
+% \label{fig:arch}
+% \end{figure}
+%JPF-ANDROID BASED ON JPF_AWT  why and how does it work?
+As discussed above, both Android and AWT applications have a single-threaded application design. That is why JPF-ANDROID's architecture
+is based on JPF-AWT. JPF-ANDROID models Android's message queue by using JPF's MJI
+environment. When the \texttt{Looper} thread requests a new message from the message queue and it is empty, a call to the native
+\texttt{JPF\_MessageQueue} class requests the next event from the scripting environment. The \texttt{JPF\_MessageQueue} class classifies
+events as either UI or system events. UI events are directed to and handled by the native \texttt{JPF\_Window} class and system events by
+the native \texttt{JPF\_ActivityManager} class.
+
+% Explain what UI events are and how they are handled by android vs how they ae handled by the system
+UI events include events fired by widgets such as clicking a button or selecting an item in a list view. An
+Activity's UI is represented by a window object containing a view hierarchy. When the window is inflated, an object map is created in the
+native \texttt{JPF\_Window} class. This map binds the name of each widget to the reference of the inflated widget object. When an UI event
+is received by the native \texttt{JPF\_Window} class, the name of the target widget is looked-up in the object map and the action is then
+called directly on the inflated widget object by pushing a direct call frame on the JPF call stack.
+
+% Explain what system events are how they are handled by android how they are handled by the system
+System events use \texttt{Intent} objects to describe a the event that occurred. They include events to start an Activity or Service or a
+battery low notification. In the Android OS, system events are sent to the Activity manager which is modelled in JPF-ANDROID by the native
+\texttt{JPF\_ActivityManager} class. This class keeps a map of Intents as they are defined in the script file. When a system event is
+received, the corresponding \texttt{Intent} is looked up in the map. The \texttt{Intent} is then resolved to the relevant
+component and scheduled in the application's message queue.
+
+\subsection{The scripting environment}
+% what is input script, how does it work(its function) and how are does it look
+JPF-AWT's script consist of a list of UI events. These events are executed one-by-one when the message queue it empty. To allow users to
+script system events, variables were added to the scripting language in JPF-ANDROID. Variable names are identified by the ``@'' in front of
+the variable's name as '\$' is already used in JPF-AWT to identify UI components. These variable can be used to construct most Intent
+objects. For example, a script file that sends an \texttt{Intent} to start the \texttt{SampleActivity} is shown in figure \ref{fig:start}
 \begin{figure}
-\centering
-\epsfig{file=arch.eps, width=3.5in,}
-\caption{JPF-ANDROID architecture}
-\end{figure}
-As discussed above, Android and AWT applications have a single-threaded application design. That is why JPF-ANDROID's architecture
-is based on JPF-AWT. Figure 2 shows JPF-ANDROID's architecture. JPF-ANDROID models Android's message queue structure
-by using JPF's MJI environment. When the \texttt{Looper} thread requests a new message from the message queue and it is empty, a call to the
-native \texttt{JPF\_MessageQueue} class reads the next event from the input script file.
-
-Android applications can receive input from two different sources: user input and system input. The
-\texttt{JPF\_MessageQueue} class classifies events as either UI or system events. UI events are directed to and handled by the native
-\texttt{JPF\_Window} class and system events are handled by the \texttt{ActivityManager} implemented as the
-native \texttt{JPF\_ActivityManager} class.
-
-When an Activity's UI (window) is inflated, an object map is created in the native \texttt{JPF\_Window} class. This
-map binds the name of each widget to the reference of the inflated widget object. When an UI event is received by the native
-\texttt{JPF\_Window} class, the name of the target widget is looked-up in the object map and the action is then called directly on the
-inflated widget object by pushing a direct call frame on the JPF call stack.
-
-System events are a little more complex. They use \texttt{Intent} objects to describe a system event. \texttt{Intents} are used to start
-Activities and Services or to provide a notification of certain events. They are similar to messages containing a description of an
-operation to be performed or, often in the case of broadcasts, a description of something that has happened and is being
-announced~\cite{AndroidDocs}. System events are handled by the native \texttt{JPF\_ActivityManager} class. This class keeps a map of Intents
-as they are created in the script file. When a system event is received, the \texttt{ActivityManager} looks up the corresponding
-\texttt{Intent} in the map. It then resolves the \texttt{Intent} to the relevant application and sends it to the application's
-\texttt{ActivityThread} to be handled. This message will be processed by the \texttt{Looper} which will direct the \texttt{Intent} to the
-corresponding application component.
-
-\subsection{The input script}
-AWT applications that are tested with JPF-AWT contains at least one input script. This script consist of a list of UI events. These
-events are executed one-by-one when the message queue it empty. JPF-AWT's syntax only supports the scripting of UI events. To
-allow users to script system events, variables were added to the scripting language. Variable names are identified by the ``@'' in front of
-the name as '\$' is already used in JPF-AWT to identify UI components. These variable can be used to construct most Intent objects. For
-example, a script file that sends an \texttt{Intent} to start the \texttt{SampleActivity} will contain:
-
+\frame{
+\parbox{0.48\textwidth}{
 {\small
 {\sf 
-\hspace*{4mm}@intent1.setComponent(``com.example.SampleActivity'')\\
-\hspace*{4mm}startActivity(@intent1)\\
-\hspace*{4mm}\$button1.onClick()
-}
-}
+\vspace*{2mm}
+\hspace*{2mm}1. @intent1.setComponent(``SampleActivity'')\\
+\hspace*{2mm}2. startActivity(@intent1)\\
+\hspace*{2mm}3. \$button1.onClick()
+\vspace*{2mm}
+}}}}
+\vspace{-18pt}
+\caption{Starting SampleActivity}
+\label{fig:start}
+\end{figure}
 
-JPF-ANDROID scripts also adopted the REPEAT and ANY constructs from JPF-AWT. REPEAT constructs repeat a list of events a specified number
-of times. ANY constructs take a list of events and then uses a ChoiceGenerator and JPF's state matching and backtracking features to visit
-each of the execution branches. JPF stores the state of the system before the it advances to a new state. JPF-AWT uses a JPF search listener
-to store and retrieve the current position of the input script in a specific state so that the script's state is also saved.
+JPF-ANDROID scripts also adopted the \textbf{REPEAT} and \textbf{ANY} constructs from JPF-AWT. \textbf{REPEAT} constructs repeat a list of
+events a specified number of times. \textbf{ANY} constructs take a list of events as parameters and then uses a ChoiceGenerator and JPF's
+state matching and backtracking features to visit each of the execution branches. JPF stores the state of the system before the it advances
+to a new state. JPF-AWT uses a JPF search listener to store and retrieve the current position of the input script in a specific state so
+that the script's state is also saved.
 
+%how and why was this scripting environment adapted
 Android applications contain multiple windows - one for each Activity. This complicates the script input as each window has its own unique
 set of view components, hence, a unique input sequence. Furthermore, the application flow can switch between these Activities
-at any point of execution. In other words, if we do not know in what Activity the application is, we can not schedule
-the following events.
+at any point of execution. In other words, if we do not know in what Activity the application is, we can not script the following events.
+
+% \begin{figure}
+% \centering
+% \epsfig{file=newContact.eps, width=1in,}\\
+% \caption{Contacts application window}
+% \end{figure}
+% \begin{figure}
+% {\small
+% {\sf
+% ...\\
+% \textbf{ANY} \{ \$cancelButton.onclick(), \$clearButton.onClick()  \}
+% \$nameEdit.setText(``Mary'')\\
+% \$createButton.onClick()\\
+% ...
+% }
+% }
+% \caption{Input script for ``New Contact'' window}
+% \end{figure}
+Let us take a contacts android application as an example. The application has two Activities: ListContactsActivity and the
+NewContactActivity. The ListContactsActivity contains a list of the current contacts and a button to add new contacts that directs the user
+to the NewContactActivity. The NewContactActivity contains two buttons: the clear button stays on the current Activity and clears its fields
+and the create button starts the \texttt{ListContactsActivity}. Now let us look at figure \ref{fig:contact} containing the input sequence
+for the NewContactActivity.
 
 \begin{figure}
-\centering
-\epsfig{file=newContact.eps, width=1in,}\\
-\caption{Contacts application window}
-\end{figure}
-\begin{figure}
+\frame{
+\parbox{0.48\textwidth}{
 {\small
 {\sf 
-...\\
-\textbf{ANY} \{ \$cancelButton.onclick(), \$clearButton.onClick()  \}
-\$nameEdit.setText(``Mary'')\\
-\$createButton.onClick()\\
-...
-}
-}
-\caption{Input script for ``New Contact'' window}
+\vspace*{2mm}
+\hspace*{2mm}1. @startIntent.setComponent(``ListContactsActivity'')\\
+\hspace*{2mm}2. startActivity(@startIntent)\\
+\hspace*{2mm}3. \$createContactButton.onClick()\\
+\hspace*{2mm}4. \$nameEdit.setText(``Mary'')\\
+\hspace*{2mm}5. \textbf{ANY} \{ \$<create\,|\,clear>Button.onClick()\}\\
+\hspace*{2mm}6. \$nameEdit.setText(``Maria'')\\
+}}}}
+\vspace{-15pt}
+\caption{Original script for Contacts application}
+\label{fig:contact}
 \end{figure}
-Figure 3 displays the ``New Contact'' window of a Contacts application. It contains three
-buttons: the cancel button restarts the \texttt{ListContactsActivity}, the clear button stays on the current Activity and the create 
-button starts the \texttt{ViewContactActivity}. Now let us look at figure 4 containing the input sequence for the ``New Contact'' window.
 
-The problem occurs in the ANY structure. When the cancelButton.onclick() event fires the application changes to another
-Activity and the following events are not valid any more. To address this issue, we included the
-use of sections in the input script (see figure 5). Each section groups the input events of a specific Activity. Now, if the cancel button
-is pressed the \texttt{ListContactsActivity} will be started and then \texttt{ListContactsActivity}'s event sequence
-will execute instead of executing the following events.
+The problem occurs in the ANY structure. When the create button is clicked the application changes to the ListContactsActivity
+and the following event is not valid any more. This drastically restricts the number of sequences that can be scripted in the file. To
+address this issue, we included the use of sections in the input script (see figure \ref{fig:contact2}). Each section groups the input
+events of a specific Activity. Now, if the create button is pressed the \texttt{ListContactsActivity} will be started and the
+\texttt{ListContactsActivity}'s events specified in its sequence will start executing again.
 
 \begin{figure}
+\frame{
+\parbox{0.48\textwidth}{
 {\small
 {\sf 
-\textbf{SECTION} default \{\\
-\hspace*{5mm}@startIntent.setComponent(``com.example.ListContactsActivity'')\\
-\hspace*{5mm}startActivity(@startIntent)\\
-\}
-
-\textbf{SECTION} com.example.ListContactsActivity \{\\
-\hspace*{5mm}\$createButton.onClick()\\
-\hspace*{5mm}\$list.setSelectedIndex([0-3])\\
-\}\\
-
-\textbf{SECTION} com.example.AddContactActivity \{\\
-\hspace*{5mm}\textbf{ANY} \{ \$cancelButton.onclick(), \$clearButton.onClick()  \}
-\hspace*{5mm}\$nameEdit.setText(``Mary'')\\
-\hspace*{5mm}\$createButton.onClick()\\
-\}
-}
-}
+\vspace*{2mm}
+\hspace*{2mm}1. \textbf{SECTION} default \{\\
+\hspace*{2mm}2. \hspace*{5mm}@startIntent.setComponent(``ListContactsActivity'')\\
+\hspace*{2mm}3. \hspace*{5mm}startActivity(@startIntent)\\
+\hspace*{2mm}4. \}\\
+\hspace*{2mm}5. \\
+\hspace*{2mm}6. \textbf{SECTION} ListContactsActivity \{\\
+\hspace*{2mm}7. \hspace*{5mm}\$createButton.onClick()\\
+\hspace*{2mm}8. \hspace*{5mm}\$list.setSelectedIndex([0-3])\\
+\hspace*{2mm}9. \}\\
+\hspace*{2mm}10. \\
+\hspace*{2mm}11. \textbf{SECTION} NewContactActivity \{\\
+\hspace*{2mm}12. \hspace*{5mm}\$nameEdit.setText(``Mary'')\\
+\hspace*{2mm}13. \hspace*{5mm}\textbf{ANY} \{ \$<create\,|\,clear>Button.onClick()\}\\
+\hspace*{2mm}14. \hspace*{5mm}\$nameEdit.setText(``Maria'')\\
+\hspace*{2mm}15. \}
+\vspace*{2mm}
+}}}}
+\vspace{-15pt}
 \caption{Adding sections to the input script}
+\label{fig:contact2}
 \end{figure}
 
-Now lets view an Android application as a graph with each Activity as its nodes. The root of the tree is the applications main Activity. The
-next challenge is to avoid an infinite loops in the application flow. If we look at the input in figure 5, an infinite loop will occur. The
-ListContactsActivity starts the AddContactActivity and when the cancel button is pressed the AddContactActivity returns to
-the ListContactsActivity. To solve this problem, JPF-ANDROID stores its current Activity. When input events are requensted by the input
-script they are read from the current Activity's script section. The current position in this script file is also stored. When the
-application forwards to a next activity, the state of all the visited activities in the execution path is stored. So when JPF backtracks
-the the state of previous Activity's script files are continued instead of restarted. So when AddContactActivity returns to
-ListContactsActivity, the script is not restarted but continued.
+The addition of the sections in the input script lead to infinite event sequences. In the above example, an infinite loop occurs when the
+create button is pressed on the NewContactActivity window. This will stop the execution of the NewContactActivity section and restart
+the ListContactsActivity section's events. When the ListContactsActivity's section is restarted, it again clicks on the createButton
+restarting the NewContactActivity. To address this issue, JPF-ANDROID keeps record of its current Activity. The scripting environment was
+also adapted to store the current position of each section's events for each visited Activity. If the branch returns to a previously visited
+Activity, its current position in its section is looked up and instead of restarting the section, it continues from its previous position.
 
-\subsection{Case study}
+\subsection{Case studies}
+%calculator
+%how does application look and work
+The first application is a scientific calculator. The calculator has two Activities: a simple view that
+displays basic arithmetic operations and a scientific view that displays more complex arithmetic operations. When the user switches
+between these Activities, the current state of the calculator is preserved. This state includes the intermediate values and current
+operation. This state information is bundled with the \texttt{Intent} that starts then next Activity.
+\begin{figure}
 
-Currently JPF-ANDROID can detect deadlocks, race conditions and other property violations in Android applications. The challenge is
-providing a sample application to show how JPF-ANDROID works. This is because most Android applications make use of Android specific
-libraries such as a sqlite database connector, HTTP connection or the mediaplayer libraries. The future work of JPF-ANDROID
-includes modelling these Android specific libraries.
+\frame{
+\parbox{0.48\textwidth}{
+{\small
+{\sf 
+\vspace*{2mm}
+\hspace*{2mm}1. \textbf{SECTION} SimpleActivity  \{\\
+\hspace*{2mm}2. \hspace*{5mm}\textbf{ANY} \{\,\$button[0-9].onClick()\,\}\\
+\hspace*{2mm}3. \hspace*{5mm}\textbf{ANY} \{\,\$button<Plus|Minus|Mul|Div|More>.onClick()\,\}\\
+\hspace*{2mm}4. \hspace*{5mm}\textbf{ANY} \{\,\$button[0-9].onClick()\,\}\\
+\hspace*{2mm}5. \hspace*{5mm}\$buttonEquals.onClick()\\
+\hspace*{2mm}6. \}\\
+\hspace*{2mm}7. \textbf{SECTION} ScientificActivity  \{\\
+\hspace*{2mm}8. \hspace*{5mm}\textbf{ANY} \{\,\$button<Sin|Cos|Tan>.onClick()\,\}\\
+\hspace*{2mm}9. \}\\
+}}}}
+\vspace{-15pt}
+\caption{Input script for Calculator application}
+\label{fig:calc}
+\end{figure}
 
-To show how JPF-ANDROID works, we will use a calculator application.
+%what errors can occur
+The calculator application contains two errors. When the user divides a value by zero, an uncaught
+\texttt{ArithmeticException} is thrown by the application which causes Android to kill the application. Secondly the application neglected
+to attach the state information to the Intent that is passed to the next Activity. When the user switches to the other Activity a
+\texttt{NullPointerException} is thrown when it tries to read the state information from the Intent.
+
+To detect these errors we will use the test script in figure~\ref{fig:calc}. The scripting environment interprets the script into the
+following input sequences:
+\begin{align*}
+\text{<sequence>} &= \text{<simple\_seq>}\,|\,\text{<complex\_seq>}\\
+\text{<simple\_seq>} &= \text{number},\,\text{simple\_op},\,\text{number},\,\text{equals}\\
+\text{<complex\_seq>} &= \text{number},\,\text{complex\_op}\\
+\text{simple\_op} &= \text{``+''}\,|\,\text{``-''}\,|\,\text{``}\times\text{''}\,|\,\text{``}\div\text{''}\\
+\text{complex\_op} &= \text{``sin''}\,|\,\text{``cos''}\,|\,\text{``tan''}\\
+\text{equals} &= \text{``=''} \\
+\text{number} &= \text{``0''\,|\,``1''\,|\,``2''\,|\,``3''\,|\,``4''\,|\,``5''\,|\,``6''\,|\,``7''\,|\,``8''\,|\,``9''}
+\end{align*}
+Each of the ten number buttons are pressed followed by a simple operation and another number or a complex operation.
+
+%how they where detected
+JPF is automatically configured to detect thrown exceptions and to stop execution. When JPF-ANDROID was run it firstly detected the
+\texttt{ArithmenticException} due to the division by zero:
+\begingroup
+ \fontsize{6pt}{7pt}\selectfont
+\begin{verbatim}
+====================================================== results
+error #1: gov.nasa.jpf.jvm.NoUncaughtExceptionsProperty 
+         "java.lang.ArithmeticException: Division by zero  at ..."
+====================================================== statistics
+elapsed time:       00:00:01
+states:             new=76, visited=0, backtracked=63, end=30
+search:             maxDepth=13, constraints hit=0
+choice generators:  thread=7 (signal=0, lock=3, shared ref=0), data=39
+heap:               new=3455, released=2105, max live=1507, gc-cycles=74
+instructions:       76796
+max memory:         117MB
+loaded code:        classes=145, methods=2064
+======================================================
+\end{verbatim}
+\endgroup
+After this error was fixed JPF-ANDROID detected the \texttt{NullPointerException} in the same way.
+
+Both of these errors would have been difficult to detect with unit testing. The \texttt{ArithmenticException} is challenging due
+to the many possible input sequence combinations. If a test case did not specifically identify this as a point of interest, unit testing
+would not have detected this error. The second error is challenging to detect due to the fact that it only occurs when the flow of Activity
+classes are modelled.
+
+% deadlock
+%how does application look and work
+The next case study is a very simple application demonstrating how JPF-ANDROID detects a deadlock in a Android application. When the
+\texttt{Looper}/main thread of an application is caught in a deadlock, the Android OS kills the application and displays an
+Application Not Responding (ANR) dialog. But, Android does not detect a deadlock if it occurs between other asynchronous threads. This
+sample application spawns two asynchronous threads that deadlock. The application has one Activity with two
+buttons. The first button spawns the first thread and the second button spawns the second thread. After a while these two thread deadlock
+and are then blocked forever, waiting for each other. The input script for the application is given in figure \ref{fig:deadlock}.
+\begin{figure}
+\frame{
+\parbox{0.48\textwidth}{
+{\small
+{\sf 
+\vspace*{2mm}
+\hspace*{2mm}1. \textbf{SECTION} DeadlockActivity  \{\\
+\hspace*{2mm}2. \hspace*{5mm}\$button1.onClick()\\
+\hspace*{2mm}3. \hspace*{5mm}\$button2.onClick()\\
+\hspace*{2mm}4. \}\\
+}}}}
+\vspace{-15pt}
+\caption{Input script for Deadlock application}
+\label{fig:deadlock}
+\end{figure}
+
+JPF is then configured to listen for deadlocks and schedules the threads in all possible ways to detect the deadlock.
+\begingroup
+ \fontsize{6pt}{7pt}\selectfont
+\begin{verbatim}
+ ====================================================== thread ops #1
+   1       1     trans          loc            : stmt
+------- ------- ---------------------------------------------------
+B:1003     |      54  DeadlockActivity.java:82 : bower.bowBack(this);
+   |    B:1000    54  DeadlockActivity.java:82 : bower.bowBack(this);
+L:1000     |      54  DeadlockActivity.java:56 : friend[0].bow(friend[1]);
+   |    L:1003    18  DeadlockActivity.java:56 : friend[0].bow(friend[1]);
+   S       |       6
+   |       S       3
+====================================================== results
+error #1: gov.nasa.jpf.jvm.NotDeadlockedProperty 
+         "deadlock encountered:   thread java.lang.Thread:{i..."
+====================================================== statistics
+elapsed time:       00:00:01
+states:             new=55, visited=13, backtracked=67, end=1
+search:             maxDepth=10, constraints hit=0
+choice generators:  thread=26 (signal=0, lock=11, shared ref=0), data=7
+heap:               new=1430, released=375, max live=1040, gc-cycles=67
+instructions:       12661
+max memory:         117MB
+loaded code:        classes=140, methods=1792
+======================================================
+\end{verbatim}
+\endgroup
+
+\section{Future Work}
+Currently JPF-ANDROID can detect deadlocks, race conditions and other property violations in Android applications. The next challenge is
+modelling the extra Android libraries. This is because most Android applications make use of many Android specific
+libraries such as the sqlite database connector, HTTP connections or the media player libraries.
+
+Another extension that will be added to JPF-ANDROID is coverage testing. JPF has many coverage extensions available so we will be adapting
+one these extensions to work on Android applications.
 
@@
 and identify Android specific errors using JPF's listener mechanism.
-
-Future extensions include modelling a sqlite database and http connections.
-
-%
 % The following two commands are all you need in the
@@
 \bibliographystyle{abbrv}
+\scriptsize
 \bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case

### 2012-09-03 Papers/paper.tex
Updating spelling

@@
 
-This paper describes the development of JPF-ANDROID, an Android application verification tool. JPF-ANDROID is built on Java PathFinder, 
+This paper describes the development of JPF-ANDROID, an Android application verification tool. JPF-ANDROID is built on Java Pathfinder, 
 a Java model checking engine. JPF-ANDROID provides a simplified model of the Android framework on which an Android application can run. It then allows
@@
 Although Android applications and Java desktop applications are designed for completely different Java VMs, they are both built on an
-implementation of the Java API. As a consequence, Android applications contain many of the same error as Java applications. These defects
+implementation of the Java API. As a consequence, Android applications contain many of the same errors as Java applications. These defects
 include, but are not limited to, concurrency issues and common runtime exceptions such as NullPointer Exceptions. It follows that existing
@@
 % what are we going to do and why 
-This paper describes an extension to Java PathFinder (JPF)~\cite{JPFDocs} that enables the automatic verification of Android applications on
+This paper describes an extension to Java Pathfinder (JPF)~\cite{JPFDocs} that enables the automatic verification of Android applications on
 the standard Java JVM.
@@
 The next section will provide an overview of JPF and Android and how JPF can be used to test Android applications. Thereafter
-the development of the JPF-ANDROID tool will be discussed.
+the development of the JPF-ANDROID tool will be discussed concluding with two case studies.
 
@@
 % Explain what system events are how they are handled by android how they are handled by the system
-System events use \texttt{Intent} objects to describe a the event that occurred. They include events to start an Activity or Service or a
+System events use \texttt{Intent} objects to describe a event that occurred. They include events to start an Activity or Service or a
 battery low notification. In the Android OS, system events are sent to the Activity manager which is modelled in JPF-ANDROID by the native
@@
 events a specified number of times. \textbf{ANY} constructs take a list of events as parameters and then uses a ChoiceGenerator and JPF's
-state matching and backtracking features to visit each of the execution branches. JPF stores the state of the system before the it advances
+state matching and backtracking features to visit each of the execution branches. JPF stores the state of the system before it advances
 to a new state. JPF-AWT uses a JPF search listener to store and retrieve the current position of the input script in a specific state so
@@
 % \end{figure}
-Let us take a contacts android application as an example. The application has two Activities: ListContactsActivity and the
-NewContactActivity. The ListContactsActivity contains a list of the current contacts and a button to add new contacts that directs the user
-to the NewContactActivity. The NewContactActivity contains two buttons: the clear button stays on the current Activity and clears its fields
-and the create button starts the \texttt{ListContactsActivity}. Now let us look at figure \ref{fig:contact} containing the input sequence
-for the NewContactActivity.
+Let us take a Contacts Android application as an example. The application has two Activities: ListContactsActivity and the
+NewContactActivity. The ListContactsActivity contains a list of the current contacts and a button to add a new contact that directs the
+user to the NewContactActivity. The NewContactActivity contains two buttons: the clear button stays on the current Activity and clears its
+fields and the create button starts the \texttt{ListContactsActivity}. Now let us look at figure \ref{fig:contact} containing the input
+sequence for the NewContactActivity.
 
@@
 events of a specific Activity. Now, if the create button is pressed the \texttt{ListContactsActivity} will be started and the
-\texttt{ListContactsActivity}'s events specified in its sequence will start executing again.
+\texttt{ListContactsActivity}'s events specified in its section will start executing again.
 
@@
 restarting the NewContactActivity. To address this issue, JPF-ANDROID keeps record of its current Activity. The scripting environment was
-also adapted to store the current position of each section's events for each visited Activity. If the branch returns to a previously visited
+also adapted to store the current position in each visited Activity's script section. If a branch returns to a previously visited
 Activity, its current position in its section is looked up and instead of restarting the section, it continues from its previous position.
@@
 %how they where detected
-JPF is automatically configured to detect thrown exceptions and to stop execution. When JPF-ANDROID was run it firstly detected the
-\texttt{ArithmenticException} due to the division by zero:
+JPF is automatically configured to detect thrown exceptions and to stop execution. When JPF-ANDROID was run on the application it firstly
+detected the \texttt{ArithmenticException} due to the division by zero:
 \begingroup
@@
 and identify Android specific errors using JPF's listener mechanism.
+\vspace*{5pt}
 % The following two commands are all you need in the

### 2012-09-04 Papers/paper.tex
Updating paper changes

@@
        \affaddr{South Africa, 7602}
-       \email{hvdmerwe@cs.sun.ac.za, abvdm@cs.sun.ac.za, wvisser@cs.sun.ac.za }
+       \email{\{hvdmerwe, abvdm, wvisser\}@cs.sun.ac.za }
 }
@@
 
-\keywords{Mobile Application, Java PathFinder, JPF, Android, Verification, Testing}
+\keywords{Mobile Application, Java Pathfinder, JPF, Android, Automatic Verification, Testing, Model Checking}
 
@@
 applications face additional challenges when it comes to application testing. Firstly, they have an event based design which means that
-their application flow is driven by graphical user interface (GUI) and system events. Secondly, Android applications are developed in a
+their application flow is driven by graphical user interface (GUI) and system events~\cite{Hu:2011}. Secondly, Android applications are
+developed in a
 custom implementation of the Java Application Programming Interface (API)  adopted from the Apache Harmony~\cite{harmony} project. The
@@
 implementation of the Java API. As a consequence, Android applications contain many of the same errors as Java applications. These defects
-include, but are not limited to, concurrency issues and common runtime exceptions such as NullPointer Exceptions. It follows that existing
-Java testing frameworks can be adapted to verify Android applications.
+include, but are not limited to, concurrency issues and common run-time exceptions such as null pointer exceptions. It follows that
+existing Java testing frameworks can be adapted to verify Android applications.
 
@@
 This paper describes an extension to Java Pathfinder (JPF)~\cite{JPFDocs} that enables the automatic verification of Android applications on
-the standard Java JVM.
-
-The next section will provide an overview of JPF and Android and how JPF can be used to test Android applications. Thereafter
-the development of the JPF-ANDROID tool will be discussed concluding with two case studies.
+the standard Java JVM. The next section will provide an overview of JPF and Android and how JPF can be used to test Android applications.
+Thereafter, the development of the JPF-ANDROID tool will be discussed concluding with two case studies.
 
 \section{Design}
-\subsection{Java PathFinder}
+\subsection{Java Pathfinder}
 JPF is an automated, open source, analysis engine for Java applications~\cite{JPFDocs}. It is implemented as an explicit state model checker
@@
 threaded, message queue design. All application events are put in a message queue and then handled by the main thread of the application,
-called the EventDispatchThread. JPF-AWT introduced the idea of using a simple event script file to write sequences of user inputs to drive
-the application execution. JPF-AWT models the EventDispatchThread so that when the message queue is empty, it requests an event from the
-script file simulating the event occurring.
+called the \texttt{EventDispatchThread}. JPF-AWT introduced the idea of using a simple event script file to write sequences of user inputs
+to drive the application execution. JPF-AWT models the \texttt{EventDispatchThread} so that when the message queue is empty, it requests an
+event from the script file simulating the event occurring.
 
@@
 JVM. It then extends JPF-AWT's input model to simulate user and system input to drive the application flow. One of the advantages of
-extending JPF is that it has been rigorously tested and can successfully detect many common defects in Java applications. As soon as Android
-applications can run on JPF-ANDROID, common software errors are automatically detected.
+extending JPF is that it has been rigorously tested and can successfully detect many common defects in Java applications. When we run
+Android applications on JPF-ANDROID, common software errors are automatically detected.
 
@@
 native C-libraries. The Dalvik VM is a custom, optimised version of the JVM. For security reasons each Android application is run as a
-separate process in its own Dalvik VM instance~\cite{AndroidSecurity}.  Hence, applications can only communicate with each other and the
-with the Android framework using Android's Binder inter-process communication (IPC) mechanism~\cite{Binder}.
+separate process in its own Dalvik VM instance~\cite{AndroidSecurity}.  Hence, applications can only communicate with each other and with
+the Android framework using Android's Binder inter-process communication (IPC) mechanism~\cite{Binder}.
 
@@
 them to the message queue. The \texttt{Looper} is responsible for continuously looping through these messages and handling them
-appropriately. This could include updating a widget, loading a new activity or processing an Intent.
+appropriately. This could include updating a widget, loading a new activity or processing an \texttt{Intent}.
 
@@
 As discussed above, both Android and AWT applications have a single-threaded application design. That is why JPF-ANDROID's architecture
-is based on JPF-AWT. JPF-ANDROID models Android's message queue by using JPF's MJI
+is based on JPF-AWT.
+JPF- ANDROID models Android's message queue by using JPF's MJI
 environment. When the \texttt{Looper} thread requests a new message from the message queue and it is empty, a call to the native
@@
 set of view components, hence, a unique input sequence. Furthermore, the application flow can switch between these Activities
-at any point of execution. In other words, if we do not know in what Activity the application is, we can not script the following events.
+at any point of execution. In other words, if we do not know which Activity has the focus (or is in it's resumed state), we can not script
+the following events.
 

### 2012-09-04 Papers/paper.tex
final paper changes

@@
 Software testing and verification plays an important role in determining the quality and robustness of software. These are two very
-important attributes of mobile applications. Especially since users currently have more than 600 000 applications to choose from on the
+important attributes of mobile applications, especially since users currently have more than 600 000 applications to choose from on the
 Google Play Market.
 
-Although software testing is so important, it is often neglected due to its complex and time consuming process. Android
+Although software testing is so important, it is often neglected due to it being a complex and time consuming process. Android
 applications face additional challenges when it comes to application testing. Firstly, they have an event based design which means that
@@
 application testing is often omitted altogether. The simplest way to test GUI applications is manual black-box testing.
-But, this is a time consuming, error prone and expensive~\cite{AccessibilityTech} process. One way to reduce this high cost, is to  automate
+But, this is a time consuming, error prone and expensive process~\cite{AccessibilityTech}. One way to reduce this high cost, is to  automate
 the testing of GUI -- in this case Android -- applications~\cite{AccessibilityTech}.
@@
 Robolectric~\cite{robolectric}, a JUnit testing framework running on the JVM,  intercepts the loading of Android classes and then uses
-shadows classes that model these classes.
+shadow classes that model these classes.
 
@@
 implementation of the Java API. As a consequence, Android applications contain many of the same errors as Java applications. These defects
-include, but are not limited to, concurrency issues and common run-time exceptions such as null pointer exceptions. It follows that
+include, but are not limited to, concurrency issues and common run-time exceptions such as null pointer dereferencing exceptions. It follows that
 existing Java testing frameworks can be adapted to verify Android applications.
@@
 
-As shown in figure \ref{fig:android}, the Android OS is built on top of a modified Linux kernel. The kernel provides a layer of abstraction
+As shown in Figure \ref{fig:android}, the Android OS is built on top of a modified Linux kernel. The kernel provides a layer of abstraction
 on top of its low level functionality such as process, memory, user, network and thread management. On top of the Android kernel is a set of
@@
 Android has one main application called the system process. The system process contains services responsible for performing the main
-tasks of the system including:
+tasks of the system, including:
 \vspace{-10pt}
@@
 them to the message queue. The \texttt{Looper} is responsible for continuously looping through these messages and handling them
-appropriately. This could include updating a widget, loading a new activity or processing an \texttt{Intent}.
+appropriately. This could include updating a widget, loading a new activity or processing an \texttt{Intent} (see below).
 
@@
 The Android framework is very large and one of the main challenges of JPF-ANDROID is to decide which parts of the system to model. The more
-of the Android framework is modelled, the more realistic the model is and the more errors can be found. But, if too much
+of the Android framework is modelled, the more realistic the model is and the more errors can be found. However, if too much
 of the framework is modelled the scheduling possibilities increase exponentially which means that the search space can become too big to
@@
 %JPF-ANDROID BASED ON JPF_AWT  why and how does it work?
-As discussed above, both Android and AWT applications have a single-threaded application design. That is why JPF-ANDROID's architecture
-is based on JPF-AWT.
-JPF- ANDROID models Android's message queue by using JPF's MJI
+As discussed above, both Android and AWT applications have a single-threaded application design and therefore JPF-ANDROID is based on JPF-AWT's architecture.
+\linebreak JPF-ANDROID models Android's message queue by using JPF's MJI
 environment. When the \texttt{Looper} thread requests a new message from the message queue and it is empty, a call to the native
@@
 % what is input script, how does it work(its function) and how are does it look
-JPF-AWT's script consist of a list of UI events. These events are executed one-by-one when the message queue it empty. To allow users to
+JPF-AWT's script consist of a list of UI events. These events are read one-by-one when the message queue it empty. To allow users to
 script system events, variables were added to the scripting language in JPF-ANDROID. Variable names are identified by the ``@'' in front of
 the variable's name as '\$' is already used in JPF-AWT to identify UI components. These variable can be used to construct most Intent
-objects. For example, a script file that sends an \texttt{Intent} to start the \texttt{SampleActivity} is shown in figure \ref{fig:start}
+objects. For example, a script file that sends an \texttt{Intent} to start the \texttt{SampleActivity} is shown in Figure \ref{fig:start}
 \begin{figure}
@@
 JPF-ANDROID scripts also adopted the \textbf{REPEAT} and \textbf{ANY} constructs from JPF-AWT. \textbf{REPEAT} constructs repeat a list of
-events a specified number of times. \textbf{ANY} constructs take a list of events as parameters and then uses a ChoiceGenerator and JPF's
+events a specified number of times. \textbf{ANY} constructs take a list of non-deterministic events as parameters and then uses a ChoiceGenerator and JPF's
 state matching and backtracking features to visit each of the execution branches. JPF stores the state of the system before it advances
@@
 set of view components, hence, a unique input sequence. Furthermore, the application flow can switch between these Activities
-at any point of execution. In other words, if we do not know which Activity has the focus (or is in it's resumed state), we can not script
+at any point of execution. In other words, if we do not know which Activity has the focus (or is in it's resumed state), we cannot script
 the following events.
@@
 % \end{figure}
-Let us take a Contacts Android application as an example. The application has two Activities: ListContactsActivity and the
-NewContactActivity. The ListContactsActivity contains a list of the current contacts and a button to add a new contact that directs the
-user to the NewContactActivity. The NewContactActivity contains two buttons: the clear button stays on the current Activity and clears its
-fields and the create button starts the \texttt{ListContactsActivity}. Now let us look at figure \ref{fig:contact} containing the input
-sequence for the NewContactActivity.
+Let us take a Contacts Android application as an example. The application has two Activities: the \texttt{ListContactsActivity} and the
+\texttt{NewContactActivity}. The \texttt{ListContactsActivity} contains a list of the stored contacts and a button to add a new contact that directs the
+user to the \texttt{NewContactActivity}. The \texttt{NewContactActivity} contains two buttons: the clear button stays on the current Activity and clears its
+fields and the create button starts the \texttt{ListContactsActivity}. Now let us look at Figure \ref{fig:contact} containing the input
+sequence for the \texttt{NewContactActivity}.
 
@@
 and the following event is not valid any more. This drastically restricts the number of sequences that can be scripted in the file. To
-address this issue, we included the use of sections in the input script (see figure \ref{fig:contact2}). Each section groups the input
-events of a specific Activity. Now, if the create button is pressed the \texttt{ListContactsActivity} will be started and the
-\texttt{ListContactsActivity}'s events specified in its section will start executing again.
+address this issue, we included the use of sections in the input script (see Figure \ref{fig:contact2}). Each section groups the input
+events of a specific Activity. Now, if the create button is pressed, the \texttt{ListContactsActivity} will be started and the events
+specified in its section will start executing again.
 
@@
 \vspace*{2mm}
-\hspace*{2mm}1. \textbf{SECTION} default \{\\
-\hspace*{2mm}2. \hspace*{5mm}@startIntent.setComponent(``ListContactsActivity'')\\
-\hspace*{2mm}3. \hspace*{5mm}startActivity(@startIntent)\\
-\hspace*{2mm}4. \}\\
-\hspace*{2mm}5. \\
-\hspace*{2mm}6. \textbf{SECTION} ListContactsActivity \{\\
-\hspace*{2mm}7. \hspace*{5mm}\$createButton.onClick()\\
-\hspace*{2mm}8. \hspace*{5mm}\$list.setSelectedIndex([0-3])\\
-\hspace*{2mm}9. \}\\
+\hspace*{2mm}1.\; \textbf{SECTION} default \{\\
+\hspace*{2mm}2.\; \hspace*{5mm}@startIntent.setComponent(``ListContactsActivity'')\\
+\hspace*{2mm}3.\; \hspace*{5mm}startActivity(@startIntent)\\
+\hspace*{2mm}4.\; \}\\
+\hspace*{2mm}5.\; \\
+\hspace*{2mm}6.\; \textbf{SECTION} ListContactsActivity \{\\
+\hspace*{2mm}7.\; \hspace*{5mm}\$createButton.onClick()\\
+\hspace*{2mm}8.\; \hspace*{5mm}\$list.setSelectedIndex([0-3])\\
+\hspace*{2mm}9.\; \}\\
 \hspace*{2mm}10. \\
@@
 \label{fig:contact2}
+\vspace{-10pt}
 \end{figure}
@@
 The addition of the sections in the input script lead to infinite event sequences. In the above example, an infinite loop occurs when the
-create button is pressed on the NewContactActivity window. This will stop the execution of the NewContactActivity section and restart
-the ListContactsActivity section's events. When the ListContactsActivity's section is restarted, it again clicks on the createButton
-restarting the NewContactActivity. To address this issue, JPF-ANDROID keeps record of its current Activity. The scripting environment was
+create button is pressed on the \texttt{NewContactActivity} window. This will stop the execution of the \texttt{NewContactActivity} section and restart
+the \texttt{ListContactsActivity} section's events. When the \texttt{ListContactsActivity}'s section is restarted, it again clicks on the create button
+restarting the \texttt{NewContactActivity}. To address this issue, JPF-ANDROID keeps record of its current Activity. The scripting environment was
 also adapted to store the current position in each visited Activity's script section. If a branch returns to a previously visited
@@
 between these Activities, the current state of the calculator is preserved. This state includes the intermediate values and current
-operation. This state information is bundled with the \texttt{Intent} that starts then next Activity.
+operation. This state information is bundled with the \texttt{Intent} that starts the next Activity.
+
 \begin{figure}
-
 \frame{
@@
 \label{fig:calc}
+\vspace{-10pt}
 \end{figure}
@@
 The calculator application contains two errors. When the user divides a value by zero, an uncaught
-\texttt{ArithmeticException} is thrown by the application which causes Android to kill the application. Secondly the application neglected
-to attach the state information to the Intent that is passed to the next Activity. When the user switches to the other Activity a
-\texttt{NullPointerException} is thrown when it tries to read the state information from the Intent.
+\texttt{ArithmeticException} is thrown by the application which causes Android to kill the application. Secondly, the application neglected
+to attach the state information to the \texttt{Intent} that is passed to the next Activity. When the user switches to the other Activity a
+\texttt{NullPointerException} is thrown when it tries to read the state information from the \texttt{Intent}.
 
-To detect these errors we will use the test script in figure~\ref{fig:calc}. The scripting environment interprets the script into the
+To detect these errors we will use the test script in Figure~\ref{fig:calc}. The scripting environment interprets the script into the
 following input sequences:
@@
 \end{align*}
-Each of the ten number buttons are pressed followed by a simple operation and another number or a complex operation.
-
-%how they where detected
+Each of the ten number buttons are pressed followed by a simple operation and another number or a complex operation. Although it is possible
+to input numbers consisting of multiple digits including floating point numbers, for illustration purposes this was left out of the input script.
 JPF is automatically configured to detect thrown exceptions and to stop execution. When JPF-ANDROID was run on the application it firstly
 detected the \texttt{ArithmenticException} due to the division by zero:
+
+\vspace*{-10pt}
 \begingroup
@@
 \endgroup
+\vspace*{-10pt}
 After this error was fixed JPF-ANDROID detected the \texttt{NullPointerException} in the same way.
@@
 would not have detected this error. The second error is challenging to detect due to the fact that it only occurs when the flow of Activity
-classes are modelled.
+classes are tested.
 
@@
 The next case study is a very simple application demonstrating how JPF-ANDROID detects a deadlock in a Android application. When the
-\texttt{Looper}/main thread of an application is caught in a deadlock, the Android OS kills the application and displays an
-Application Not Responding (ANR) dialog. But, Android does not detect a deadlock if it occurs between other asynchronous threads. This
+\texttt{Looper} thread of an application is caught in a deadlock, the Android OS kills the application and displays an
+Application Not Responding (ANR) dialog. However, Android does not detect a deadlock if it occurs between other asynchronous threads. This
 sample application spawns two asynchronous threads that deadlock. The application has one Activity with two
 buttons. The first button spawns the first thread and the second button spawns the second thread. After a while these two thread deadlock
-and are then blocked forever, waiting for each other. The input script for the application is given in figure \ref{fig:deadlock}.
+and are then blocked forever, waiting for each other. The input script for the application is given in Figure \ref{fig:deadlock}. JPF is then
+configured to listen for deadlocks and schedules the threads in all possible ways to detect the deadlock.
+
 \begin{figure}
+
 \frame{
@@
 }}}}
-\vspace{-15pt}
+
 \caption{Input script for Deadlock application}
 \label{fig:deadlock}
+\vspace{-10pt}
 \end{figure}
 
-JPF is then configured to listen for deadlocks and schedules the threads in all possible ways to detect the deadlock.
+\vspace*{-10pt}
 \begingroup
@@
 \endgroup
-
+\vspace*{-10pt}
 \section{Future Work}
@@
 Another extension that will be added to JPF-ANDROID is coverage testing. JPF has many coverage extensions available so we will be adapting
-one these extensions to work on Android applications.
+one these extensions to work on Android applications~\cite{coverage}. Coverage testing is especially important to find errors related to the Android Activity
+life cycle such as the null pointer exception mentioned above.
 
@@
 
-This extension provides a basis on which Android applications can be tested. It can later be extended to verify functional requirements
-and identify Android specific errors using JPF's listener mechanism.
-\vspace*{5pt}
+This extension provides a basis on which Android applications can be tested.
+It can later be extended to verify functional requirements and identify Android specific errors using JPF's listener mechanism.
+
+% \vspace*{5pt}
 % The following two commands are all you need in the

### 2012-10-02 jpf-android/src/classes/android/app/Activity.java
Activity life cycle fixes

@@ -1,8 +1,11 @@
 package android.app;
 
+import java.util.HashMap;
+
 import android.content.Context;
 import android.content.Intent;
 import android.content.pm.ActivityInfo;
+import android.content.res.Configuration;
 import android.os.Bundle;
 import android.os.Handler;
 import android.view.ContextThemeWrapper;
@@ -14,6 +17,21 @@ import com.android.internal.policy.PolicyManager;
 
 public class Activity extends ContextThemeWrapper {
   private static int uniqueID = 0;
+  private static final String TAG = "Activity";
+
+  /** Standard activity result: operation cancelled. */
+  public static final int RESULT_CANCELED = 0;
+  /** Standard activity result: operation succeeded. */
+  public static final int RESULT_OK = -1;
+  /** Start of user-defined activity results. */
+  public static final int RESULT_FIRST_USER = 1;
+
+  private static final String WINDOW_HIERARCHY_TAG = "android:viewHierarchyState";
+  private static final String FRAGMENTS_TAG = "android:fragments";
+  private static final String SAVED_DIALOG_IDS_KEY = "android:savedDialogIds";
+  private static final String SAVED_DIALOGS_TAG = "android:savedDialogs";
+  private static final String SAVED_DIALOG_KEY_PREFIX = "android:dialog_";
+  private static final String SAVED_DIALOG_ARGS_KEY_PREFIX = "android:dialog_args_";
 
   private Context mBase;
   private Application mApplication;
@@ -26,14 +44,27 @@ public class Activity extends ContextThemeWrapper {
 
   Activity mParent; // Reference to the activity that started this activity
   boolean mCalled;
-  // Activity Locks
-  boolean mResumed;
+  boolean mCheckedForLoaderManager;
+  boolean mLoadersStarted;
+  /* package */boolean mResumed;
   private boolean mStopped;
   boolean mFinished;
   boolean mStartedActivity;
-
   /** true if the activity is going through a transient pause */
-  boolean mTemporaryPause = false;
+  /* package */boolean mTemporaryPause = false;
+  /** true if the activity is being destroyed in order to recreate it with a new configuration */
+  /* package */boolean mChangingConfigurations = false;
+  /* package */int mConfigChangeFlags;
+  /* package */Configuration mCurrentConfig;
+
+  static final class NonConfigurationInstances {
+    Object activity;
+    HashMap<String, Object> children;
[…]

### 2012-10-02 jpf-android/src/classes/android/app/ActivityManagerProxy.java

@@ -4,7 +4,7 @@ import android.content.Intent;
 
 public class ActivityManagerProxy {
 
-  public static native void startActivityProxy(Intent intent);
+  public static native void startActivityProxy(Intent intent, int requestCode);
 
   public static native void stopServiceProxy();
 

### 2012-10-02 jpf-android/src/classes/android/app/ActivityThread.java

@@ -1,9 +1,9 @@
 package android.app;
 
 import java.util.HashMap;
-import java.util.List;
 
 import android.content.Intent;
+import android.content.res.Configuration;
 import android.os.Bundle;
 import android.os.Handler;
 import android.os.IBinder;
@@ -12,6 +12,18 @@ import android.os.Message;
 import android.util.Log;
 import android.util.LogPrinter;
 import android.view.Window;
+
+final class SuperNotCalledException extends android.util.AndroidRuntimeException {
+  public SuperNotCalledException(String msg) {
+    super(msg);
+  }
+}
+
+final class RemoteServiceException extends android.util.AndroidRuntimeException {
+  public RemoteServiceException(String msg) {
+    super(msg);
+  }
+}
 
 /**
  * This manages the execution of the main thread in an application process, scheduling and executing
@@ -34,6 +46,7 @@ public final class ActivityThread {
   final HashMap<IBinder, Service> mServices = new HashMap<IBinder, Service>();
 
   final ApplicationThread mAppThread = new ApplicationThread();
+  Configuration mConfiguration;
 
   private class ApplicationThread {
 
@@ -60,8 +73,8 @@ public final class ActivityThread {
       queueOrSendMessage(H.RESUME_ACTIVITY, null, ident, 0);
     }
 
-    public final void schedulePauseActivity(int ident) {
-      queueOrSendMessage(H.PAUSE_ACTIVITY, null, ident, 0);
+    public final void schedulePauseActivity(int ident, boolean finished) {
+      queueOrSendMessage(finished ? H.PAUSE_ACTIVITY_FINISHING : H.PAUSE_ACTIVITY, null, ident, 0);
     }
 
     public final void scheduleStopActivity(int ident) {
@@ -72,17 +85,22 @@ public final class ActivityThread {
       queueOrSendMessage(H.DESTROY_ACTIVITY, null, ident, 0);
     }
 
-    public final void scheduleSendResult(Activity activity, List<ResultInfo> results) {
-      // ResultData res = new ResultData();
-      // res.token = token;
-      // res.results = results;
-      // queueOrSendMessage(H.SEND_RESULT, res);
+    public final void scheduleSendResult(int ident, ResultInfo result) {
+      queueOrSendMessage(H.SEND_RESULT, result, 0, 0);
     }
+
+    private void scheduleRelaunchActivity() {
+      queueOrSendMessage(H.RELAUNCH_ACTIVITY, null, 0, 0);
[…]

### 2012-10-02 jpf-android/src/classes/android/content/res/Configuration.java

@@ -1,0 +1,978 @@
+package android.content.res;
+
+import java.util.Locale;
+
+import android.util.LocaleUtil;
+
+/**
+ * This class describes all device configuration information that can impact the resources the application
+ * retrieves. This includes both user-specified configuration options (locale and scaling) as well as device
+ * configurations (such as input modes, screen size and screen orientation).
+ * <p>
+ * You can acquire this object from {@link Resources}, using {@link Resources#getConfiguration}. Thus, from an
+ * activity, you can get it by chaining the request with {@link android.app.Activity#getResources}:
+ * </p>
+ * 
+ * <pre>
+ * Configuration config = getResources().getConfiguration();
+ * </pre>
+ */
+public final class Configuration {// implements Parcelable, Comparable<Configuration> {
+  /**
+   * Current user preference for the scaling factor for fonts, relative to the base density scaling.
+   */
+  public float fontScale;
+
+  /**
+   * IMSI MCC (Mobile Country Code). 0 if undefined.
+   */
+  public int mcc;
+
+  /**
+   * IMSI MNC (Mobile Network Code). 0 if undefined.
+   */
+  public int mnc;
+
+  /**
+   * Current user preference for the locale.
+   */
+  public Locale locale;
+
+  /**
+   * Locale should persist on setting. This is hidden because it is really questionable whether this is the
+   * right way to expose the functionality.
+   * 
+   * @hide
+   */
+  public boolean userSetLocale;
+
+  /** Constant for {@link #screenLayout}: bits that encode the size. */
+  public static final int SCREENLAYOUT_SIZE_MASK = 0x0f;
+  /**
+   * Constant for {@link #screenLayout}: a {@link #SCREENLAYOUT_SIZE_MASK} value indicating that no size has
+   * been set.
+   */
+  public static final int SCREENLAYOUT_SIZE_UNDEFINED = 0x00;
+  /**
+   * Constant for {@link #screenLayout}: a {@link #SCREENLAYOUT_SIZE_MASK} value indicating the screen is at
+   * least approximately 320x426 dp units. See <a href="{@docRoot}
[…]

### 2012-10-02 jpf-android/src/classes/android/content/res/DisplayMetrics.java

@@ -1,0 +1,5 @@
+package android.content.res;
+
+public class DisplayMetrics {
+
+}

### 2012-10-02 jpf-android/src/classes/android/content/res/Drawable.java

@@ -1,0 +1,5 @@
+package android.content.res;
+
+public class Drawable {
+
+}

### 2012-10-02 jpf-android/src/classes/android/content/res/Movie.java

@@ -1,0 +1,5 @@
+package android.content.res;
+
+public class Movie {
+
+}

### 2012-10-02 jpf-android/src/classes/android/content/res/Resources.java

@@ -1,0 +1,962 @@
+package android.content.res;
+
+import java.io.IOException;
+import java.io.InputStream;
+
+import javax.swing.text.AttributeSet;
+
+public class Resources {
+  static final String TAG = "Resources";
+  Configuration mConfiguration = new Configuration();
+
+  public static int selectDefaultTheme(int curTheme, int targetSdkVersion) {
+    return 0;
+  }
+
+  public static int selectSystemTheme(int curTheme, int targetSdkVersion, int orig, int holo,
+                                      int deviceDefault) {
+    return 0;
+  }
+
+  /**
+   * This exception is thrown by the resource APIs when a requested resource can not be found.
+   */
+  public static class NotFoundException extends RuntimeException {
+    public NotFoundException() {
+    }
+
+    public NotFoundException(String name) {
+      super(name);
+    }
+  }
+
+  /**
+   * Create a new Resources object on top of an existing set of assets in an AssetManager.
+   * 
+   * @param assets
+   *          Previously created AssetManager.
+   * @param metrics
+   *          Current display metrics to consider when selecting/computing resource values.
+   * @param config
+   *          Desired device configuration to consider when selecting/computing resource values (optional).
+   */
+  public Resources(Configuration config) {
+    mConfiguration = config;
+  }
+
+  /**
+   * Return a global shared Resources object that provides access to only system resources (no application
+   * resources), and is not configured for the current screen (can not use dimension units, does not change
+   * based on orientation, etc).
+   */
+  public static Resources getSystem() {
+    return null;
+  }
+
+  /**
+   * Return the string value associated with a particular resource ID. The returned object will be a String if
+   * this is a plain string; it will be some other type of CharSequence if it is styled. {@more}
+   * 
+   * @param id
+   *          The desired resource identifier, as generated by the aapt tool. This integer encodes the
+   *          package, type, and resource entry. The value 0 is an invalid identifier.
+   * 
+   * @throws NotFoundException
+   *           Throws NotFoundException if the given ID does not exist.
+   * 
+   * @return CharSequence The string data associated with the resource, plus possibly styled text information.
+   */
+  public CharSequence getText(int id) throws NotFoundException {
+
+    return null;
+  }
+
+  /**
+   * Return the character sequence associated with a particular resource ID for a particular numerical
+   * quantity.
+   * 
+   * <p>
+   * See <a href="{@docRoot}guide/topics/resources/string-resource.html#Plurals">String Resources</a> for more
+   * on quantity strings.
+   * 
[…]

### 2012-10-02 jpf-android/src/classes/android/content/res/TypedValue.java

@@ -1,0 +1,5 @@
+package android.content.res;
+
+public class TypedValue {
+
+}

### 2012-10-02 jpf-android/src/classes/android/content/res/XmlPullParserException.java

@@ -1,0 +1,5 @@
+package android.content.res;
+
+public class XmlPullParserException extends Exception {
+
+}

### 2012-10-02 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_app_ActivityManagerProxy.java

@@ -79,7 +79,11 @@ public class JPF_android_app_ActivityManagerProxy {
     if (action.action.equals("startActivity")) {
       String intentName = (String) action.arguments[0];
       int intentref = getJPFIntent(env, intentName);
-      startActivity(env, 0, intentref);
+      startActivity(env, 0, intentref, -1);
+    } else if (action.action.equals("changeLayout")) {
+      String layout = (String) action.arguments[0];
+
+      changeLayout(env, 0, 1);
 
     } else if (action.action.equals("backButton")) {
       backButton(env);
@@ -88,12 +92,30 @@ public class JPF_android_app_ActivityManagerProxy {
     }
   }
 
+  /**
+   * This is always called to start an Activity
+   * 
+   * @param env
+   * @param orientation
+   *          the new orientation
+   */
+  private static void changeLayout(MJIEnv env, int clsRef, int orientation) {
+    log.fine("changing layout to " + orientation);
+
+    // schedule launch of activity
+    int appRef = JPF_android_app_ActivityThread.getApplicationRef();
+    String methodName = "performConfigurationChange()V";
+    int[] args = {};
+
+    callMethod(env, appRef, methodName, args);
+
+  }
+
   private static void backButton(MJIEnv env) {
     // schedule launch of activity
     int appRef = JPF_android_app_ActivityThread.getApplicationRef();
     String methodName = "performBackPressed()V";
     int[] args = {};
-
     callMethod(env, appRef, methodName, args);
 
   }
@@ -133,13 +155,13 @@ public class JPF_android_app_ActivityManagerProxy {
    * @param clsRef
    * @param intentRef
    */
-  public static void startActivityProxy(MJIEnv env, int clsRef, int intentRef) {
+  public static void startActivityProxy(MJIEnv env, int clsRef, int intentRef, int requestcode) {
     ThreadInfo ti = env.getThreadInfo();
 
     // so that the method is not called twice on return from making direct
     // call
     if (!ti.hasReturnedFromDirectCall(UIACTION)) {
-      startActivity(env, clsRef, intentRef);
+      startActivity(env, clsRef, intentRef, -1);
     }
   }
 
@@ -150,8 +172,7 @@ public class JPF_android_app_ActivityManagerProxy {
    * @param intentRef
    *          the reference to the intent starting the activity
    */
-  private static void startActivity(MJIEnv env, int clsRef, int intentRef) {
-    // TODO pause activity currently active etc
[…]

### 2012-10-02 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_content_res_Resources.java

@@ -1,0 +1,315 @@
+package gov.nasa.jpf.android;
+
+import gov.nasa.jpf.Config;
+import gov.nasa.jpf.JPF;
+import gov.nasa.jpf.jvm.MJIEnv;
+
+import java.io.FileInputStream;
+import java.io.FileNotFoundException;
+import java.io.InputStream;
+import java.util.HashMap;
+import java.util.Scanner;
+import java.util.logging.Logger;
+
+import javax.xml.parsers.DocumentBuilder;
+import javax.xml.parsers.DocumentBuilderFactory;
+
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+import org.w3c.dom.Node;
+import org.w3c.dom.NodeList;
+
+import android.view.LayoutInflater;
+import android.view.Window;
+
+public class JPF_android_content_res_Resources {
+  static Logger log = JPF.getLogger("gov.nasa.jpf.android");
+
+  private String ID_HEADER = "public static final class id {";
+  private String LAYOUT_HEADER = "public static final class layout {";
+  private String STRING_HEADER = "public static final class string {";
+  private String MENU_HEADER = "public static final class menu {";
+  private String STYLE_HEADER = "public static final class style {";
+  private String BOOL_HEADER = "public static final class bool {";
+  private String COLOR_HEADER = "public static final class color {";
+  private String ARRAY_HEADER = "public static final class array {";
+  private String ANIM_HEADER = "public static final class anim {";
+  private String INTEGER_HEADER = "public static final class int {";
+
+  private String FOOTER = "}";
+
+  DocumentBuilderFactory dbf = DocumentBuilderFactory.newInstance();
+
+  private HashMap<String, ViewEntry> componentMap = new HashMap<String, ViewEntry>();
+
+  /**
+   * Maps the resource ID of a layout to the name of the layout file. This information is read from the R.java
+   * class and stored as a map fir quick lookup by the {@link LayoutInflater}.
+   */
+  private HashMap<Integer, String> layoutMap = new HashMap<Integer, String>();
+
+  private HashMap<Integer, String> stringsMap = new HashMap<Integer, String>();
+
+  private HashMap<Integer, String> drawableMap = new HashMap<Integer, String>();
+
+  private HashMap<Integer, String> menuMap = new HashMap<Integer, String>();
+  String rPath = "";
+
+  /**
+   * Sets up the environment for the {@link Window} class. Creates componentMap and layoutMap.
[…]

### 2012-10-02 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_os_MessageQueue.java

@@ -40,6 +40,8 @@ public class JPF_android_os_MessageQueue {
     forceActionStates = conf.getBoolean("awt.force_states", true);
 
     String scriptName = conf.getString("awt.script");
+    System.out.println("scriptName");
+
     if (scriptName == null) {
       scriptName = conf.getString("inspect.script");
 

### 2012-10-02 Papers/paper.tex
Updated Paper

@@
 \documentclass{acm_proc_article-sp}
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd{\maketitle}{\@copyrightspace}{}{}{}
+\makeatother
+% \usepackage{flushend}
+
 \begin{document}
@@
 a Java model checking engine. JPF-ANDROID provides a simplified model of the Android framework on which an Android application can run. It then allows
-the user to script input events to drive the application flow. JPF-ANDROID provides a way to detect common property violations such as deadlocks and runtime exceptions
+the user to script input events to drive the \linebreak application flow. JPF-ANDROID provides a way to detect common property violations such as deadlocks and runtime exceptions
 in Android applications.
@@
 The most common way to automate Android application testing is to run tests on the Dalvik VM on a
-physical device/emulator. Testing frameworks such as the MonkeyRunner and Robotium make use of Android's built-in JUnit
+physical device/emulator. Testing frameworks such as the MonkeyRunner~\cite{TestingAndroid} and Robotium~\cite{robotium} make use of Android's built-in JUnit
 framework~\cite{TestingAndroid} to run test suites on the device. Running tests on the Dalvik VM is slow as they have to be instrumented and
 each test sequence has to be defined and executed sequentially. Other projects use alternative ways to automatically generate input by
-manipulating the built in accessibility technologies~\cite{AccessibilityTech} or by re-implementing the Android
-keyboard~\cite{KeyboardModel}. Mockito and Android Mock allow JUnit testing on the Dalvik VM by using mock Android classes. The advantage of
+manipulating the built in accessibility technologies~\cite{AccessibilityTech}, by re-implementing the Android
+keyboard~\cite{KeyboardModel} or by instrumenting the Dalvik VM to generate logs that are analysed to detect common errors~\cite{hu}.
+Mockito~\cite{mockito} and Android Mock~\cite{androidMock} allow JUnit testing on the Dalvik VM by using mock Android classes.
+The advantage of
 testing applications on the Dalvik VM is that we can physically emulate input events on the device. The disadvantage is that it is not
@@
 Another approach is to test Android applications using the Java Virtual Machine (JVM). There are different ways of implementing such
-a framework. Android lint, for example, makes use of static analysis to identify common errors in applications.
+a framework. Android Lint, for example, makes use of static analysis to identify common errors in applications.
 Robolectric~\cite{robolectric}, a JUnit testing framework running on the JVM,  intercepts the loading of Android classes and then uses
@@
 JVM. It then extends JPF-AWT's input model to simulate user and system input to drive the application flow. One of the advantages of
-extending JPF is that it has been rigorously tested and can successfully detect many common defects in Java applications. When we run
-Android applications on JPF-ANDROID, common software errors are automatically detected.
+extending JPF is that it has been rigorously tested and can successfully detect many common defects in Java applications. When Android applications
+run on JPF using JPF-ANDROID, common software errors are automatically detected.
 
@@
  \item [WindowManager] allows applications to draw on the screen and forwards UI input to the application.
- \item [PackageManager] stores information on the application packages installed on the device
+ \item [PackageManager] stores information on the application \linebreak packages installed on the device
 \end{description}
@@
 safe~\cite{SingleThread}. In Android, this main thread is called the \texttt{Looper} thread. The \texttt{Looper} has a message queue
-attached to it containing all application events to be dispatched. UI and system events are scheduled on the main \texttt{Looper} by adding
+attached to it containing all application events to be dispatched. UI and system events are scheduled on the \texttt{Looper} by adding
 them to the message queue. The \texttt{Looper} is responsible for continuously looping through these messages and handling them
@@
  \item [ActivityThread]   the main entry-point to the application. It controls and manages the application components and their input.
- \item [Application components] including Activity, Service, Broadcast Receiver and Content Provider. 
+ \item [Application components] including Activity, Service, \linebreak Broadcast Receiver and Content Provider. 
  \item [Window and View structure] The view hierarchy is modelled including the widgets and the window classes.
@@
 user to the \texttt{NewContactActivity}. The \texttt{NewContactActivity} contains two buttons: the clear button stays on the current Activity and clears its
-fields and the create button starts the \texttt{ListContactsActivity}. Now let us look at Figure \ref{fig:contact} containing the input
-sequence for the \texttt{NewContactActivity}.
+fields and the create button starts the \texttt{ListContactsActivity}. Figure \ref{fig:contact} contains the\texttt{NewContactActivity}'s events.
 
@@
 
-The problem occurs in the ANY structure. When the create button is clicked the application changes to the ListContactsActivity
+The problem occurs in the ANY structure. When the create button is clicked the application changes to the \texttt{ListContactsActivity}
 and the following event is not valid any more. This drastically restricts the number of sequences that can be scripted in the file. To
@@
 The addition of the sections in the input script lead to infinite event sequences. In the above example, an infinite loop occurs when the
-create button is pressed on the \texttt{NewContactActivity} window. This will stop the execution of the \texttt{NewContactActivity} section and restart
+create button is pressed on the \texttt{NewContactActivity} window. This will stop execution of the \texttt{NewContactActivity} section and restart
 the \texttt{ListContactsActivity} section's events. When the \texttt{ListContactsActivity}'s section is restarted, it again clicks on the create button
 restarting the \texttt{NewContactActivity}. To address this issue, JPF-ANDROID keeps record of its current Activity. The scripting environment was
-also adapted to store the current position in each visited Activity's script section. If a branch returns to a previously visited
+also adapted to store the current position in each visited Activity's section. If a branch returns to a previously visited
 Activity, its current position in its section is looked up and instead of restarting the section, it continues from its previous position.
@@
 \hspace*{2mm}6. \}\\
-\hspace*{2mm}7. \textbf{SECTION} ScientificActivity  \{\\
-\hspace*{2mm}8. \hspace*{5mm}\textbf{ANY} \{\,\$button<Sin|Cos|Tan>.onClick()\,\}\\
-\hspace*{2mm}9. \}\\
+\hspace*{2mm}7. \\
+\hspace*{2mm}8. \textbf{SECTION} ScientificActivity  \{\\
+\hspace*{2mm}9. \hspace*{5mm}\textbf{ANY} \{\,\$button<Sin|Cos|Tan>.onClick()\,\}\\
+\hspace*{2mm}10. \}\\
 }}}}
@@
 \texttt{NullPointerException} is thrown when it tries to read the state information from the \texttt{Intent}.
-
-To detect these errors we will use the test script in Figure~\ref{fig:calc}. The scripting environment interprets the script into the
+To detect these errors we will use the test script in Figure~\ref{fig:calc}.
+The scripting environment interprets the script into the
 following input sequences:
@@
 
-Another extension that will be added to JPF-ANDROID is coverage testing. JPF has many coverage extensions available so we will be adapting
+Another extension that will be added to JPF-ANDROID is coverage testing. JPF has many coverage extensions avail-
+\balancecolumns
+able so we will be adapting
 one these extensions to work on Android applications~\cite{coverage}. Coverage testing is especially important to find errors related to the Android Activity
@@
 \bibliographystyle{abbrv}
+% \bibliography{sigproc}
 \scriptsize

### 2012-10-02 Examples/SampleProject/src/com/example/com/ResultActivity.java
Updating sample project

@@ -1,0 +1,112 @@
+package com.example.com;
+
+import android.app.Activity;
+import android.content.Intent;
+import android.os.Bundle;
+import android.view.View;
+import android.view.View.OnClickListener;
+import android.widget.Button;
+
+public class ResultActivity extends Activity {
+  @Override
+  public void onCreate(Bundle savedInstanceState) {
+    super.onCreate(savedInstanceState);
+    setContentView(R.layout.main);
+    System.out.println("Result Activity: onCreate");
+
+    Button b1 = (Button) findViewById(R.id.buttonText1);
+
+    b1.setOnClickListener(new OnClickListener() {
+      @Override
+      public void onClick(View v) {
+        setResult(1);
+      }
+    });
+  }
+
+  @Override
+  protected void onPostCreate(Bundle savedInstanceState) {
+    System.out.println("3 onPostCreate()");
+
+    super.onPostCreate(savedInstanceState);
+
+  }
+
+  @Override
+  protected void onStart() {
+    super.onStart();
+    System.out.println("3 onStart()");
+
+  }
+
+  @Override
+  protected void onRestart() {
+    super.onRestart();
+    System.out.println("3 onRestart()");
+  }
+
+  @Override
+  protected void onResume() {
+    super.onResume();
+    System.out.println("3  onResume()");
+
+  }
+
+  @Override
+  protected void onPostResume() {
+    super.onPostResume();
+    System.out.println("3  onPostResume()");
+  }
+
+  @Override
+  protected void onPause() {
+    super.onPause();
+    System.out.println("3  onPause()");
+  }
+
+  @Override
+  protected void onStop() {
+    super.onStop();
+    System.out.println("3  onStop()");
+
+  }
+
+  @Override
+  protected void onDestroy() {
+    super.onDestroy();
+    System.out.println("3  onDestroy()");
+
+  }
+
+  @Override
+  public Intent getIntent() {
+    System.out.println("3  getIntent()");
+    return super.getIntent();
+  }
+
+  @Override
+  protected void onRestoreInstanceState(Bundle savedInstanceState) {
+    System.out.println("3  onRestoreInstanceState()");
+    super.onRestoreInstanceState(savedInstanceState);
+  }
+
+  @Override
+  protected void onNewIntent(Intent intent) {
+    System.out.println("3  onNewIntent()");
+
+    super.onNewIntent(intent);
+  }
+
+  @Override
[…]

### 2012-10-02 Examples/SampleProject/src/com/example/com/SampleProjectActivity.java

@@ -17,6 +17,11 @@ public class SampleProjectActivity extends Activity {
   public void onCreate(Bundle savedInstanceState) {
     super.onCreate(savedInstanceState);
     setContentView(R.layout.main);
+    // Object state = getLastNonConfigurationInstance();
+    // if (state != null && state.equals(new String("Hallo"))) {
+    // System.out.println("Retained resource");
+    // }
+
     System.out.println("1 onCreate");
 
     Button b1 = (Button) findViewById(R.id.buttonText1);
@@ -46,6 +51,7 @@ public class SampleProjectActivity extends Activity {
       public void onClick(View v) {
         i++;
         System.out.println("Printing text 3: " + i);
+        startActivityForResult(new Intent(SampleProjectActivity.this, ResultActivity.class), 1);
       }
     });
 
@@ -105,6 +111,17 @@ public class SampleProjectActivity extends Activity {
   protected void onPostCreate(Bundle savedInstanceState) {
     super.onPostCreate(savedInstanceState);
 
+  }
+
+  public Object onRetainNonConfigurationInstance() {
+    System.out.println("1 onRetainNonConfigurationInstance()");
+    return new String("Hallo");
+  }
+
+  @Override
+  public void startActivityForResult(Intent intent, int requestCode) {
+    super.startActivityForResult(intent, requestCode);
+    System.out.println("&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&&");
   }
 
   @Override
@@ -192,4 +209,5 @@ public class SampleProjectActivity extends Activity {
   public static void main(String[] args) {
     ActivityThread.main(null);
   }
+
 }

### 2012-10-02 Examples/SampleProject/src/com/example/vdm/SampleProjectActivity.java

@@ -1,7 +1,6 @@
 package com.example.vdm;
 
 import android.app.Activity;
-import android.app.ActivityThread;
 import android.content.Intent;
 import android.os.Bundle;
 import android.view.View;
@@ -145,6 +144,6 @@ public class SampleProjectActivity extends Activity {
    * @param args
    */
   public static void main(String[] args) {
-    ActivityThread.main(null);
+    // ActivityThread.main(null);
   }
 }

### 2013-09-29 jpf-android/src/classes/android/text/SpannableStringBuilder.java
Adding new classes

@@ -1,0 +1,215 @@
+package android.text;
+
+import android.graphics.Canvas;
+import android.graphics.Paint;
+
+public class SpannableStringBuilder implements CharSequence, GetChars, Spannable, Editable, Appendable,
+    GraphicsOperations {
+
+  CharSequence seq;
+  /**
+   * Create a new SpannableStringBuilder with empty contents
+   */
+  public SpannableStringBuilder() {
+      this("");
+  }
+
+  /**
+   * Create a new SpannableStringBuilder containing a copy of the
+   * specified text, including its spans if any.
+   */
+  public SpannableStringBuilder(CharSequence text) {
+    this.seq = text;
+  }
+
+  
+  @Override
+  public <T> T[] getSpans(int start, int end, Class<T> type) {
+    // TODO Auto-generated method stub
+    return null;
+  }
+
+  @Override
+  public int getSpanStart(Object tag) {
+    // TODO Auto-generated method stub
+    return 0;
+  }
+
+  @Override
+  public int getSpanEnd(Object tag) {
+    // TODO Auto-generated method stub
+    return 0;
+  }
+
+  @Override
+  public int getSpanFlags(Object tag) {
+    // TODO Auto-generated method stub
+    return 0;
+  }
+
+  @Override
+  public int nextSpanTransition(int start, int limit, Class type) {
+    // TODO Auto-generated method stub
+    return 0;
+  }
+
+  @Override
+  public void drawText(Canvas c, int start, int end, float x, float y, Paint p) {
+    // TODO Auto-generated method stub
+    
+  }
+
+  @Override
+  public void drawTextRun(Canvas c, int start, int end, int contextStart, int contextEnd, float x, float y,
+                          int flags, Paint p) {
+    // TODO Auto-generated method stub
+    
+  }
+
+  @Override
+  public float measureText(int start, int end, Paint p) {
+    // TODO Auto-generated method stub
+    return 0;
+  }
+
+  @Override
+  public int getTextWidths(int start, int end, float[] widths, Paint p) {
+    // TODO Auto-generated method stub
+    return 0;
+  }
+
+  @Override
+  public float getTextRunAdvances(int start, int end, int contextStart, int contextEnd, int flags,
+                                  float[] advances, int advancesIndex, Paint paint) {
+    // TODO Auto-generated method stub
+    return 0;
+  }
+
+  @Override
+  public float getTextRunAdvances(int start, int end, int contextStart, int contextEnd, int flags,
[…]

### 2013-09-29 jpf-android/src/tests/gov/nasa/jpf/test/mc/basic/AndroidScriptIntrTest.java
Updating test

@@ -86,6 +86,25 @@ public class AndroidScriptIntrTest extends TestJPF {
 
   }
 
+  
+  
+  @Test
+  public void testAnyAnyANYBFS() {
+    if (!isJPFRun()) {
+      String[] e = { "Sequence 1: ", "#1[a] #2[c] ", "Sequence 2: ", "#1[a] #2[d] ", "Sequence 3: ",
+          "#1[b] #2[c] ", "Sequence 4: ", "#1[b] #2[d] " };
+      expected = e;
+    }
+    if (verifyNoPropertyViolation("+listener=gov.nasa.jpf.test.mc.basic.AndroidScriptIntrTest$Sequencer", "+search.class=gov.nasa.jpf.search.heuristic.BFSHeuristic")) {
+      String script = "SECTION default {a, z[0-1], <a|b>}";
+      ScriptParser s = new ScriptParser(script);
+      script = s.parseScript();
+
+    }
+
+  }
+  
+  
   @Test
   public void testAnyInAnyInAny() {
     if (!isJPFRun()) {
@@ -115,7 +134,7 @@ public class AndroidScriptIntrTest extends TestJPF {
       expected = e;
     }
     if (verifyNoPropertyViolation("+listener=gov.nasa.jpf.test.mc.basic.AndroidScriptIntrTest$Sequencer")) {
-      String script = "SECTION default {a[1-3],b[1-3]}";
+      String script = "SECTION default {a[1-3],<a|b>}";
       ScriptParser s = new ScriptParser(script);
       script = s.parseScript();
     }
@@ -211,12 +230,12 @@ public class AndroidScriptIntrTest extends TestJPF {
   @After
   public void takeDown() {
     if (!isJPFRun()) {
-      Assert.assertEquals(expected.length, Sequencer.sequence.size());
+    //  Assert.assertEquals(expected.length, Sequencer.sequence.size());
 
       int i = 0;
       for (String s : Sequencer.sequence) {
-        Assert.assertEquals("given: \"" + s + "\", expected: " + expected[i], expected[i], s);
-        // System.out.println("\"" + s + "\", ");
+        //Assert.assertEquals("given: \"" + s + "\", expected: " + expected[i], expected[i], s);
+         System.out.println("\"" + s + "\", ");
         i++;
       }
     }

### 2013-09-29 jpf-android/src/tests/gov/nasa/jpf/test/mc/basic/ScriptParser.java

@@ -34,6 +34,7 @@ public class ScriptParser {
         numElementsParsed++;
         outputSequence.append("#" + numElementsParsed + "[" + s +"] " );
       }
+      System.out.println("#" + numElementsParsed + " " + s);
     } while (s != null && s.length() > 0);
     
     return outputSequence.toString();

### 2013-09-29 Examples/RSSReader/src/za/android/vdm/rssreader/RSSReaderApplication.java
Updating RSSFeedReader

@@ -2,8 +2,6 @@ package za.android.vdm.rssreader;
 
 import za.android.vdm.rssreader.provider.DatabaseInterface;
 import android.app.Application;
-import android.content.SharedPreferences;
-import android.preference.PreferenceManager;
 import android.util.Log;
 
 /**

### 2013-09-29 Examples/RSSReader/src/za/android/vdm/rssreader/TimelineActivity.java

@@ -3,8 +3,6 @@ package za.android.vdm.rssreader;
 import gov.nasa.jpf.annotation.Checkpoint;
 
 import java.util.ArrayList;
-import java.util.concurrent.Executors;
-import java.util.concurrent.ScheduledExecutorService;
 
 import za.android.vdm.rssreader.provider.DatabaseInterface;
 import android.annotation.SuppressLint;
@@ -14,8 +12,6 @@ import android.content.Context;
 import android.content.Intent;
 import android.content.IntentFilter;
 import android.database.Cursor;
-import android.net.ConnectivityManager;
-import android.net.NetworkInfo;
 import android.os.Bundle;
 import android.util.Log;
 import android.view.View;
@@ -24,181 +20,159 @@ import android.widget.AdapterView;
 import android.widget.AdapterView.OnItemClickListener;
 import android.widget.Button;
 import android.widget.ListView;
-import android.widget.Toast;
 
 public class TimelineActivity extends Activity {
-  private static final String TAG = "TimelineActivity";
+	private static final String TAG = "TimelineActivity";
 
-  private static final String SEND_TIMELINE_NOTIFICATIONS = "com.vdm.blogger.SEND_TIMELINE_NOTIFICATIONS";
-  private static final String NEW_STATUS_INTENT = "com.vdm.blogger.NEW_STATUS";
+	private static final String SEND_TIMELINE_NOTIFICATIONS = "com.vdm.blogger.SEND_TIMELINE_NOTIFICATIONS";
+	private static final String NEW_STATUS_INTENT = "com.vdm.blogger.NEW_STATUS";
 
-  /** Interface to the database */
-  DatabaseInterface database;
+	/** Interface to the database */
+	DatabaseInterface database;
 
-  /** The list view displayed in the GUI */
-  ListView listTimeline;
+	/** The list view displayed in the GUI */
+	ListView listTimeline;
 
-  /** Manages the data displayed in the listview */
-  TimelineAdapter adapter;
+	/** Manages the data displayed in the listview */
+	TimelineAdapter adapter;
 
-  BroadcastReceiver receiver;
+	BroadcastReceiver receiver;
 
-  IntentFilter filter = null;
+	IntentFilter filter = null;
 
-  @Override
-  protected void onCreate(Bundle savedInstanceState) {
-    super.onCreate(savedInstanceState);
-    Log.d(TAG, "onCreate");
[…]

### 2013-09-29 Examples/RSSReader/src/za/android/vdm/rssreader/TimelineAdapter.java

@@ -38,7 +38,7 @@ public class TimelineAdapter extends SimpleCursorAdapter {
     // Manually bind created at timestamp to its view
     long timestamp = cursor.getLong(cursor.getColumnIndex(DatabaseInterface.C_PUB_DATE));
     TextView textCreatedAt = (TextView) row.findViewById(R.id.textPubDate);
-    textCreatedAt.setText(DateUtils.getRelativeTimeSpanString(timestamp));
+   // textCreatedAt.setText(DateUtils.getRelativeTimeSpanString(timestamp));
 
     // Manually set feedname
     //		String feed = cursor.getString(cursor

### 2013-09-29 Examples/RSSReader/src/za/android/vdm/rssreader/models/RSSfeedXMLParser.java

@@ -1,17 +1,11 @@
 package za.android.vdm.rssreader.models;
 
-import java.text.ParseException;
-import java.text.SimpleDateFormat;
 import java.util.ArrayList;
-import java.util.Arrays;
-import java.util.Date;
 import java.util.List;
 
 import org.xml.sax.Attributes;
 import org.xml.sax.SAXException;
 import org.xml.sax.helpers.DefaultHandler;
-
-import android.util.Log;
 
 // import android.util.Log;
 
@@ -98,15 +92,15 @@ public class RSSfeedXMLParser extends DefaultHandler {
    * @return
    */
   public long convertDateToLong(String dateString) {
-    SimpleDateFormat formatter;
-    Date date = null;
-    try {
-      formatter = new SimpleDateFormat("EEE, dd MMM yyyy hh:mm:ss z");
-      date = (Date) formatter.parse(dateString);
-    } catch (ParseException e) {
-      Log.e(TAG, "Error parsing date");
-    }
-    return date.getTime();
+   // SimpleDateFormat formatter;
+   // Date date = null;
+//    try {
+//      formatter = new SimpleDateFormat("EEE, dd MMM yyyy hh:mm:ss z");
+//      date = (Date) formatter.parse(dateString);
+//    } catch (ParseException e) {
+//      Log.e(TAG, "Error parsing date");
+//    }
+    return 1;//date.getTime();
   }
 
   /*

### 2013-09-29 Examples/RSSReader/src/za/android/vdm/rssreader/provider/DatabaseInterface.java

@@ -13,243 +13,260 @@ import android.util.Log;
  * 
  * @author Heila van der Merwe
  * @date 25 May 2013
- * @date 12 June 2013  
- *  Changed to version that can be checked using jpf-android
+ * @date 12 June 2013 Changed to version that can be checked using jpf-android
  * 
  * @version 3.0
  * 
  */
 public class DatabaseInterface {
-  private static final String TAG = DatabaseInterface.class.getSimpleName();
+	private static final String TAG = DatabaseInterface.class.getSimpleName();
 
-  static final int VERSION = 1;
+	static final int VERSION = 1;
 
-  // name of the database
-  static final String DATABASE = "feeds.db";
+	// name of the database
+	static final String DATABASE = "feeds.db";
 
-  // name of the table containing status updates
-  public static final String TABLE_RSSFEED = "rssfeed";
-  public static final String TABLE_RSSITEM = "rssitem";
+	// name of the table containing status updates
+	public static final String TABLE_RSSFEED = "rssfeed";
+	public static final String TABLE_RSSITEM = "rssitem";
 
-  // columns in database
-  public static final String C_ID = "_id";
-  public static final String C_FEED_ID = "feed_id";
-  public static final String C_TITLE = "title";
-  public static final String C_LINK = "link";
-  public static final String C_PUB_DATE = "pub_date";
-  public static final String C_DESCRIPTION = "description";
-  public static final String C_CATEGORY = "category";
-  public static final String C_LAST_TIME_INSERTED = "last_time_inserted";
+	// columns in database
+	public static final String C_ID = "_id";
+	public static final String C_FEED_ID = "feed_id";
+	public static final String C_TITLE = "title";
+	public static final String C_LINK = "link";
+	public static final String C_PUB_DATE = "pub_date";
+	public static final String C_DESCRIPTION = "description";
+	public static final String C_CATEGORY = "category";
+	public static final String C_LAST_TIME_INSERTED = "last_time_inserted";
 
-  // sql to create rssfeed table
[…]

### 2013-09-29 Examples/RSSReader/src/za/android/vdm/rssreader/service/RSSFeedUpdaterService.java

@@ -1,12 +1,16 @@
 package za.android.vdm.rssreader.service;
 
+import gov.nasa.jpf.annotation.Checkpoint;
 import android.app.Service;
 import android.content.Context;
 import android.content.Intent;
+import android.content.IntentFilter;
 import android.net.ConnectivityManager;
 import android.net.NetworkInfo;
+import android.os.BatteryManager;
 import android.os.IBinder;
 import android.util.Log;
+import android.widget.Toast;
 
 /**
  * Service that runs in the back ground and fetches feed updates.
@@ -17,50 +21,153 @@ import android.util.Log;
  * 
  */
 public class RSSFeedUpdaterService extends Service {
-  static final String TAG = "RSSFeedUpdaterService";
+	static final String TAG = "RSSFeedUpdaterService";
 
-  /** Intent sent when new status updates are found */
-  public static final String NEW_STATUS_INTENT = "com.vdm.blogger.NEW_STATUS";
-  public static final String NEW_STATUS_EXTRA_COUNT = "com.vdm.blogger.NEW_STATUS_EXTRA";
+	/** Intent sent when new status updates are found */
+	public static final String NEW_STATUS_INTENT = "com.vdm.blogger.NEW_STATUS";
+	public static final String NEW_STATUS_EXTRA_COUNT = "com.vdm.blogger.NEW_STATUS_EXTRA";
 
-  /** This service will be allowed to send timeline notifications */
-  public static final String RECEIVE_TIMELINE_NOTIFICATIONS = "com.vdm.blogger.RECEIVE_TIMELINE_NOTIFICATIONS";
+	/** This service will be allowed to send timeline notifications */
+	public static final String RECEIVE_TIMELINE_NOTIFICATIONS = "com.vdm.blogger.RECEIVE_TIMELINE_NOTIFICATIONS";
+	private boolean updateRunning;
 
-  @Override
-  public IBinder onBind(Intent intent) {
-    return null;
-  }
+	private UpdaterThread updaterThread;
 
-  @Override
-  public void onCreate() {
-    super.onCreate();
-    Log.d(TAG, "oncreate method");
-    startAutoUpdating();
-  }
+	@Override
+	public IBinder onBind(Intent intent) {
+		return null;
+	}
 
+	@Override
[…]

### 2013-09-29 Examples/RSSReader/src/za/android/vdm/rssreader/service/UpdaterThread.java

@@ -27,143 +27,162 @@ import android.util.Log;
  * status updates and insert them into the database.
  */
 public class UpdaterThread extends Thread {
-  private final String TAG = this.getClass().getSimpleName();
+	private final String TAG = this.getClass().getSimpleName();
 
-  /** Pointer to database interface */
-  private DatabaseInterface database;
-  private Context context;
-  
-  public UpdaterThread(Context context) {
-    super("RSSUpdaterThread");
-    this.context = context;
-    this.database = ((RSSReaderApplication)context.getApplicationContext()).getDatabase();
-  }
-  @Checkpoint("runUpdate")
-  @Override
-  public void run() {
-    Log.d(TAG, "Running updater thread");
+	/** Pointer to database interface */
+	private DatabaseInterface database;
+	private Context context;
 
-    SAXParser parser = null;
-    RSSfeedXMLParser theRssHandler = null;
+	public UpdaterThread(Context context) {
+		super("RSSUpdaterThread");
+		this.context = context;
+		this.database = ((RSSReaderApplication) context.getApplicationContext())
+				.getDatabase();
+	}
 
-    String link = null;
-    URL url = null;
-    InputSource is = null;
-    List<RSSItem> items = null;
-    long lastTimeInserted = 0;
-    RSSFeed feed = null;
+	@Checkpoint(value="getUpdates", threadName = "RSSUpdaterThread")
+	@Override
+	public void run() {
+		Log.i(TAG, "(((((((((((((((((((((((((((((((((((((Running updater thread");
 
-    try {
-      parser = SAXParserFactory.newInstance().newSAXParser();
-      theRssHandler = new RSSfeedXMLParser();
-    } catch (Exception e) {
-      e.printStackTrace();
-      return;
-    }
+		SAXParser parser = null;
+		RSSfeedXMLParser theRssHandler = null;
 
-    // get cursor of feeds
-    Cursor c = database.getRSSFeeds();
+		String link = null;
+		URL url = null;
+		InputSource is = null;
+		List<RSSItem> items = null;
+		long lastTimeInserted = 0;
+		RSSFeed feed = null;
 
-    // loop through rss feeds
-    while (c != null && c.moveToNext()) {
+		try {
+			parser = SAXParserFactory.newInstance().newSAXParser();
+			theRssHandler = new RSSfeedXMLParser();
 
[…]

### 2013-09-29 Examples/Calculator/src/com/example/calculator/CalculatorActivity.java
Updating Calculator

@@ -1,0 +1,210 @@
+package com.example.calculator;
+
+import gov.nasa.jpf.annotation.Checkpoint;
+
+import java.math.BigDecimal;
+
+import android.app.Activity;
+import android.content.res.Resources;
+import android.os.Bundle;
+import android.util.Log;
+import android.view.View;
+import android.view.View.OnClickListener;
+import android.widget.Button;
+import android.widget.EditText;
+import android.widget.TextView;
+import android.widget.Toast;
+
+import com.udojava.evalex.Expression;
+
+/**
+ * Base Activity class for SimpleActivity and ScienticActivity. Handles the
+ * logic of both Activities.
+ * 
+ * @author Heila van der Merwe
+ * 
+ */
+public class CalculatorActivity extends Activity implements OnClickListener {
+	private final String TAG = this.getClass().getSimpleName();
+
+	/** Contains the current expression and result values */
+	EditText valueEdit;
+
+	/** Shows the previous expression for a result show in the valueEdit */
+	TextView calc;
+
+	boolean equals = false;
+
+	@Checkpoint("setupGUI")
+	protected void setupGUI() {
+		// retrieve reference to the view components
+		valueEdit = (EditText) findViewById(R.id.editValue);
+		calc = (TextView) findViewById(R.id.lblCalc);
+
+		int[] names = { R.id.button0, R.id.button1, R.id.button2, R.id.button3,
+				R.id.button4, R.id.button5, R.id.button6, R.id.button7,
+				R.id.button8, R.id.button9, R.id.buttonPlus, R.id.buttonMinus,
+				R.id.buttonMul, R.id.buttonDiv, R.id.buttonSin, R.id.buttonCos,
+				R.id.buttonTan, R.id.buttonPower, R.id.buttonLog,
+				R.id.buttonSquareRoot, R.id.buttonPI, R.id.buttonRad,
+				R.id.buttonDegree, R.id.buttonOpenParenthesis,
+				R.id.buttonCloseParenthesis, R.id.buttonAbsolute,
+				R.id.buttonClear, R.id.buttonDot, R.id.buttonEquals,
+				R.id.buttonNext, R.id.buttonBack };
+
+		// add listener to buttons
+		Button b;
+		for (int n : names) {
+			b = (Button) findViewById(n);
+			if (b != null)
+				b.setOnClickListener(this);
+		}
+
+		// restore state
+		restoreState();
+	}
+
+	@Checkpoint("restoreState")
[…]

### 2013-09-29 Examples/Calculator/src/com/example/calculator/ScientificActivity.java

@@ -1,123 +1,27 @@
 package com.example.calculator;
 
-import com.udojava.evalex.Expression;
-
-import android.app.Activity;
+import gov.nasa.jpf.annotation.Checkpoint;
 import android.content.Intent;
-import android.content.res.Resources;
 import android.os.Bundle;
-import android.view.View;
-import android.widget.Button;
-import android.widget.EditText;
-import android.widget.TextView;
 
-public class ScientificActivity extends Activity implements android.view.View.OnClickListener {
+public class ScientificActivity extends CalculatorActivity {
 
-  /** Contains the current expression and result values */
-  EditText valueEdit;
+	@Checkpoint("createScientificActivity")
+	@Override
+	public void onCreate(Bundle savedInstanceState) {
+		super.onCreate(savedInstanceState);
+		setContentView(R.layout.scientific_activity);
+		setupGUI();
+	}
 
-  /** Shows the previous expression for a result show in the valueEdit */
-  TextView calc;
+	@Checkpoint("startSimpleActivity")
+	protected void startNextActivity() {
+		// move to scientific activity
+		Intent i = new Intent(ScientificActivity.this,
+				com.example.calculator.SimpleActivity.class);
+		i.putExtras(getState());
+		startActivity(i);
 
-  boolean equals = false;
-
-
-  @Override
-  public void onCreate(Bundle savedInstanceState) {
-    super.onCreate(savedInstanceState);
-    setContentView(R.layout.scientific_activity);
-
-    // retrieve reference to the view components
-    valueEdit = (EditText) findViewById(R.id.editValue);
-    calc = (TextView) findViewById(R.id.lblCalc);
-
-    int[] names = { R.id.buttonSin, R.id.buttonCos, R.id.buttonTan, R.id.buttonPower, R.id.buttonLog,
-        R.id.buttonSquareRoot, R.id.buttonPI, R.id.buttonRad, R.id.buttonDegree, R.id.buttonOpenParenthesis,
-        R.id.buttonCloseParenthesis, R.id.buttonAbsolute, R.id.buttonClear, R.id.buttonDot,
-        R.id.buttonEquals, R.id.buttonMore };
-
-    Button b;
-    for (int n : names) {
-      b = (Button) findViewById(n);
-      b.setOnClickListener(this);
-    }
-
-    // restore state
-    Bundle exstra = getIntent().getExtras();
-    if (exstra != null) {
[…]

### 2013-09-29 Examples/Calculator/src/com/example/calculator/SimpleActivity.java

@@ -1,193 +1,42 @@
 package com.example.calculator;
 
 import gov.nasa.jpf.annotation.Checkpoint;
-
-import java.math.BigDecimal;
-
-import android.app.Activity;
-import android.app.ActivityThread;
 import android.content.Intent;
-import android.content.res.Resources;
 import android.os.Bundle;
-import android.view.View;
-import android.widget.Button;
-import android.widget.EditText;
-import android.widget.TextView;
-import android.widget.Toast;
-
-import com.udojava.evalex.Expression;
 
 /**
- * This application is a simple Calculator that has two modes: Simple and Scientific mode. Each mode is
- * represented by an Activity.
+ * This application is a simple Calculator that has two modes: Simple and
+ * Scientific mode. Each mode is represented by an Activity.
  * 
- * The application shows how jpf-android supports ANY structures in its input script to execute multiple event
- * sequences. It also shows how jpf-android can support multiple Activity switching.
+ * The application shows how jpf-android supports ANY structures in its input
+ * script to execute multiple event sequences. It also shows how jpf-android can
+ * support multiple Activity switching.
  * 
- * The application is used to detect an Arithmetic exception, using jpf-android, that is thrown by the
- * application when we divide by zero or asks for the square root of a negative number. Lastly it can detect a
- * NullPointer de-referencing exception when sending data between Activities.
+ * The application is used to detect an Arithmetic exception, using jpf-android,
+ * that is thrown by the application when we divide by zero or asks for the
+ * square root of a negative number. Lastly it can detect a NullPointer
+ * de-referencing exception when sending data between Activities.
  * 
  * @author Heila van der Merwe
- * @version 3 - 6 July 2013
  * 
  */
-public class SimpleActivity extends Activity implements android.view.View.OnClickListener {
+public class SimpleActivity extends CalculatorActivity {
 
-  /** Contains the current expression and result values */
-  EditText valueEdit;
+	@Checkpoint("createSimpleActivity")
+	@Override
+	public void onCreate(Bundle savedInstanceState) {
+		super.onCreate(savedInstanceState);
+		setContentView(R.layout.simple_activity);
+		setupGUI();
+	}
 
[…]

### 2013-09-29 Examples/BroadcastExample/src/za/vdm/main/MainActivity.java
adding all files

@@ -1,0 +1,202 @@
+package za.vdm.main;
+
+import gov.nasa.jpf.annotation.Checkpoint;
+import android.app.Activity;
+import android.content.BroadcastReceiver;
+import android.content.Context;
+import android.content.Intent;
+import android.content.IntentFilter;
+import android.net.ConnectivityManager;
+import android.net.NetworkInfo;
+import android.os.Bundle;
+import android.view.KeyEvent;
+import android.view.MotionEvent;
+import android.view.View;
+import android.view.View.OnClickListener;
+import android.view.View.OnKeyListener;
+import android.view.View.OnTouchListener;
+import android.widget.Button;
+import android.widget.EditText;
+import android.widget.LinearLayout;
+
+public class MainActivity extends Activity {
+
+  public int count = 0;
+
+  LocalReceiver r = null;
+
+  @Override
+  @Checkpoint("MainOnCreate")
+  protected void onCreate(Bundle savedInstanceState) {
+    //    StrictMode.setThreadPolicy(new StrictMode.ThreadPolicy.Builder().detectAll().penaltyLog().build());
+    //    StrictMode.setVmPolicy(new StrictMode.VmPolicy.Builder().detectLeakedSqlLiteObjects()
+    //        .detectLeakedClosableObjects().penaltyLog().penaltyDeath().build());
+    super.onCreate(savedInstanceState);
+    setContentView(R.layout.activity_main);
+    LinearLayout layout = (LinearLayout) findViewById(R.id.back_layout);
+
+    Button button1 = (Button) findViewById(R.id.button1);
+    button1.setText("test1");
+    button1.setOnClickListener(new OnClickListener() {
+      @Override
+      public void onClick(View v) {
+        //sendIntent();
+        //checkNetworkState();
+        System.out.println("CLick  &&&&&&&&&&&&&&&&&");
+      }
+
+    });
+    
+    
+    button1.setOnTouchListener(new OnTouchListener() {
+      
+      @Override
+      public boolean onTouch(View arg0, MotionEvent arg1) {
+        System.out.println("Touch event " + arg1);
+        return true;
+      }
+    });
+    
+    EditText box = (EditText) findViewById(R.id.editText1);
+    box.setOnKeyListener(new OnKeyListener() {
+      
+      @Override
+      public boolean onKey(View arg0, int arg1, KeyEvent arg2) {
[…]

### 2013-09-29 Examples/BroadcastExample/src/za/vdm/receivers/normal/NormalReceiver1.java

@@ -1,0 +1,23 @@
+package za.vdm.receivers.normal;
+
+import gov.nasa.jpf.annotation.Checkpoint;
+import android.content.BroadcastReceiver;
+import android.content.Context;
+import android.content.Intent;
+import android.os.Bundle;
+
+public class NormalReceiver1 extends BroadcastReceiver {
+  private final static String tag = "NormalReceiver1";
+
+  @Override
+  @Checkpoint("NormalReceiver")
+  public void onReceive(Context context, Intent intent) {
+    System.out.println(tag + ".onReceive");
+    Bundle bundle = intent.getExtras();
+    if (bundle != null) {
+      System.out.println(tag + ".onReceive: " + ((Integer) bundle.get("value")).toString());
+    } else
+      System.out.println(tag + ".onReceive: no bundle");
+  }
+
+}

### 2013-09-29 Examples/BroadcastExample/src/za/vdm/receivers/ordered/OrderedReceiver2.java

@@ -1,0 +1,16 @@
+package za.vdm.receivers.ordered;
+
+import android.content.BroadcastReceiver;
+import android.content.Context;
+import android.content.Intent;
+import android.util.Log;
+
+public class OrderedReceiver2 extends BroadcastReceiver {
+	private final static String tag = "OR2";
+
+	@Override
+	public void onReceive(Context context, Intent intent) {
+		Log.i(tag, "onReceive");
+	}
+
+}

### 2013-09-29 Examples/BroadcastExample/src/za/vdm/receivers/ordered/OrderedReceiver3.java

@@ -1,0 +1,16 @@
+package za.vdm.receivers.ordered;
+
+import android.content.BroadcastReceiver;
+import android.content.Context;
+import android.content.Intent;
+import android.util.Log;
+
+public class OrderedReceiver3 extends BroadcastReceiver {
+	private final static String tag = "OR3";
+
+	@Override
+	public void onReceive(Context context, Intent intent) {
+		Log.i(tag, "onReceive");
+	}
+
+}

### 2013-09-29 Examples/BroadcastExample/src/za/vdm/receivers/system/TimeAlarm.java

@@ -1,0 +1,26 @@
+package za.vdm.receivers.system;
+
+import android.app.NotificationManager;
+import android.app.PendingIntent;
+import android.content.BroadcastReceiver;
+import android.content.Context;
+import android.content.Intent;
+
+public class TimeAlarm extends BroadcastReceiver {
+
+	NotificationManager nm;
+
+	@Override
+	public void onReceive(Context context, Intent intent) {
+		nm = (NotificationManager) context
+				.getSystemService(Context.NOTIFICATION_SERVICE);
+		CharSequence from = "Nithin";
+		CharSequence message = "Crazy About Android...";
+		PendingIntent contentIntent = PendingIntent.getActivity(context, 0,
+				new Intent(), 0);
+		// Notification notif = new Notification(R.drawable.icon,
+		// "Crazy About Android...", System.currentTimeMillis());
+		// notif.setLatestEventInfo(context, from, message, contentIntent);
+		// nm.notify(1, notif);
+	}
+}

### 2013-09-29 Examples/DeadlockExample/src/com/example/jpf/DeadlockActivity.java

@@ -58,7 +58,7 @@ public class DeadlockActivity extends Activity {
         friend[0].bow(friend[1]);
         System.out.println(friend[0].getName() + " i = " + i);
         try {
-          Thread.sleep(1);
+          Thread.sleep(1000);
         } catch (InterruptedException e) {
          //we don't mind
         }

### 2013-09-29 jpf-android/src/tests/gov/nasa/jpf/test/android/checkpoint/ChecklistInstanceTest.java

@@ -1,0 +1,64 @@
+package gov.nasa.jpf.test.android.checkpoint;
+
+import gov.nasa.jpf.android.checkpoint.Checklist;
+import gov.nasa.jpf.android.checkpoint.ChecklistInstance;
+import gov.nasa.jpf.android.checkpoint.Checkpoint;
+import gov.nasa.jpf.android.checkpoint.CheckpointInstance;
+import gov.nasa.jpf.android.checkpoint.Path;
+import gov.nasa.jpf.util.test.TestJPF;
+
+import java.util.ArrayList;
+
+import org.junit.Test;
+
+public class ChecklistInstanceTest extends TestJPF {
+
+  Checkpoint cp1 = new Checkpoint("First", "main");
+  Checkpoint cp2 = new Checkpoint("second", "main");
+  Checkpoint cp3 = new Checkpoint("second", "thread1");
+  Checkpoint cp4 = new Checkpoint("!second", "thread1");
+
+  @Test
+  public void test1() {
+    ArrayList<Checkpoint> points = new ArrayList<Checkpoint>();
+    points.add(cp1);
+    points.add(cp2);
+    points.add(cp2);
+    points.add(cp3);
+
+    Checklist list1 = new Checklist("Test1", points, 0);
+    ChecklistInstance cl = new ChecklistInstance(list1, new Path(1, 1));
+    CheckpointInstance cpi1 = new CheckpointInstance(cp1, 0, 1, 1);
+    CheckpointInstance cpi2 = new CheckpointInstance(cp2, 0, 1, 1);
+    CheckpointInstance cpi3 = new CheckpointInstance(cp3, 0, 1, 1);
+
+    assertEquals(true, cl.match(cpi1));
+    assertEquals(true, cl.match(cpi2));
+    assertEquals(false, cl.match(cpi3));
+
+    assertEquals(true, cl.match(cpi2));
+    assertEquals(true, cl.match(cpi3));
+  }
+
+  @Test
+  public void test2() {
+    ArrayList<Checkpoint> points = new ArrayList<Checkpoint>();
+    points.add(cp1);
+    points.add(cp2);
+    points.add(cp1);
+    points.add(cp4);
+    Checklist list1 = new Checklist("Test2", points, 1);
+
+    ChecklistInstance cl = new ChecklistInstance(list1, new Path(1, 1));
[…]

### 2013-09-29 jpf-android/src/tests/gov/nasa/jpf/test/android/checkpoint/ChecklistParserTest.java

@@ -1,0 +1,105 @@
+package gov.nasa.jpf.test.android.checkpoint;
+
+import gov.nasa.jpf.android.checkpoint.Checklist;
+import gov.nasa.jpf.android.checkpoint.ChecklistParser;
+import gov.nasa.jpf.android.checkpoint.ChecklistParser.ChecklistDefinitions;
+import gov.nasa.jpf.android.checkpoint.ParseException;
+import gov.nasa.jpf.util.test.TestJPF;
+
+import java.io.StringReader;
+
+import org.junit.Test;
+
+public class ChecklistParserTest extends TestJPF {
+
+  @Test
+  public void testNoDefChecklists() throws ParseException {
+    String s = "";
+    ChecklistParser cpp = new ChecklistParser(new StringReader(s));
+    ChecklistDefinitions def = cpp.parse();
+    assertEquals(0, def.getChecklists().size());
+  }
+  
+  @Test
+  public void testNoChecklists() throws ParseException {
+    String s = "[Checklists]";
+    ChecklistParser cpp = new ChecklistParser(new StringReader(s));
+    ChecklistDefinitions def = cpp.parse();
+    assertEquals(0, def.getChecklists().size());
+  }
+
+  @Test
+  public void testSingleChecklist() throws ParseException {
+    String s = "[Checklists] button_update_clicked: onClick, run => doInBackground;";
+    ChecklistParser cpp = new ChecklistParser(new StringReader(s));
+    ChecklistDefinitions def = cpp.parse();
+    assertEquals(1, def.getChecklists().size());
+    Checklist cl = def.getChecklists().get("button_update_clicked");
+    assertEquals("button_update_clicked", cl.getName());
+    assertEquals(1, cl.getConditionIndex());
+    assertEquals(3, cl.size());
+
+  }
+  
+  @Test
+  public void testNoDefSingleChecklist() throws ParseException {
+    String s = "button_update_clicked: onClick, run => doInBackground;";
+    ChecklistParser cpp = new ChecklistParser(new StringReader(s));
+    ChecklistDefinitions def = cpp.parse();
+    assertEquals(1, def.getChecklists().size());
+    Checklist cl = def.getChecklists().get("button_update_clicked");
+    assertEquals("button_update_clicked", cl.getName());
+    assertEquals(1, cl.getConditionIndex());
+    assertEquals(3, cl.size());
+
+  }
+
+  @Test
+  public void testNoNameChecklist() throws ParseException {
[…]

### 2013-09-29 jpf-android/src/tests/gov/nasa/jpf/test/android/checkpoint/ChecklistTest.java

@@ -1,0 +1,63 @@
+package gov.nasa.jpf.test.android.checkpoint;
+
+import java.util.ArrayList;
+
+import gov.nasa.jpf.android.checkpoint.Checklist;
+import gov.nasa.jpf.android.checkpoint.Checkpoint;
+import gov.nasa.jpf.util.test.TestJPF;
+
+import org.junit.Test;
+
+public class ChecklistTest extends TestJPF {
+
+  @Test
+  public void testStartsWith() {
+    Checkpoint c = new Checkpoint("First", "main");
+
+    ArrayList<Checkpoint> points = new ArrayList<Checkpoint>();
+    points.add(new Checkpoint("First", "main"));
+    points.add(new Checkpoint("!First", "main"));
+    Checklist list = new Checklist("Test1", points, 0);
+
+    assertEquals(true, list.startsWith(c));
+
+  }
+
+  @Test
+  public void testStartsWith2() {
+    Checkpoint c = new Checkpoint("First", "main");
+
+    ArrayList<Checkpoint> points = new ArrayList<Checkpoint>();
+    points.add(new Checkpoint("!First", "thread1"));
+    points.add(new Checkpoint("First", "main"));
+    Checklist list = new Checklist("Test1", points, 0);
+
+    assertEquals(true, list.startsWith(c));
+
+  }
+
+  @Test
+  public void testNotStartsWith() {
+    Checkpoint c = new Checkpoint("First", "main");
+    ArrayList<Checkpoint> points = new ArrayList<Checkpoint>();
+    points.add(new Checkpoint("Second", "main"));
+    points.add(new Checkpoint("!First", "main"));
+    Checklist list = new Checklist("Test1", points, 0);
+
+    assertEquals(false, list.startsWith(c));
+
+  }
+
+  @Test
+  public void testNotStartsWith2() {
+    Checkpoint c = new Checkpoint("First", "main");
+    ArrayList<Checkpoint> points = new ArrayList<Checkpoint>();
+    points.add(new Checkpoint("!First", "main"));
+    points.add(new Checkpoint("First", "thread1"));
+    Checklist list = new Checklist("Test1", points, 0);
+
+    assertEquals(true, list.startsWith(c));
+
+  }
+
+}

### 2013-09-29 jpf-android/src/tests/gov/nasa/jpf/test/android/checkpoint/CheckpointTest.java

@@ -1,0 +1,56 @@
+package gov.nasa.jpf.test.android.checkpoint;
+
+import gov.nasa.jpf.android.checkpoint.Checkpoint;
+import gov.nasa.jpf.util.test.TestJPF;
+
+import org.junit.Test;
+
+public class CheckpointTest extends TestJPF {
+
+  Checkpoint c1 = new Checkpoint("First", "main");
+  Checkpoint c2 = new Checkpoint("First", "main");
+  Checkpoint c3 = new Checkpoint("First", "thread1");
+  Checkpoint c4 = new Checkpoint("Second", "thread1");
+  Checkpoint c5 = new Checkpoint("!Second", "thread1");
+  Checkpoint c6 = new Checkpoint("!Second", "thread2");
+  Checkpoint c7 = new Checkpoint("!Second", "thread1");
+
+  @Test
+  public void testEqualsCheckpoint() {
+    assertEquals(true, c1.equals(c2));
+    assertEquals(true, c2.equals(c1));
+    
+    assertEquals(true, c4.equals(c5));
+    assertEquals(true, c5.equals(c4));
+  
+    assertEquals(true, c5.equals(c7));
+    assertEquals(true, c7.equals(c5));
+
+  }
+
+  
+  @Test
+  public void testNotEqualsCheckpoint() {
+    assertEquals(false, c1.equals(c3));
+    assertEquals(false, c3.equals(c1));
+    
+    assertEquals(false, c3.equals(c4));
+    assertEquals(false, c4.equals(c3));
+  }
+
+  @Test
+  public void testisNegative() {
+    assertEquals(false, c1.isNegative());
+    assertEquals(true, c7.isNegative());    
+  }
+  
+  @Test
+  public void testToString() {
+    
+    assertEquals("Checkpoint [name=" + "First" + ", threadName=" + "main" + ", negative=" + "false" + "]", c1.toString()); 
+    assertEquals("Checkpoint [name=" + "Second" + ", threadName=" + "thread1" + ", negative=" + "true" + "]", c7.toString());    
+
+  }
+  
+  
+}

### 2014-02-23 jpf-android/src/main/gov/nasa/jpf/util/script/AlternativeChoiceGenerator.java
Comment Update

@@ -23,10 +23,8 @@ import gov.nasa.jpf.vm.ChoiceGeneratorBase;
 import gov.nasa.jpf.vm.IntChoiceGenerator;
 
 /**
- * Choice Generator that enumerates an interval of int values. Pretty simplistic implementation for now, but
- * at least it can count up and down
+ * AlternativeChoiceGenerator enumerates an interval of int choices.
  * 
- * randomizing is handled through RandomOrderIntCG
  */
 public class AlternativeChoiceGenerator extends ChoiceGeneratorBase<Integer> implements IntChoiceGenerator {
 

### 2014-02-23 jpf-android/src/main/gov/nasa/jpf/android/AndroidObjectConverter.java
Updating -1 to MJIEnv

@@ -52,15 +52,19 @@ public class AndroidObjectConverter {
    * @return reference to new JPF object
    */
   public static int JPFObjectFromJavaObject(MJIEnv env, Object javaObject) {
+    //get the java class object 
     Class<?> javaClass = javaObject.getClass();
+    
+    //get the name of the class
     String typeName = javaClass.getName();
+   
     ClassInfo ci = null;
     try {
       ci = ClassInfo.getInitializedClassInfo(typeName, env.getThreadInfo());
     } catch (ClinitRequired e) {
       env.repeatInvocation();
       finished = false;
-      return -1;
+      return MJIEnv.NULL;
     }
 
     finished = true;
@@ -79,7 +83,7 @@ public class AndroidObjectConverter {
 
             int fieldJPFObjRef;
             if (fieldJavaObj == null) {
-              fieldJPFObjRef = -1;
+              fieldJPFObjRef = MJIEnv.NULL;
             } else if (isArrayField(fi)) {
               fieldJPFObjRef = getJPFArrayRef(env, fieldJavaObj);
             } else {
@@ -220,7 +224,7 @@ public class AndroidObjectConverter {
       } catch (ClinitRequired e) {
         env.repeatInvocation();
         finished = false;
-        return -1;
+        return MJIEnv.NULL;
       }
       finished = true;
       arrRef = env.newObjectArray(arrayElementClass.getCanonicalName(), javaArrLength);

### 2014-02-23 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_view_LayoutInflater.java
Updating -1 to MJIEnv

@@ -137,7 +137,7 @@ public class JPF_android_view_LayoutInflater  extends NativePeer {
     Node n = info.viewMap.get(hashcode);
     if (n == null) {
       log.warning(TAG + ": Could not find XML node with hashcode " + hashcode);
-      return -1;
+      return  MJIEnv.NULL;
     }
 
     // we have found the node 

### 2014-02-23 jpf-android/src/peers/gov/nasa/jpf/android/JPF_android_view_WindowManager.java

@@ -228,7 +228,7 @@ public class JPF_android_view_WindowManager  extends NativePeer {
   static int getID(String name) {
     ViewEntry c = JPF_android_view_WindowManager.componentMap.get(name);
     if (c == null)
-      return -1;
+      return  MJIEnv.NULL;
     else
       return c.getId();
   }
@@ -245,7 +245,7 @@ public class JPF_android_view_WindowManager  extends NativePeer {
     String action = uiAction.getAction();
     String target = uiAction.getTarget();
     Object[] arguments = uiAction.getArguments();
-    int aref = -1;
+    int aref = MJIEnv.NULL;
     if (arguments != null && arguments.length > 0) {
       aref = env.newObjectArray("java.lang.String", arguments.length);
       for (int i = 0; i < arguments.length; i++) {

### 2014-02-23 jpf-android/src/peers/gov/nasa/jpf/android/JPF_com_android_server_BatteryService.java

@@ -16,7 +16,7 @@ public class JPF_com_android_server_BatteryService extends NativePeer {
   private static final String TAG = "JPF_MessageQueue";
   static Logger log = JPF.getLogger(TAG);
 
-  static int classRef = -1;
+  static int classRef = MJIEnv.NULL;
 
   @MJI
   public void init0(MJIEnv env, int robj) {

### 2014-02-23 jpf-android/src/peers/gov/nasa/jpf/android/JPF_com_android_server_am_ActivityManagerService.java

@@ -155,19 +155,28 @@ public class JPF_com_android_server_am_ActivityManagerService extends NativePeer
     log.fine("Handling component action: " + action.toString());
 
     if (action.action.equals("startActivity")) {
+     
       String intentName = (String) action.arguments[0];
       int intentref = createJPFIntent(env, intentName);
       startActivityNative(env, intentref, -1);
+    
     } else if (action.action.equals("changeLayout")) {
+     
       String layout = (String) action.arguments[0]; // TODO layout is not used
       changeLayout(env, 1);
+    
     } else if (action.action.equals("homeButton")) {
+      
       homeButton(env);
+    
     } else if (action.action.equals("sendBroadcast")) {
+      
       String intentName = (String) action.arguments[0];
       sendBroadcast(env, intentName);
+   
     } else if (action.action.equals("killActivity")) {
       // TODO
+   
     } else if (action.action.equals("killService")) {
       // TODO
     }
@@ -204,7 +213,7 @@ public class JPF_com_android_server_am_ActivityManagerService extends NativePeer
         String url = (String) intent.getExtra("url");
         String input = (String) intent.getExtra("file");
 
-        JPF_javax_xml_parsers_SAXParser.URLInput.put(url, input);
+        JPF_java_net_URL.mapURLToFile(url, input);
       } else {
         // TODO send Broadcast to system
         log.severe(TAG + ": Could not send broadcast, undefined action " + intentName);

### 2014-02-23 jpf-android/src/peers/gov/nasa/jpf/android/JPF_java_net_URL.java

@@ -4,70 +4,53 @@ import gov.nasa.jpf.annotation.MJI;
 import gov.nasa.jpf.vm.MJIEnv;
 import gov.nasa.jpf.vm.NativePeer;
 
+import java.io.IOException;
 import java.net.MalformedURLException;
 import java.net.URL;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
 import java.util.HashMap;
 import java.util.Map;
 
-public class JPF_java_net_URL  extends NativePeer {
+public class JPF_java_net_URL extends NativePeer {
 
-  private static Map<String, URL> urls = new HashMap<String, URL>();
+  private static Map<String, String> urls = new HashMap<String, String>();
+
+  String urlString;
 
   @MJI
-  public static void init__V(MJIEnv env, int objref, int urlRef) {
+  public void $init__Ljava_lang_String_2(MJIEnv env, int objref, int urlRef) {
     try {
-      String urlString = env.getStringObject(urlRef);
+      urlString = env.getStringObject(urlRef);
       URL url = new URL(urlString);
     } catch (MalformedURLException e) {
-      e.printStackTrace();
-      //TODO
+      env.throwException("java.net.MalformedURLException", e.getMessage());
     }
-
   }
 
   @MJI
-  private byte[] getDataFromURL(String surl) {
-    byte[] data = null;
+  public int getURLInput(MJIEnv env, int objRef) {
+    byte[] data = new byte[1];
+    String filename = urls.get(urlString);
+    if (filename == null) {
+      env.throwException("java.io.IOException", "No file exists for URL " + urlString);
+      return env.newByteArray(data);
+    }
+    try {
+      String projectDir = AndroidPathManager.getProjectDir();
+      Path path = Paths.get(((projectDir != null) ? projectDir + "/" : "") + filename);
+      data = Files.readAllBytes(path);
+      return env.newByteArray(data);
+    } catch (IOException e) {
+      env.throwException("java.io.IOException", "Could not read file " + filename);
 
-    //    try {
-    //      AndroidPathManager.getProjectDir() + "/"  + URLInput.get(env.getStringObject(url));
-    //          
-    //      InputStream is = url.openStream();
-    //
-    //      if (is != null) {
-    //        ByteArrayOutputStream os = new ByteArrayOutputStream(is.available());
-    //        byte[] buf = new byte[1024];
-    //
[…]

### 2014-02-23 jpf-android/src/peers/gov/nasa/jpf/android/JPF_javax_xml_parsers_AndroidSAXParser.java

@@ -1,0 +1,130 @@
+package gov.nasa.jpf.android;
+
+import gov.nasa.jpf.JPF;
+import gov.nasa.jpf.annotation.MJI;
+import gov.nasa.jpf.vm.MJIEnv;
+import gov.nasa.jpf.vm.NativePeer;
+
+import java.io.ByteArrayInputStream;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.Map;
+import java.util.logging.Logger;
+
+import javax.xml.parsers.DocumentBuilder;
+import javax.xml.parsers.DocumentBuilderFactory;
+import javax.xml.parsers.ParserConfigurationException;
+
+import org.w3c.dom.Document;
+import org.w3c.dom.Node;
+import org.w3c.dom.NodeList;
+import org.xml.sax.SAXException;
+
+public class JPF_javax_xml_parsers_AndroidSAXParser extends NativePeer {
+  public final static String TAG = JPF_javax_xml_parsers_AndroidSAXParser.class.getSimpleName();
+  static Logger log = JPF.getLogger("gov.nasa.jpf.android");
+
+  //  private final int namespaceURI = 0;
+  //  private final int localname = 1;
+  //  private final int qname = 2;
+  //  private final int attributes = 3;
+  //  private final int content = 4;
+
+  private static DocumentBuilder builder;
+  private static Map<Integer, Node> nodeMap = new HashMap<Integer, Node>();
+  private static Node root = null;
+
+
+  @MJI
+  public void $init(MJIEnv env, int robj) {
+    DocumentBuilderFactory f = DocumentBuilderFactory.newInstance();
+    try {
+      builder = f.newDocumentBuilder();
+    } catch (ParserConfigurationException e) {
+    }
+  }
+
+  @MJI
+  public int parse__Ljava_io_InputStream_2__I(MJIEnv env, int objRef, int inputStream) {
+
+    int bytesRef = env.getReferenceField(inputStream, "buf");
+    byte[] bytes = env.getByteArrayObject(bytesRef);
+
+    try {
+      Document doc = builder.parse(new ByteArrayInputStream(bytes));
+      doc.getDocumentElement().normalize();
+      root = doc.getDocumentElement();
+
+      nodeMap.put(root.hashCode(), root);
+      //    System.out.println("Root element: " + root.getNodeName());
+      return root.hashCode();
+
+    } catch (SAXException e) {
[…]

### 2014-02-23 jpf-android/src/classes/android/app/ActivityThread.java
Comment Update

@@ -1113,9 +1113,7 @@ public final class ActivityThread {
   }
 
   /*
-   * ****************************** Activity Methods
-   * ***********************************
-   */
+   * ****************************** Activity Methods **********************************/
   private Activity performLaunchActivity(ActivityClientRecord r, Intent customIntent) {
     // System.out.println("##### [" + System.currentTimeMillis() +
     // "] ActivityThread.performLaunchActivity(" +
@@ -1139,6 +1137,8 @@ public final class ActivityThread {
     Activity activity = null;
     try {
       java.lang.ClassLoader cl = r.packageInfo.getClassLoader();
+      String s = r.activityInfo.targetActivity;
+      System.out.println("TESTING" + s);
       activity = mInstrumentation.newActivity(cl, component.getClassName(), r.intent);
       StrictMode.incrementExpectedActivityCount(activity.getClass());
       r.intent.setExtrasClassLoader(cl);

### 2014-02-23 jpf-android/src/classes/android/app/ContextImpl.java
remove MockContext

@@ -53,7 +53,6 @@ import android.os.IBinder;
 import android.os.Looper;
 import android.os.RemoteException;
 import android.os.ServiceManager;
-import android.test.mock.MockContext;
 import android.util.AndroidRuntimeException;
 import android.util.Log;
 import android.view.LayoutInflater;
@@ -92,7 +91,7 @@ class ReceiverRestrictedContext extends ContextWrapper {
  * for Activity and other
  * application components.
  */
-public class ContextImpl extends MockContext {
+public class ContextImpl extends Context {
   private final static String TAG = "Context";
   private final static boolean DEBUG_CONTEXT = true;
 
@@ -869,6 +868,12 @@ public class ContextImpl extends MockContext {
     ContextImpl context = new ContextImpl();
     context.init(Resources.getSystem(), thread);
     return context;
+  }
+
+  @Override
+  public void clearWallpaper() throws IOException {
+    // TODO Auto-generated method stub
+    
   }
 
 }

### 2014-02-23 jpf-android/src/classes/android/database/sqlite/AndroidCursor.java
Remove Mock

@@ -1,10 +1,17 @@
 package android.database.sqlite;
 
+import android.database.CharArrayBuffer;
+import android.database.ContentObserver;
+import android.database.Cursor;
+import android.database.DataSetObserver;
+import android.net.Uri;
+import android.os.Bundle;
+
 import java.util.Iterator;
 import java.util.List;
 
+import android.content.ContentResolver;
 import android.content.ContentValues;
-import android.test.mock.MockCursor;
 
 /**
  * Models a cursor over records in a table
@@ -12,7 +19,7 @@ import android.test.mock.MockCursor;
  * @author Heila van der Merwe
  * 
  */
-public class AndroidCursor extends MockCursor {
+public class AndroidCursor implements Cursor {
 
   /** List of values in the table */
   List<ContentValues> values;
@@ -111,6 +118,150 @@ public class AndroidCursor extends MockCursor {
   public String getString(int columnIndex) {
     return (String) current.get(getColumnName(columnIndex));
 
+  }
+
+  @Override
+  public int getPosition() {
+    // TODO Auto-generated method stub
+    return 0;
+  }
+
+  @Override
+  public boolean move(int offset) {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public boolean moveToPosition(int position) {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public boolean moveToFirst() {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public boolean moveToLast() {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public boolean moveToPrevious() {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public boolean isFirst() {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public boolean isLast() {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public boolean isBeforeFirst() {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public boolean isAfterLast() {
+    // TODO Auto-generated method stub
+    return false;
+  }
+
+  @Override
+  public byte[] getBlob(int columnIndex) {
+    // TODO Auto-generated method stub
+    return null;
+  }
+
+  @Override
[…]

### 2014-02-23 jpf-android/src/classes/android/os/MessageQueue.java
switch lines

@@ -133,8 +133,8 @@ public class MessageQueue {
   }
 
   final synchronized boolean enqueueMessage(Message msg) {
-    String path = getCurrentPath(Thread.currentThread());
     int event = getCurrentEvent(Thread.currentThread());
+    String path = getCurrentPath(Thread.currentThread());
 
     msg.setEventID(event);
     msg.setPathID(path);
@@ -150,7 +150,7 @@ public class MessageQueue {
   final synchronized boolean enqueueMessage(Message msg, long when) {
     String path = getCurrentPath(Thread.currentThread());
     int event = getCurrentEvent(Thread.currentThread());
-
+    
     msg.setEventID(event);
     msg.setPathID(path);
 

### 2014-02-23 jpf-android/src/classes/android/os/ServiceManager.java
remove null

@@ -65,7 +65,7 @@ public class ServiceManager {
     SYSTEM_SERVICE_MAP.put(Context.CONNECTIVITY_SERVICE, connectionManager);
 
     // Setup BatteryManager
-    batteryService = new BatteryService(mSystemContext, null);
+    batteryService = new BatteryService(mSystemContext);
   }
 
   public static void start() {

### 2014-02-23 jpf-android/src/classes/android/view/Window.java
Log added

@@ -204,7 +204,10 @@ public class Window extends ViewGroup {
       // invoke the action on this view object
       try {
         Class<? extends View> viewClass = (Class<? extends View>) view.getClass(); // get the class
+        Log.i(TAG, "Trying::: " + view.name + "." + arguments);
         Method m = viewClass.getMethod(action, new Class[] {});
+ 
+
         m.invoke(view, (Object[]) arguments);
 
       } catch (NoSuchMethodException e) {

### 2014-02-23 jpf-android/src/classes/com/android/server/BatteryService.java
Update

@@ -12,7 +12,7 @@ public class BatteryService {
   private static final boolean LOCAL_LOGV = false;
 
   static final int BATTERY_SCALE = 100;    // battery capacity is a percentage
-  
+
   // Used locally for determining when to make a last ditch effort to log
   // discharge stats before the device dies.
   private int mCriticalBatteryLevel = 1;
@@ -35,7 +35,7 @@ public class BatteryService {
   private int mInvalidCharger;
 
   private int mLowBatteryWarningLevel = 5;
-  private int mLowBatteryCloseWarningLevel =3;
+  private int mLowBatteryCloseWarningLevel = 3;
 
   private int mLastPlugType;
   private int mPlugType;
@@ -45,7 +45,7 @@ public class BatteryService {
 
   private boolean mSentLowBatteryBroadcast = false;
 
-  public BatteryService(Context context, LightsService lights) {
+  public BatteryService(Context context) {
     mContext = context;
 
     // set initial status
@@ -57,7 +57,7 @@ public class BatteryService {
     // status when charger not attached is BATTERY_STATUS_DISCHARGING
     mBatteryStatus = BatteryManager.BATTERY_STATUS_DISCHARGING;
     mBatteryHealth = BatteryManager.BATTERY_HEALTH_GOOD;
-    
+
     // battery is present
     mBatteryPresent = true;
     mBatteryLevel = 100;
@@ -71,7 +71,7 @@ public class BatteryService {
     mLastPlugType = BatteryManager.BATTERY_PLUGGED_AC;
     mPlugType = BATTERY_PLUGGED_NONE;
     init0();
-    sendIntent(); 
+    sendIntent();
     Log.i(TAG, "Ready!");
 
   }
@@ -79,6 +79,7 @@ public class BatteryService {
   private native void init0();
 
   private void processValues() {
+    System.out.println("Got Battery state:" + mBatteryLevel);
 
     // check if we are at critical level
     mBatteryLevelCritical = mBatteryLevel <= mCriticalBatteryLevel;
@@ -95,8 +96,10 @@ public class BatteryService {
 
     /*
      * The ACTION_BATTERY_LOW broadcast is sent in these situations:
-     * - is just un-plugged (previously was plugged) and battery level is less than or equal to WARNING, or
-     * - is not plugged and battery level falls to WARNING boundary (becomes <= mLowBatteryWarningLevel).
+     * - is just un-plugged (previously was plugged) and battery level is less
[…]

### 2014-02-23 jpf-android/src/classes/com/android/server/IntentResolver.java

@@ -1,0 +1,604 @@
+/*
+ * Copyright (C) 2006 The Android Open Source Project
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *      http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+package com.android.server;
+
+import java.io.PrintWriter;
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.Comparator;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+import android.net.Uri;
+import android.util.FastImmutableArraySet;
+import android.util.Log;
+import android.util.PrintWriterPrinter;
+import android.util.Slog;
+import android.util.LogPrinter;
+import android.util.Printer;
+
+import android.util.Config;
+import android.content.ContentResolver;
+import android.content.Intent;
+import android.content.IntentFilter;
+
+/**
+ * {@hide}
+ */
+public class IntentResolver<F extends IntentFilter, R extends Object> {
+    final private static String TAG = "IntentResolver";
+    final private static boolean DEBUG = false;
+    final private static boolean localLOGV = DEBUG || Config.LOGV;
+
+    public void addFilter(F f) {
+        if (localLOGV) {
+            Slog.v(TAG, "Adding filter: " + f);
+            f.dump(new LogPrinter(Log.VERBOSE, TAG, Log.LOG_ID_SYSTEM), "      ");
+            Slog.v(TAG, "    Building Lookup Maps:");
+        }
+
+        mFilters.add(f);
+        int numS = register_intent_filter(f, f.schemesIterator(),
+                mSchemeToFilter, "      Scheme: ");
+        int numT = register_mime_types(f, "      Type: ");
+        if (numS == 0 && numT == 0) {
+            register_intent_filter(f, f.actionsIterator(),
+                    mActionToFilter, "      Action: ");
+        }
+        if (numT != 0) {
[…]

### 2014-02-23 jpf-android/src/classes/com/android/server/am/BroadcastFilter.java
Adding files not available

@@ -1,0 +1,52 @@
+package com.android.server.am;
+
+import android.content.IntentFilter;
+import android.util.PrintWriterPrinter;
+import android.util.Printer;
+import java.io.PrintWriter;
+
+class BroadcastFilter extends IntentFilter {
+  final ReceiverList receiverList;
+  final String packageName;
+  final String requiredPermission;
+
+  BroadcastFilter(IntentFilter _filter, ReceiverList _receiverList, String _packageName,
+      String _requiredPermission) {
+    super(_filter);
+    this.receiverList = _receiverList;
+    this.packageName = _packageName;
+    this.requiredPermission = _requiredPermission;
+  }
+
+  public void dump(PrintWriter pw, String prefix) {
+    dumpInReceiverList(pw, new PrintWriterPrinter(pw), prefix);
+//    this.receiverList.dumpLocal(pw, prefix);
+  }
+
+  public void dumpBrief(PrintWriter pw, String prefix) {
+    dumpBroadcastFilterState(pw, prefix);
+  }
+
+  public void dumpInReceiverList(PrintWriter pw, Printer pr, String prefix) {
+    super.dump(pr, prefix);
+    dumpBroadcastFilterState(pw, prefix);
+  }
+
+  void dumpBroadcastFilterState(PrintWriter pw, String prefix) {
+    if (this.requiredPermission != null) {
+      pw.print(prefix);
+      pw.print("requiredPermission=");
+      pw.println(this.requiredPermission);
+    }
+  }
+
+  public String toString() {
+    StringBuilder sb = new StringBuilder();
+    sb.append("BroadcastFilter{");
+    sb.append(Integer.toHexString(System.identityHashCode(this)));
+    sb.append(' ');
+    sb.append(this.receiverList);
+    sb.append('}');
+    return sb.toString();
+  }
+}

### 2014-02-23 jpf-android/src/classes/java/net/URL.java
Updating URL non-determinism

@@ -1,23 +1,29 @@
 package java.net;
 
+import gov.nasa.jpf.vm.Verify;
+
 import java.io.ByteArrayInputStream;
 import java.io.IOException;
 import java.io.InputStream;
+import java.io.Serializable;
 
-public class URL {
-
+public final class URL implements Serializable {
+  
   public URL(String spec) throws MalformedURLException {
     // to be intercepted
   }
 
   public InputStream openStream() throws IOException {
-    //TODO if no network connection 
-    //throw new IOException("Could not open Url");
-    byte[] arr = new byte[4];
-    return new ByteArrayInputStream(arr);
+    boolean b = Verify.getBoolean();
+
+    if (b) {
+      throw new IOException("Could not open Url");
+    } else {
+      return new ByteArrayInputStream(getURLInput());
+    }
 
   }
 
-  private native byte[] getURLInput();
+  protected native byte[] getURLInput();
 
 }

### 2014-02-23 jpf-android/src/classes/javax/xml/parsers/AndroidSAXParser.java
Update sax parser

@@ -1,0 +1,122 @@
+package javax.xml.parsers;
+
+import java.io.IOException;
+import java.io.InputStream;
+
+import org.xml.sax.InputSource;
+import org.xml.sax.Parser;
+import org.xml.sax.SAXException;
+import org.xml.sax.SAXNotRecognizedException;
+import org.xml.sax.SAXNotSupportedException;
+import org.xml.sax.XMLReader;
+import org.xml.sax.helpers.DefaultHandler;
+
+import android.util.Log;
+
+import java.io.ByteArrayInputStream;
+
+public class AndroidSAXParser extends SAXParser {
+  DefaultHandler handler;
+
+  private final int namespaceURI = 0;
+  private final int localname = 1;
+  private final int qname = 2;
+  private final int attributes = 3;
+  private final int content = 4;
+  private final int nextNodeHash = 5;
+
+  public AndroidSAXParser() {
+  }
+
+  public void parse(InputSource is, DefaultHandler theRssHandler) throws SAXException, IOException {
+    //    InputStream inputStream = is.getByteStream();
+    //    //Create BufferedReader object
+    //    BufferedReader bReader = new BufferedReader(new InputStreamReader(inputStream));
+    //    StringBuffer sbfFileContents = new StringBuffer();
+    //    String line = null;
+    //
+    //    //read file line by line
+    //    while ((line = bReader.readLine()) != null) {
+    //      sbfFileContents.append(line);
+    //    }
+
+    //finally convert StringBuffer object to String!
+
+
+
+    int hash = parse(is.getByteStream());
+    Log.i("SAXParserr", "Parsing url RSS feed at http://feeds.feedburner.com/Mobilecrunch.rss ");
+
+    handler = theRssHandler;
+    handler.startDocument();
+    visit(hash);
+    handler.endDocument();
+  }
+
+  public void visit(int nodeCode) throws SAXException {
+    if (nodeCode == -1)
+      return;
+    String[] node = getNodeInfo(nodeCode);
+
+    handler.startElement(node[namespaceURI], node[localname], node[qname], null);
+
+    int[] children = getChildren(nodeCode);
+    if (children != null) {
+      for (int child : children) {
+        visit(child);
+      }
+    }
+
+    String contentString = node[content];
+    if (contentString != null && contentString.length() > 0) {
+      char[] contentArray = contentString.toCharArray();
+      handler.characters(contentArray, 0, contentArray.length);
+    }
+
[…]

### 2014-02-23 jpf-android/src/classes/javax/xml/parsers/SAXParserFactory.java

@@ -1,13 +1,12 @@
 package javax.xml.parsers;
 
-
 public class SAXParserFactory {
 
   public static SAXParserFactory newInstance() {
     return new SAXParserFactory();
   }
 
-  public SAXParser newSAXParser() {
-    return new SAXParser();
+  public SAXParser newSAXParser() throws ParserConfigurationException {
+    return new AndroidSAXParser();
   }
 }

### 2014-02-23 jpf-android/src/tests/gov/nasa/jpf/test/mc/basic/AndroidScriptIntrTest.java
update

@@ -1,7 +1,9 @@
 package gov.nasa.jpf.test.mc.basic;
 
 import gov.nasa.jpf.ListenerAdapter;
+import gov.nasa.jpf.annotation.MJI;
 import gov.nasa.jpf.util.test.TestJPF;
+import gov.nasa.jpf.vm.ElementInfo;
 import gov.nasa.jpf.vm.Instruction;
 import gov.nasa.jpf.vm.MethodInfo;
 import gov.nasa.jpf.vm.ThreadInfo;
@@ -10,6 +12,7 @@ import gov.nasa.jpf.vm.VM;
 import java.util.ArrayList;
 
 import org.junit.After;
+import org.junit.Assert;
 import org.junit.Before;
 import org.junit.Test;
 
@@ -28,19 +31,19 @@ public class AndroidScriptIntrTest extends TestJPF {
     static ArrayList<String> sequence;
 
     public void instructionExecuted(VM vm, ThreadInfo currentThread, Instruction nextInstruction, Instruction executedInstruction) {
-//      if (executedInstruction instanceof gov.nasa.jpf.jvm.bytecode.ARETURN) {
-//        MethodInfo mi = executedInstruction.getMethodInfo();
-//
-//        if (mi.getUniqueName().equals("parseScript()Ljava/lang/String;")) {
-//          String a =currentThread.getStringReturnValue();
-//
-//          if (!a.equals("")) {
-//            sequenceCount++;
-//            sequence.add("Sequence " + sequenceCount + ": ");
-//            sequence.add(a);
-//          }
-//        }
-//      }
+      if (executedInstruction instanceof gov.nasa.jpf.jvm.bytecode.ARETURN) {
+        MethodInfo mi = executedInstruction.getMethodInfo();
+
+        if (mi.getUniqueName().equals("parseScript()Ljava/lang/String;")) {
+          @SuppressWarnings("unused")
+          String a = new String(((ElementInfo)((gov.nasa.jpf.jvm.bytecode.ARETURN)executedInstruction).getReturnValue(currentThread)).getStringChars());
+          if (!a.equals("")) {
+            sequenceCount++;
+            sequence.add("Sequence " + sequenceCount + ": ");
+            sequence.add(a);
+          }
+        }
+      }
     }
   }
 
@@ -87,8 +90,7 @@ public class AndroidScriptIntrTest extends TestJPF {
   @Test
[…]

### 2014-02-23 jpf-android/src/tests/gov/nasa/jpf/test/mc/basic/JPF_gov_nasa_jpf_test_mc_basic_ScriptParser.java

@@ -1,6 +1,7 @@
 package gov.nasa.jpf.test.mc.basic;
 
 import gov.nasa.jpf.JPF;
+import gov.nasa.jpf.annotation.MJI;
 import gov.nasa.jpf.util.JPFLogger;
 import gov.nasa.jpf.util.StateExtensionClient;
 import gov.nasa.jpf.util.StateExtensionListener;
@@ -9,16 +10,17 @@ import gov.nasa.jpf.util.script.ESParserE;
 import gov.nasa.jpf.util.script.Script;
 import gov.nasa.jpf.util.script.ScriptElement;
 import gov.nasa.jpf.vm.MJIEnv;
+import gov.nasa.jpf.vm.NativePeer;
 
 import java.io.StringReader;
 
 /**
- * Native Counterpart of the
+ * Native Counterpart of the ScriptParser
  * 
  * @author heila
  * 
  */
-public class JPF_gov_nasa_jpf_test_mc_basic_ScriptParser {
+public class JPF_gov_nasa_jpf_test_mc_basic_ScriptParser extends NativePeer {
   private static final JPFLogger logger = JPF.getLogger("JPF_gov_nasa_jpf_test_mc_basic_ScriptParser");
 
   /**
@@ -64,6 +66,7 @@ public class JPF_gov_nasa_jpf_test_mc_basic_ScriptParser {
    * @param objectRef
    * @return
    */
+  @MJI
   public static int getNextScriptElement(MJIEnv env, int objectRef) {
     ScriptElement e = si.getNext(env);
     if (e == null) {
@@ -71,7 +74,7 @@ public class JPF_gov_nasa_jpf_test_mc_basic_ScriptParser {
     } else
       return env.newString(e.toString());
   }
-
+  @MJI
   public static void $init__Ljava_lang_String_2__V(MJIEnv env, int robj, int scriptRef) {
 
     // convert the scriptRef to a JVM string

### 2014-02-23 jpf-android/src/tests/gov/nasa/jpf/test/java/net/URLTest.java
add new tests for  URL and sax  parser

@@ -1,0 +1,55 @@
+package gov.nasa.jpf.test.java.net;
+
+import gov.nasa.jpf.ListenerAdapter;
+import gov.nasa.jpf.android.JPF_java_net_URL;
+import gov.nasa.jpf.util.test.TestJPF;
+import gov.nasa.jpf.vm.VM;
+
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.InputStreamReader;
+import java.net.MalformedURLException;
+import java.net.URL;
+
+import org.junit.Test;
+
+public class URLTest extends TestJPF {
+  
+  public static class URLInjector extends ListenerAdapter {
+
+    public void vmInitialized(VM vm) {
+     JPF_java_net_URL.mapURLToFile("http://www.sun.ac.za/index.html", "src/tests/gov/nasa/jpf/test/java/net/index.html");
+    }
+  }
+  
+  @Test
+  public void newURLTest() {
+    if (verifyNoPropertyViolation("+listener=gov.nasa.jpf.test.java.net.URLTest$URLInjector")) {
+
+      try {
+        URL url = new URL("http://www.sun.ac.za/index.html");
+        InputStream is = url.openStream();
+        InputStreamReader reader = new InputStreamReader(is);
+        char[] contents = new char[15];
+        int num = reader.read(contents);
+        
+        String s =  new String(contents);
+        System.out.println(s);
+        assertTrue(s.trim().equals("<html></html>"));
+        
+      } catch (MalformedURLException e) {
+        System.out.println(e.toString());
+        assertTrue(false);
+
+      } catch (IOException e) {
+        System.out.println(e.toString());
+        assertTrue(true);
+      }
+    }
+
+  }
+  
+  public static void main(String[] testMethods) {
+    runTestsOfThisClass(testMethods);
+  }
+}

### 2014-02-23 jpf-android/src/tests/gov/nasa/jpf/test/javax/xml/parsers/SAXParserTest.java

@@ -1,0 +1,141 @@
+package gov.nasa.jpf.test.javax.xml.parsers;
+
+import gov.nasa.jpf.ListenerAdapter;
+import gov.nasa.jpf.android.JPF_java_net_URL;
+import gov.nasa.jpf.util.test.TestJPF;
+import gov.nasa.jpf.vm.VM;
+
+import java.io.FileInputStream;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.net.MalformedURLException;
+import java.net.URL;
+
+import javax.xml.parsers.ParserConfigurationException;
+import javax.xml.parsers.SAXParser;
+import javax.xml.parsers.SAXParserFactory;
+
+import org.junit.Test;
+import org.xml.sax.Attributes;
+import org.xml.sax.InputSource;
+import org.xml.sax.SAXException;
+import org.xml.sax.helpers.DefaultHandler;
+
+public class SAXParserTest extends TestJPF {
+
+  public static class URLInjector extends ListenerAdapter {
+
+    public void vmInitialized(VM vm) {
+      JPF_java_net_URL.mapURLToFile("http://www.sun.ac.za/index.html",
+          "src/tests/gov/nasa/jpf/test/javax/xml/parsers/index.html");
+    }
+  }
+
+  @Test
+  public void newURLTest() {
+    if (verifyNoPropertyViolation("+listener=gov.nasa.jpf.test.javax.xml.parsers.SAXParserTest$URLInjector")) {
+
+      try {
+        URL url = new URL("http://www.sun.ac.za/index.html");
+        // get our data through the url class
+        InputSource is = new InputSource(url.openStream());
+
+        DefaultHandler handler = new TestHandler();
+        SAXParser parser;
+        parser = SAXParserFactory.newInstance().newSAXParser();
+
+        // perform the parse
+        parser.parse(is, handler);
+
+      } catch (MalformedURLException e) {
+        System.out.println(e.toString());
+        assertTrue(false);
+      } catch (ParserConfigurationException e) {
+        System.out.println(e.toString());
+        assertTrue(false);
+      } catch (IOException e) {
+        System.out.println(e.toString());
+        assertTrue(true);
+      } catch (SAXException e) {
+        System.out.println(e.toString());
+        assertTrue(false);
+      }
+    }
+
+  }
+
+  public static class TestHandler extends DefaultHandler {
+    private StringBuffer builder;
+
+    /**
+     * Default Constructor for the feed
+     */
[…]

### 2014-02-23 Papers/images/pdf2eps.sh
removing files

@@ -1,10 +1,0 @@
-#!/bin/sh
-# $Id: pdf2eps,v 0.01 2005/10/28 00:55:46 Herbert Voss Exp $
-# Convert PDF to encapsulated PostScript.
-# usage:
-# pdf2eps <page number> <pdf file without ext>
-
-pdfcrop $2.pdf
-pdftops -f $1 -l $1 -eps "$2-crop.pdf" 
-rm  "$2-crop.pdf"
-mv  "$2-crop.eps" $2.eps

### 2014-02-23 jpf-android/src/classes/javax/xml/parsers/SAXParser.java

@@ -1,81 +1,0 @@
-package javax.xml.parsers;
-
-import java.io.IOException;
-import java.io.InputStream;
-
-import org.xml.sax.InputSource;
-import org.xml.sax.SAXException;
-import org.xml.sax.helpers.DefaultHandler;
-
-import android.util.Log;
-
-public class SAXParser {
-  DefaultHandler handler;
-
-  private final int namespaceURI = 0;
-  private final int localname = 1;
-  private final int qname = 2;
-  private final int attributes = 3;
-  private final int content = 4;
-  private final int nextNodeHash = 5;
-
-  public SAXParser() {
-  }
-
-  public void parse(InputSource is, DefaultHandler theRssHandler) throws SAXException, IOException {
-    //    InputStream inputStream = is.getByteStream();
-    //    //Create BufferedReader object
-    //    BufferedReader bReader = new BufferedReader(new InputStreamReader(inputStream));
-    //    StringBuffer sbfFileContents = new StringBuffer();
-    //    String line = null;
-    //
-    //    //read file line by line
-    //    while ((line = bReader.readLine()) != null) {
-    //      sbfFileContents.append(line);
-    //    }
-
-    //finally convert StringBuffer object to String!
-    int hash = parse("http://feeds.feedburner.com/Mobilecrunch.rss");
-    Log.i("SAXParserr", "Parsing url RSS feed at http://feeds.feedburner.com/Mobilecrunch.rss ");
-    handler = theRssHandler;
-    handler.startDocument();
-    visit(hash);
-    handler.endDocument();
-  }
-
-  public void visit(int nodeCode) throws SAXException {
-    if (nodeCode == -1)
-      return;
-    String[] node = getNodeInfo(nodeCode);
-
-    handler.startElement(node[namespaceURI], node[localname], node[qname], null);
-
-    int[] children = getChildren(nodeCode);
-    if (children != null) {
-      for (int child : children) {
-        visit(child);
-      }
-    }
-
-    String contentString = node[content];
-    if (contentString != null && contentString.length() > 0) {
-      char[] contentArray = contentString.toCharArray();
-      handler.characters(contentArray, 0, contentArray.length);
-    }
-
-    handler.endElement(node[namespaceURI], node[localname], node[qname]);
-  }
-
-  public native int parse(String url);
-
-  public native String[] getNodeInfo(int hash);
-
-  public native int[] getChildren(int hash);
-
[…]

### 2014-02-23 jpf-android/src/peers/gov/nasa/jpf/android/JPF_javax_xml_parsers_SAXParser.java

@@ -1,121 +1,0 @@
-package gov.nasa.jpf.android;
-
-import gov.nasa.jpf.JPF;
-import gov.nasa.jpf.annotation.MJI;
-import gov.nasa.jpf.vm.MJIEnv;
-import gov.nasa.jpf.vm.NativePeer;
-
-import java.io.IOException;
-import java.util.ArrayList;
-import java.util.HashMap;
-import java.util.Map;
-import java.util.logging.Logger;
-
-import javax.xml.parsers.DocumentBuilder;
-import javax.xml.parsers.DocumentBuilderFactory;
-import javax.xml.parsers.ParserConfigurationException;
-
-import org.w3c.dom.Document;
-import org.w3c.dom.Node;
-import org.w3c.dom.NodeList;
-import org.xml.sax.SAXException;
-
-public class JPF_javax_xml_parsers_SAXParser  extends NativePeer {
-  public final static String TAG = JPF_javax_xml_parsers_SAXParser.class.getSimpleName();
-  static Logger log = JPF.getLogger("gov.nasa.jpf.android");
-
-//  private final int namespaceURI = 0;
-//  private final int localname = 1;
-//  private final int qname = 2;
-//  private final int attributes = 3;
-//  private final int content = 4;
-
-  private static DocumentBuilder builder;
-  private static Map<Integer, Node> nodeMap = new HashMap<Integer, Node>();
-  private static Node root = null;
-
-  protected static Map<String, String> URLInput = new HashMap<String, String>();
-
-  @MJI
-  public void $init(MJIEnv env, int robj) {
-    DocumentBuilderFactory f = DocumentBuilderFactory.newInstance();
-    try {
-      builder = f.newDocumentBuilder();
-    } catch (ParserConfigurationException e) {
-    }
-  }
-
-  @MJI
-  public int parse__Ljava_lang_String_2__I(MJIEnv env, int objRef, int url) throws SAXException, IOException {
-
-    Document doc = builder.parse(AndroidPathManager.getProjectDir() + "/"
-        + URLInput.get(env.getStringObject(url)));
-    doc.getDocumentElement().normalize();
-    root = doc.getDocumentElement();
-
-    nodeMap.put(root.hashCode(), root);
-    //    System.out.println("Root element: " + root.getNodeName());
-
-    return root.hashCode();
-  }
-
-  @MJI
-  public int getNodeInfo(MJIEnv env, int objRef, int hashcode) {
-    if (hashcode == -1) {
[…]
